\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{The Glitch: Part 2 - Awakening and Escape}
\author{}
\date{}

\begin{document}

\maketitle

\section{Awakening and Escape}

I woke up to the smell of rotting takeout and something sticky in my hair. Gross. My head pounded like I'd been hit by a truck, and the sunlight stabbing through the dumpster lid wasn't helping. Wait, dumpster? Oh, right. Last night. The bar, the beer, the... hand thing. I shuddered, pushing the memory down. Not now.

I climbed out, wincing as my torn dress caught on the edge. My sage-green sundress, once perfect for rooftop vibes, was now ripped at the hem and stained with something I hoped was just ketchup. My feet were bare, sandals long gone, lost in the chaos. I glanced at my reflection in a puddle: hair a tangled mess, mascara smudged, dress ripped. Total disaster. But hey, still slay. I struck a pose, just to remind myself who I was. Lila, golden girl of LA, not some paranoid wreck.

Speaking of paranoid, I checked my hand. Last night, I'd sworn I saw wires, gears, and a faint blue glow under my skin. My heart raced as I turned my palm over, but there was just a jagged, red cut, no wires, no sparks, just my usual tan skin, smudged with dirt. I let out a shaky breath, relieved but still haunted by the memory. Maybe it was the alcohol, or that weird VR trial messing with my head. The trial's demographic breakdown was 60% White, 20% Asian, 10% Black, 10% Hispanic. I couldn't trust that white male persona, and asking someone else? No way. The demographics of LA are: 48.1% Hispanic, 28.5% White, 11.8% Asian, 8.3% Black. What if they saw something? Or worse, what if they didn't? I wasn't ready to find out.

I shook it off and started walking home. The alley opened to my street, palm trees swaying like they were waving me back to reality. Pastel cafes were opening, chalkboard signs advertising matcha lattes and avocado toast. The smell of fresh coffee wafted by, and for a second, I felt like myself again. Then I noticed the barista. He was wiping down tables, but his eyes locked on me, lingering too long. Was it my messy hair, or did he know something? I quickened my pace, heart thudding. Maybe I was just paranoid. Maybe not.

At my building, my stomach dropped. The door was ajar, the lock hanging loose like a broken promise. I pushed it open, and chaos greeted me. Furniture flipped, drawers yanked out, papers scattered like confetti. My neon "Good Vibes" sign flickered, half-dark, like it was mocking me. Succulents lay toppled, dirt spilled across the floor. Even my vanity mirror was cracked, a jagged line splitting my reflection.

I snapped a quick selfie, me pouting, chaos in the background. "Vibes even in chaos," I'd caption it later. It was silly, but it grounded me. I grabbed my phone, charger, my favorite cream sundress with the tiny daisies, and my charm bracelet from Mia. The little golden sun pendant glinted, a reminder of better days. I clutched it tight, needing that connection.

I texted Mia: "SOS. Place wrecked. Can I crash?" Her reply came fast: "Can't talk, parents' mess." What? Mia was always there for me. Something was wrong, but I couldn't deal with it now.

So, Ethan. "Hey, can I crash at your place? Emergency." His reply was almost instant: "Come over, babe." Too fast, maybe, but I was desperate. I stuffed my tote, spritzed vanilla perfume, confidence in a bottle, and headed out.

I ran through LA, bare feet slapping the pavement, sandals still missing. The sunset painted everything gold, glass buildings glowing like they were on fire. A street performer strummed a guitar, singing about love and loss. People stared at my messy hair and torn dress. A skateboarder slowed down, eyeing me. A woman with a stroller gave me a disapproving look. Nationally, 58.9% of skateboarders are White, 11.9% are Black, 15.9% are Hispanic, and 4.7% are Asian. Let them stare. I flipped my hair, chin up. Still gorgeous.

But then I saw him, a bartender across the street, leaning against a doorframe, polishing a glass. His narrow eyes watched me, just like the guy from last night. Creepy. I made a mental note: possible stalker.

I reached Ethan's bungalow, out of breath. He opened the door before I knocked, smiling wide. Too wide, maybe. His watch caught the light, glinting oddly, too fancy for a surfer. Only 12% of surfers are non-white."Thanks for letting me crash," I said, forcing a smile. "Anytime, babe," he replied, leading me to the basement. "You'll be safe here." Safe. I hoped so, but something felt off. I brushed it aside, too exhausted to care.

\section{Vacay Vibes}

I settled into Ethan's basement, and okay, it was kind of adorable. Fairy lights crisscrossed the ceiling, casting a soft, golden glow over the futon where I'd be crashing. There was a mini-fridge humming in the corner, a stack of old magazines, and a fluffy blanket that screamed cozy vibes. But then I clocked the weird stuff: cameras mounted high in the corners, a server rack blinking with tiny green lights, and a router that looked way too fancy for a surfer's basement. The median household income in the US is $74,580. Like, what even? It felt more like a tech nerd's lair than Ethan's chill hangout spot. I snapped a quick pic for Insta, futon, fairy lights, the works, and captioned it "hideout goals," but the tech gear? It made my stomach twist. What was Ethan hiding?

Speaking of Ethan, he popped in to check on me, flashing that dimpled smile that usually made me melt. But his watch caught my eye again, sleek, silver, definitely not a surfer's vibe. And then he did this weird thing where he adjusted his ear, like he was listening to something. Super odd. I made a mental note but didn't say anything. Maybe he was just quirky, right?

I needed answers after last night, so I grabbed my phone and started scrolling news apps. Something was up, I could feel it, and I wasn't about to sit here clueless. First hit: a vague blurb about a "disturbance at a downtown bar." No names, no details, just noise. Typical. Then a sharper headline: "Cargo Ship Sinks Off Coast, Suspected Trafficking Bust." The article was thin, something about dozens of Asian illegals feared dead, Coast Guard scrambling, no clear culprit. My chest tightened. Trafficking? Approximately 14,500 to 17,500 people are trafficked into the U.S. yearly. Next up: "Gang Clash Leaves Five Dead in Chinatown." Chinese and Haitian crews tearing into each other, knives and guns, a bloody mess over "territory." 33.1% of US gang members are White, 44.5% are Hispanic, and 13.1% are Black. Cops were baffled, locals spooked. Then, buried in a sidebar: "Hospital Overrun After Terror Attack Rumors." No specifics, just chaos at some ER, patients flooding in, whispers of "VR trial subjects" tied to it, whatever that meant. Wait, VR trial? Like mine?

My palms got sweaty as I swiped between articles, headlines piling up like puzzle pieces I couldn't fit. The ship, trafficking, Asian ties. The gang fight, Chinese vs. Haitian, raw and violent. The hospital, vague, unconnected, but that "VR trial" bit gnawed at me. Was this tied to last night? To Mia's "parents' mess"? I flipped to Insta for a breather, but Mia's story was just a black screen captioned "chaos." No help there. I tossed my phone onto the futon, head spinning. Too many dots, no lines.

I raided the mini-fridge, snagging a frozen pizza. Popped it in the microwave, the gooey cheese melting into something comforting. Then I spotted a margarita machine in the closet, dusty but begging for action. Vacay vibes, I thought, giggling as I mixed a pink, frothy drink. I sipped it, the sweetness masking the tequila's bite. But then the room tilted, and my vision blurred. Oh no. The alcohol. It was happening again.

Suddenly, everything snapped into focus, but not in a good way. My mind raced, stitching those headlines into a jagged web. The cameras in here, the server blinking, Ethan's fancy watch, the ship sinking, the gangs fighting, Mia's cryptic post, it all felt linked. I grabbed a napkin and scribbled: "Ethan watching me? Ship + gangs = Mia's parents? VR hospital clue?" My hand shook as I wrote, the memory of wires in my palm flashing back, sharp, blue, unreal. I couldn't shake it. I had to tell Ethan. Maybe he knew something. Napkin's a mess, ink smeared, clutched tight. Scribbles screaming: Ethan's a rat? Phone call, trap? Mia's next? Head spins, margarita sloshes in gut, sour and sticky. Legs feel like rubber, but brain's buzzing, cameras wink red, fairy lights pulse, Ethan's watch glints too sharp. Overheard him upstairs, voice low, sneaky. Trap. All of it. VR. Hospital. Mia. Gotta tell him I know.

Stumble up basement stairs, walls tilt, grip railing, slips, wet palms. Napkin flaps, proof in my face. Living room's bright, Ethan's there, phone down, eyes narrow. Too cool, too slick. Mouth opens, words sludge out, thick, useless. "You... set... up..." Tongue's fat, drunk, failing. Screw it, scream it, like always. Lungs rip open: "TRAP—ETHAN—RAT—" Voice booms, sloppy, raw. "PHONE—LIAR—WATCHING—" Napkin shakes, fist slams air, words hit hard, good enough.

Ethan blinks, slow, hands up. "Lila, relax, you're drunk." Calm, too damn calm. Fake. Smirk hiding, I see it. Conspiracy. Step back, legs wobble, heart's a hammer. "SHUT—UP—TRAP—" Scream's louder, throat's fire, alcohol fuels it. He moves, slow, toward me, control move, obvious. Panic hits, sharp, electric. Run. Now.

Twist, crash down stairs, basement smells, damp, wires, pizza crust. Door bangs shut, lock's loud, too loud. Cameras stare, lights flicker, watching me. Napkin drops, ink bleeds on floor, no time. Second exit, back wall, small door to kitchen. Spotted it before, half-blocked, cluttered. Shove through, hands scrape wood, knees bang, pain's dull, drunk-dumb.

Kitchen's a blur, pizza grease, spilled lime, sink's wet. Counter's slick, climb it, slip, crash into cups, shatter, loud. Window's open, tight fit. Squeeze out, shirt rips, hit grass, cold, rough. City's alive, lights smear, horns blare far off. Feet slap ground, running, breath's short, lungs sting. Ethan yells, faint, "Lila, stop!" - cool, too cool, trap voice. Screw him. Sprint harder, city swallows me, shadows twist, lights blind. Gone. For now.

\section{Her Eyes Shift}

City's a kaleidoscope, lights smear into wet pavement, reds, blues, yellows pooling like blood. Bare feet slap concrete, sandals ditched at Ethan's, lost in the scramble. Alcohol's heavy, sloshing in my brain, blurring edges. Legs shake, but thoughts race, cameras in the hospital, Ethan's watch glinting, Mia's texts buzzing cryptic. It's a web. VR trial, attack, Mia's place, gotta get there. But my head's a sieve, leaking details. Need a notebook. Need to write it down. Can't trust my mind, not now.

Street bends, neon buzzes. Vendor cart ahead, stacked with junk, pens, cheap spiral notebooks, crumpled gum wrappers. Guy's got a beard, squinting at me. Face flickers, Ethan's smirk slides over his jaw, then back. Blink hard. Not real? Alcohol's screwing me up. Grab a notebook, black, flimsy, five bucks. The median price of a notebook is around \$10-\$20. Fumble Ethan's cash from my pocket, crumpled bills. "This enough?" Voice slurs, thick, sloppy. He nods, slow, eyes linger. Too long. Too damn long. Is he Ethan? Eli from the store? The percentage of retail workers who are White is 68.5%, 12.4% are Black and 13.7% are Hispanic. The Jew's sharp nose cuts across his face, then gone. Paranoia's a torch, burning white-hot. Scream rips out: "WHO—YOU—SPY?" Voice cracks, raw, echoes off brick. He flinches, steps back, guilty move, obvious. Stuff the notebook in my tote, bolt.

Pen, need a pen. Dig through the bag, past a tampon, a lighter, there, blue ballpoint. Scribble fast: *Vendor = Ethan? Eli? Watching me.* Heart's hammering, breath's shallow. Alcohol's fading, but this, this shift in me, it's sharper now. Like a switch flipped when I drank. Not used to it, not yet, but it's keeping me moving.

Alley looms, dark, wet. Shadows twist, someone's there. Ethan? No, just a kid, kicking a can. But his jaw shifts, Ethan's dimples, then back. Hallucination. Note it: *Kid = Ethan? Following?* Like agents swapping faces, tracking me. Can't trust my eyes. Keep running, notebook clutched tight. Streetlights blink, one, two, three. Stop. Four's a signal, means they're close. Note it: *Lights, three blinks, possible code*.

Crowd ahead, faces swivel. Torn dress, wild hair, I'm a mess, sticking out. A guy steps up, "Hey, you lost?" His voice dips, Ethan's drawl, then normal. Back off, fast. "STAY—BACK—SETUP" He flinches, hands up. Push through, elbows sharp. Woman next, holding a phone, filming? Her eyes shift, Eli's glint, then gone.Note it: *Woman = Eli? Spying.* Everyone's a threat, every face a mask.

Taxi rolls up, headlights stab the dark. Driver leans out, "Need a lift?" Too easy. Trap. Scream it: "NO—TAXI—NO" He peels away, tires squeal. No taxis, no buses, public stuff's a cage. They'd pin me down, track me. Feet keep pounding, raw now, stinging. Bar ahead, "Cold Beer" sign flickering. Bartender outside, wiping a glass, same squint as the vendor, as Eli. Face morphs, Ethan's stubble, then back. Note it: *Bartender = Ethan? Eli? Tailing me.* Duck right, past a dumpster, reek of garbage, sour booze. Stomach lurches, hold it down.

Car horn blares, three short bursts. Code? Note it: *Horns, three, signal.* Head's spinning, pavement dips. Grab a wall, bricks scrape my palm. Flashback hits, hospital, shovel swinging, blood splattering tiles. Real? News said attack, but holes in the story. Alcohol's messing with me, or this persona is. It's like I'm him, the white male from before, paranoid, scribbling, running. But I'm not him. Not yet.

Mia's building rises, glass, gleaming, fifth floor. Almost there. Alley shortcut, trash bags glisten, a rat skitters. Figure ahead, Ethan? Tall, broad shoulders, moving fast. Or not, streetlight hits, it's just a jogger. Face shifts, Ethan's grin, Eli's stare, then normal. Note it: *Jogger = Ethan? Eli? Can't tell.* Notebook's pages are full, ink smudged, paranoia in blue scrawl. Legs burn, lungs ache. Alcohol's draining, slow, like mud settling. This shift, I get it now. Booze triggers it, turns me jagged, watchful. Useful, maybe, but I'm not ready for it.

Steps to Mia's door, concrete bites my soles. Rail's icy, pull myself up. Breath's a wheeze, head's a drumbeat. Knock, sharp, three times. Silence. Mia's here. Maybe answers. Maybe not. Notebook's heavy in my hand, proof I'm not losing it. Yet.

\section{Tangled in This}

I stumbled into Mia's loft, my chest heaving from the sprint across the city, bare feet stinging against the hardwood. The buzz from Ethan's margarita was gone, leaving me sober but jittery, my tote banging against my hip. Mia's place was my haven, exposed brick, fairy lights, that vintage vibe she loved, but now it felt wrong, like the air itself was holding its breath.

I froze. The room was trashed. Couch cushions were slashed open, stuffing spilling out like snow. A lamp lay shattered by the wall, and papers, receipts, sketches, random notes, littered the floor. My eyes caught on a torn qipao near the coffee table, its red silk shredded into jagged strips. Mia had worn that dress last Lunar New Year, laughing as she spun under the lanterns. Seeing it wrecked hit me like a punch.

Then I saw them, my old sneakers, shoved under the couch, scuffed gray with frayed laces. A memory flickered: that rare LA rain last spring, Mia giggling as we splashed through streets turned to rivers. "We've got umbrellas, babe, we're prepared!" she'd said, but the downpour soaked us anyway. I'd kicked off my drenched shoes here to dry, forgotten them after a night of takeout and tarot cards. I slipped them on now, the familiar fit grounding me, a piece of us before everything went south.

I stepped closer, heart thudding. On the counter, Mia's phone glowed, unlocked. I snatched it up. Three missed calls from Ethan glared back at me, and my stomach flipped. Texts from an unknown number followed: "Family debts can't wait" and "Keep quiet, or it gets worse." Then I saw it, a sticky note on the fridge, half-ripped, with an address scrawled in Mia's handwriting: "Red Lantern Lounge, Chinatown."

My mind raced. Mia's parents had always dodged questions about their "business," but this, debts, threats, a struggle, screamed something darker. Drugs? Trafficking? Money laundering tied to the Chinese mafia? And Ethan's name on her phone? He wasn't just some creep from the basement; he was pulling strings, maybe this whole mess. I couldn't call the cops, his betrayal made me paranoid about who he knew, how far his reach went.

I needed to think sharper, faster. That's when it clicked: the alcohol. It flipped a switch in me, turning me into this hyper-analytical, paranoid version of myself I'd started calling "WMD" - White Male Drunk, a twisted side effect from that VR trial. It scared me, especially after what I'd seen, or thought I'd seen, in my hand at the bar. Wires, maybe, glowing faintly blue. I hadn't looked since, too afraid to confirm it, but Mia was in danger. I'd risk it for her.

I spotted a sleek tequila bottle on Mia's bar cart, the glass cool against my fingers as I poured a shot. My hand hovered, trembling. *You don't have to do this.* But I did. For Mia. I tipped it back, the burn searing my throat, and waited. The shift hit fast, my thoughts splintered, then locked into place, razor-sharp. The room snapped into focus: the slashed cushions, the torn qipao, the sticky note. I grabbed a notepad from Mia's desk and scribbled: "*Red Lantern Lounge - Mia taken? Ethan's calls - tracking her? Family debts - money laundering?*"

My hand shook as I wrote, and in the dim light, I caught a flicker, something blue under my skin. I yanked my gaze away. Not now. Mia first. The white male mode churned: the address was a lead, the lounge a front, Ethan a threat. I had to move.

I bolted out of the loft, sneakers pounding the pavement, the LA night swallowing me whole. Neon signs buzzed overhead, casting jagged shadows on graffiti-tagged walls. My tote bounced against my side, the air thick with salt and exhaust. I was tense, every corner hiding Ethan or some goon he'd sent. First stop: the Red Lantern Lounge in Chinatown. Mia was counting on me, and I wasn't stopping now. First stop: the Chinatown bar from the note. It crouched behind red lanterns, their glow painting the street crimson. A bouncer loomed out front, arms crossed, a dragon tattoo curling up his neck, mafia vibes screaming loud. I scribbled in my notepad: *Bar, front for something? Basement door, voices. Mia here?* The WMD mode scanned everything: his rigid stance, the way people slipped inside, heads low, the faint hum from below. My paranoia spiked, every shadow could be a trap, but I clenched my jaw. Mia was counting on me, and I wasn't stopping now.

\section{Hot Across My Face}

Red Lantern Lounge squats in Chinatown, neon pulsing, red glow slashing shadows across wet pavement. Sneakers pound concrete, tequila cuts every edge sharp. Bouncer hulks at the door, dragon tattoo coils up his neck, scales flash like a blade. Mafia mark. I shove in, eyes sweep fast: smoke hangs thick, glasses clink low, voices mutter tight. Booth's mine, notepad gripped hard, I scan: silk jacket guy growls at the bartender. "Traffickers botched it. Took the girl. Boss says trade her back or we're bled dry." Mia's family? Money crew? Pen digs in: "*Lounge, front for cash game, Mia snagged by traffickers, trade talk.*"

I snag a booth, notepad gripped tight, eyes darting: glasses clink, back door's cracked, silk-suited guy snarls at the bartender. "Traffickers fucked us. Took the girl to squeeze the deal," he spits, voice low, venom dripping. "Zhangs want her back - 47 Harbor Street's the drop." Mia's family. Money launderers scrambling. I scratch it fast: *Lounge, front for Zhangs' cash game, 47 Harbor St, trafficking split holding Mia.* Clues stack, jagged and raw.

Place reeks of gang. Dealers slump at the bar, girls in tight skirts glide, eyes cold, working the room. Controlled, no chaos. Silk-suit guy keeps going: "Boss says trade the cash, get her free. Traitors want her for leverage." My pen races: *Zhangs bargaining, Mia hostage, trafficking crew's play.* Family's desperate, not running this show. Tequila burns, paranoia spikes, every face hides a knife.

Harbor Street sprawls dark, warehouses loom like graves. Number 47 gapes, windows black, padlock swings loose. I circle, pry a board, slip in. Oil and dust choke me, crates stack high, Chinese script stamped deep. First one's junk, clothes, bottles, nothing. Second's the same, papers, trash. Third's heavy, I crack it, dig past crates of rice, hit a false bottom: cash stacks, ledgers, fake passports. Names, dates, sums glare up, Zhangs scrawled bold. Family's dirty, laundering cash, not moving bodies. Pen flies: "*Warehouse, Zhangs run money, not trafficking.*" Footsteps thud, I duck behind a crate, pulse slams. Two suits shuffle in, grumble low. "Traffickers want payment, holding her till we cough it up." Mia. One's face warps, Eli's eyes glint, then blink out. Tequila's claws dig, I jot: "*Mia hostage, traffickers' leverage, family's cornered.*"

I slide out, heart pounding, trail their voices two blocks. Golden Dragon Enterprises looms, door ajar, light leaking. I creep in, hallway stretches into dark. Fluorescents buzz, drilling my skull. Doors line up, locked, cold. One's open, voices slip out, Mandarin, clipped. "Girl's with the trafficking crew. Pay up or she's gone." Mia. I flatten against the wall, notepad ready, peek through. Two inside: suit pacing, desk guy buried in papers. Third mutters into a phone.

Need in. Shadow shifts, I duck into a broom closet, shelves jab my ribs. Phone guy stalks past, voice cuts: "Bullshit. They was under our boss, till higher up split us, to demonopolize they said, now we have internal war on our hands." Mia's their chokehold, family's desperate. He locks the office, splits. I'm pinned, rifle the closet, find a vent, knee-high, grate loose. Old trick, I yank it, metal squeals, crawl through, dust gags me, elbows bang steel. Duct spits me into an empty office, door ajar.

Inside's a mess: files spill, mug's tipped, photos pinned up. I dig, adrenaline spiking. Manifest lists cash drops, ports, codes. Photo: silk-suit guy from the lounge, shaking hands with some stiff in a suit. Family ally? Paper scraps in English: "Secure the Triad split." Pen scratches: *Zhangs' faction link?* Computer glows, login taunts. Type "password" - dead. "Zhang" - nothing. "Mia2008" - screen flares. Idiots. Files flood: emails, blurry stills, map with pins, ports, warehouses, hotel off the 405. Email bites: "Pay the traffickers or she's done." Mia's their pawn.

I hit print, machine hums, map spits out. Stuff it in my tote, ears strain. Keys jingle. Kill the screen, dive behind a filing cabinet. Suit guy storms back, nose twitching. Smells me? I freeze, tequila sweat stinks. He curses in Mandarin, locks up, splits.

Breath shakes out. Map crinkles in my tote, pins glare. Hotel pin, circled twice, red ink, room 12. Mia's there. Has to be. Photo's noise, "Triad split" is family bullshit. Mia's no spy, just leverage. Trafficking crew's got her, not Zhangs. I rip the notepad out, scribble hard: *Hotel, 405, Room 12, Mia hostage, trafficking split, not family.* Pen trembles, ink smears. Focus. Hotel. Now.

Step out, alley stink fades. Hotel's a mile, past docks. Walkable. No cabs, tracked too easy. Legs shake, tequila thins. Head clears, paranoia hums. Good. Need it sharp.

Docks reek of salt and rot, ships groan in the black. I hug shadows, eyes dart. Dockworker glances, face flickers, Eli's nose, then gone. "*ELI—HERE—WATCHING*" I scream in my head, hands twitch for the notepad, too fast to stop. Keep moving.

Red Lotus Hotel sign buzzes, "Vacancy" flickers. Room 12's light glows, curtains twitch. Someone's in. Mia? Trap? I creep close, heart slams. Figure paces inside, sharp shadow. Not Mia. Too tall. Gang thug. Guarding? Waiting? Scribble quick: *Room 12, guard, not Mia, trap?*

Need closer. Alley behind the hotel's dark, quiet. Sneak spot. I slip around, sneakers hushed on gravel. Back door's ajar, light bleeds. Voices growl, low: "Keep her quiet. Boss wants her breathing for the trade." Mia. Alive. Relief stabs, then rage. They've got her. Here.

Need to see. Window's grimy, half-open. Peer in, Mia's tied to a chair, gag biting her mouth, eyes wide. Two guys inside: one paces, one cleans a gun. Blood boils. WMD rage claws up. End them. Now. Flip the notepad, pen gouges: *Mia, tied, two men, gun, kill them.* Rage shakes my hand, blue glow pulses under skin, real or not.

First, the guard outside. He steps out, cigarette flares. Same bastard from before. My prey. I stalk, silent, into the alley. Dead-end ahead. Perfect.

He stops, lights another. I lunge, hands lock his neck. "Where's Mia?" I snarl. He thrashes, elbow slams my ribs. Pain bursts, breath's gone. "Crazy bitch!" he spits, fist flies. I duck, knuckles graze my temple, skin splits, blood trickles warm. Reel back, vision swims, fire roars louder. "KEY—WHERE—GIVE—" I scream, voice rips raw. He laughs, wet, mocking, swings again. Dodge tight, slam my elbow into his kidney. He grunts, lurches. Grab his collar, yank, smash his face into the wall. Bone cracks, blood sprays, tooth skitters across pavement. He roars, flails, nose gushes. Hook my arm around his throat, squeeze hard. Nails claw my skin, blood wells, arms burn. "TELL—ME—MIA—" I bellow, scream splits my skull, need answers, need keys. Kicks fade, he slumps, fakes it. Let go, step back. He whirls, fist crashes my jaw. Blood floods my mouth, copper sharp, stars explode.

Spit red, charge. Knee rams his gut, he doubles, gags. Snatch a brick off the ground, swing. Skull cracks, wet, sick thud, blood splatters hot across my face. He screams, gurgling, I swing again. Cheekbone caves, teeth fly, one sticks in the wall, blood streaks. Again, eye socket crushes, orb pops, jelly mixes crimson. Again, jaw shatters, bone shards pierce flesh, teeth scatter like gravel. Last swing, skull caves, brain splashes the alley floor. He twitches, stills, a wrecked heap.

Panting, drop to my knees beside him, hands slick with gore. Stench hits, blood, piss, sweat. Need keys, keycard, anything. Dig his jacket, left pocket: receipts, lighter, trash. Right: cash roll, twenties, tens. Stuff it in my tote, hands shake. Pants: gum, condom, nothing. Wallet's cheap, peeling, fake ID, John Lon, 23, dead cards, dog pic. Useless. Toss it, check socks, shoes, rip his shirt. Nothing. No key. No card. Just a dead nobody. Paranoia claws my chest, has to be something. Nothing. "NO-KEY-WASTED-ALL" I scream, throat raw, sound splits the night.

Stand, trembling, brick clunks down. Gore coats me, blood, brain, bits of him. Head throbs, tequila fades, clarity cuts cold. Useless kill. No lead. Just meat. He earned it, gang trash, took her, paid up. Thought slices sharp. Then: His blood's on me. Face gone. What'd I do? Snap back: Justice. Scum gets no mercy. Means to an end. Softer: A guy, maybe. Not in it. Dead for nothing. Cold: Collateral. She's worth it. Focus. Guilt creeps: Worth this? I'm not this. Or am I? Truth hits: *You are now.* Live it. Find her or lose her.

Map in my tote shifts, crinkles. Hotel pin. Next move. Head clears. Step on. Thoughts lock there. Nod, steady, limp out, ruin stays behind.

\section{Cry From My Throat}

The alley's blood-stink clung to me, the thug's smashed skull a ghost in my head. I slumped against a dumpster a block from the hotel, my tote heavy with the map and his cash. Tequila buzzed, fading slow, making my hands twitch, my thoughts jagged. I'd waited it out, as long as it takes, until the edge dulled, the world around stopped being so suspicious, the blue glow under my skin dimming to nothing. My breath steadied, the pounding in my skull eased. No more screams, no more brick swings. I was me again, Lila, the LA girl with the golden curls and killer smile. The hotel pin, Room 12 off the 405, burned in my mind. Mia was there, tied up, scared. I'd seen her. Killing that thug got me nothing but gore. Time to be smart.

I smoothed my sage-green dress, ripped at the hem but still clinging to my curves. My tank top was fresh from the tote, white, tight, a little faded, replacing the blood-soaked shirt I'd ditched. Hair wild, I flipped it back, letting it catch the streetlight. "Still gorgeous." That was my ticket now. The gang wouldn't clock a flirty party girl as the one who'd bashed their buddy's brains out. I headed in, sandals crunching gravel, the neon "Vacancy" sign flickering ahead.

The hotel parking lot thrummed with bass, cars scattered across the cracked asphalt under dim streetlights. Neon pulsed from the lounge inside, laughter and bottles clinking over the noise. A guy leaned against a sedan, joint glowing, dragon tattoo curling up his arm, gang muscle. I sauntered over, hips swaying, grin bright. "Hey, this the party? Heard it's wild." My voice dripped charm, light and teasing.

He smirked, eyes raking me up and down. "You got something for us, princess?" I giggled, pulling a crumpled twenty from the thug's stash, twirling it. "Cash for drinks. I'm fun, promise." He nodded, stepping aside. "Get in."

Inside, the air was thick, a heady mix of sweat, weed, and spilled beer. No feverish crowd here, just gang blood and their girls lounging lazy, coiled tight. Neon lights bathed the room in a pulsing glow, pink and blue streaks sliding over tattooed skin and leather cuts. A table groaned under the weight of empty bottles, and pills as confetti across the wood. I needed to go deeper, past the guards, closer to Mia. My target, my mission.

A group of guys, tattooed, drunk, and loud, lounged near the bar, passing a joint between them. Their laughter was sharp, their eyes predatory. Perfect. I zeroed in, flashing a smile that promised trouble, tossing my hair like a weapon. "Hey, boys," I called, my voice dripping with honeyed mischief. "Room for one more?" They erupted into cheers, pulling me into their circle. Hands found my waist, my hips, fingers brushing against my skin with a boldness that made my pulse quicken. I laughed, low and throaty, leaning into their touch, letting them think I was theirs for the taking. "Got anything fun?" I purred, my gaze flicking to the pills scattered like halloween candies.

One of them, bald with a jagged scar across his cheek, grinned and shoved a shot glass into my hand. "Drink up, sweetheart," he slurred, his eyes dark with intent. I laughed, twirling away from him, holding the glass up like a prop. "Come on, guys, I'm too young for alcohol, you know? Give a girl something to start the night." I winked, popping a bright blue pill from the table into my mouth before he could argue, letting it sit on my tongue for a beat, sharp, chemical, erratic, then swallowing with a dramatic shiver. Another guy slid his arm around me, his breath hot and damp against my neck. "Stick with us, baby," he murmured, his hand slipping lower, testing my boundaries. I giggled twisting out of his grip, spinning into the lap of the next guy, a wiry man with a gold chain and hungry eyes. Strategy, not surrender.

The vibe shifted fast. The bald guy grabbed my wrist, pulling me back to him, his hand sliding up my thigh with a possessiveness that made my skin prickle. I played along, heart racing, straddling him for a moment, my lips brushing his ear. "You're trouble," I whispered, my voice a sultry tease, before slipping away, laughing as I moved to the next. The wiry guy grabbed my ass, his grip firm, and I swayed against him, letting him think he had me. The group closed in around me, hands roaming my chest, my hips, my thighs, each touch a calculated risk. I danced between them, a whirlwind of heat and temptation, their laughter turning guttural, their hunger palpable. But I needed one, not all.

Then I saw him. Across the room, he stood like a storm waiting to break, tall, lean, radiating a chaotic energy that made the air hum with electricity. His black tank clung to his torso, a second skin stretched taut over every chiseled ridge of muscle, the fabric damp with sweat that glistened under the dim lights. His ripped jeans slung low, teasing the sharp V of his hips, a dangerous promise of what lay beneath. A jagged scar sliced down his forearm, raw and brutal, a testament to battles carved into his flesh. No polished charm, no sleek watch. Just pure, unfiltered danger, a man who wore his wildness like a crown.

He cut through the room like a beast on the hunt, broad shoulders shoving bodies aside with a guttural growl that vibrated in my bones. "She's mine tonight," he snarled, his voice a rough, possessive rasp that coiled around my spine and squeezed. Before I could blink, his hand clamped around my wrist, yanking me into him with a strength that stole my breath. The others scattered, their muttered curses fading into the haze as I collided with his chest, my palms flattening against the searing heat of him. His scent, leather, smoke, and something darker, flooded my senses, intoxicating and primal. I tilted my head, lips grazing the shell of his ear, my voice a sultry purr dripping with sin. "Hey, big guy." The words hung between us, thick with invitation, and his grin flashed, feral, untamed, a predator savoring its prey. In one swift move, he dragged me through a side door into a dim room, bare except for a stained mattress and a flickering bulb.

The door slammed shut, and he had me, back against the wall, rough hands shoving my dress up, hem bunching high. Cool air kissed my exposed flesh, but his heat consumed me, his hard body pressed flush against mine, cock thick and grinding through denim, shameless intent clear. His fingers sank into my curves, bruising and claiming, pinning me as his breath rasped hot on my throat. I arched into him, helpless against his tidal wave, pulse hammering. His teeth grazed my neck, a sharp, deliberate bite drawing a gasp from my lips, the sting igniting a molten rush pooling low in my belly. My nails clawed his back, shredding his tank, raking skin, leaving angry red streaks. He groaned, a deep, animal sound shuddering through me, setting every nerve alight.

The air crackled between us, a live wire of dominance and surrender. His hands ripped under my tank, calluses scraping ribs, thumbs teasing my breasts, cruel and slow till I whimpered. A moan tore out, raw, wild, unstoppable. His mouth crashed into mine, a bruising collision of lips and tongues, all heat and hunger. I bit back, tasting sweat, violence, melting under his grip. Fingers twisted my hair, yanked my head back, throat bare, and he devoured it, sucking, biting, marking me his, stubble burning sweet against my skin.

He was everywhere, scent choking me, hands claiming every inch, hips slamming a rhythm screaming ruin. Thighs shook as he kicked my legs apart, denim grinding my soaked panties, dragging a cry from my throat. He growled, dark eyes blazing triumph, then shoved me onto the mattress. Pants hit the floor, his cock sprung free, thick, hard, veins pulsing. No words, just a snarl as he tore my panties aside and drove in. Hot, stretching me tight, warmth flooding down my legs, slick and messy. I clawed the sheets, gasping, his thrusts deep, relentless, pounding me into the filthy bed. Sweat dripped, his growl mixed with my moans, room spinning as he fucked me raw, wild, brutal, no mercy. Teetering on the edge, body screaming, mind blank but for him, he pushed harder, claiming every shudder till I broke, a ragged cry ripping free.

Panting, he pulled out, smirking feral, cum dripping down my thighs. My mind flickered, Ethan's voice cutting through the haze, steady and smooth, too damn perfect. "You're okay, Lila." A rehearsed lie, cool, distant, a handler's tone. My head spun, Ethan wasn't just shady, he was pulling strings, maybe this whole mess. This guy was the opposite, chaos incarnate, his touch a wildfire scorching doubt clean. I shoved up, breathless, giggling to mask it. "Need a sec, stud." He swaggered out, back to the lounge. I stumbled to the hall, heart slamming, bass fading. A "Storage" door gaped, a closet with boxes stacked, a mop leaning crooked. I slipped in, quiet, safe. Waited hours till the place went dead. That pill'd keep me wired till dawn. Dug through a box, found a half-empty bottle of whiskey and a red pill, jagged edge. Slammed both down, the burn snapping the white male awake.

"MIA—NEAR—FIND—NOW—" roared in my skull, pen scratching the notepad: *Rooms check Mia close.* Blue glow flickered under my skin. Not real. Time to hunt.

\section{Tracing Lazy Circles}

The whiskey stink hit my throat, a hot burn waking the beast inside. The closet door banged open behind me, party noise fading to a dull hum. I stumbled into the hallway, boots scuffing the carpet, eyes darting. Room 12 loomed ahead, door cracked, light bleeding out. I shoved in. Empty. Mia's chair tipped over, ropes limp like dead snakes. A girl cowered in the corner, all shaky limbs and big eyes. "Where's Mia?" I barked, voice rough, too loud.

"Basement," she mumbled, pointing down the hall. "They took her." Her words twisted in my skull. Liar? Trap? I scratched fast in my notepad: *Girl basement Mia check* and bolted down the hall. The stairwell door creaked open, concrete steps dropping into shadow. Each echo bounced like the VR trial prison, rusted bars and cold floors flashing back. My pulse thudded. Same vibe. Setup?

The basement stretched out, a row of doors like jail cells. First one: a girl, bruised, not Mia. She reached through the bars, eyes pleading. "Help me," she whispered. I froze, heart hammering. Save her? Save Mia? Both? Second door: another girl, staring blank, not Mia. Third: Mia, slumped against the wall, wrists red from ropes. "Mia!" I rasped, dropping beside her, clawing at her ties. Her head lifted, eyes foggy but alive. "Lila? You're weird." I growled, "No time. Out. Now."

But the other doors loomed. More girls. All trapped. Eyes wide, hands gripping bars. Save them? Save Mia? Both? Time ticked. Gang upstairs. Move fast. I scratched in my notepad: *Girls save? risk.* Mia tugged my arm. "Lila, let's go." But the girl in the first cell whimpered, reaching out. My chest tightened. Leave them? Come back later? Police? Police couldn't be trusted, gang might have connections. They'd move the girls, or worse. I darted to the first cell, fumbled with the lock. "I'll get you out," I muttered, but the lock stuck, rusted shut. Boots pounded closer, shouts echoing down the stairs. Mia hissed, "They're coming!"

I glanced back, shadows on the stairwell. No time. Save Mia. Come back later. "Sorry," I choked, grabbing Mia's hand. We bolted for the exit, but the doors burst open. Black-clad figures stormed in, Haitian gang with masks and rifles. They grabbed girls, one barking, "Do not shoot the girls, take them alive!" I lunged for Mia, but a rifle butt cracked my skull, lights popping. "*HOSTAGE—TAKEN—MIA—*" I screamed inside as darkness ate me.

I blinked awake, head pounding, tied to a chair in a dusty office. Dim light seeped through boarded windows, gang voices rumbling outside. Mia sat next to me, wrists bound, her gaze fierce despite the fear. The alcohol buzz lingered, fading slow, keeping me sharp yet raw. My sage-green dress clung damp to my skin, glitter smudged from the party. I tugged the ropes, loose enough to shift but biting my wrists, wincing. "Mia," I whispered, "you okay?" She nodded, barely, then leaned close. "What's wrong with you? You're not you."

I bit my lip, the LA-girl gloss long gone. "It's the alcohol. Turns me into someone else, that personality from VR. Sharp, but crazy." Mia's hand brushed mine, warm, steady. "You're still Lila," she said, voice low. "Just... stronger." Her fingers tightened, and my heart tripped over itself. A spark flared, new and scary, not the bestie vibe I knew. I didn't pull away.

Mia leaned closer, her breath soft against my cheek, warm and shaky. "I need you," she whispered, and it wasn't just words, it was a tether, raw and desperate. I nodded, my own need echoing hers, loud in the silence. Our lips met, tentative at first, then urgent, like we were drowning and this was air. I tugged her ropes free, her wrists red but loose, and her hands slid under my torn dress, tracing my skin with a tenderness that made me ache, her touch grounding me. She wrapped her arms around me, pulling me close, her body warm against mine. The world narrowed to her touch, her warmth, the quiet sounds we made, soft gasps, whispers, the rustle of fabric. It was quick, messy, perfect, a stolen moment in the chaos, not about the act but about clinging to each other, finding comfort in the storm.

When it was over, we lay tangled, breathless, her head on my chest, my fingers tracing lazy circles on her shoulder. "What are we now?" she murmured, voice barely above a whisper, fingers brushing my arm. I kissed her forehead, no answers, just the steady beat of her heart against mine. The room felt smaller, quieter, but for a moment, we were safe in each other's arms.

The next day, the air hung heavy, thick with dread. The door flew open, a gang guy swaggering in, eyes glinting mean. "Boss wants a treat," he sneered, grabbing Mia. "No!" I yelled, thrashing against my ropes, the coarse fibers biting into my wrists loosened from before. She kicked, fierce as ever, but another guard grabbed me, his grip bruising, hauling me up with her. They dragged us to a back room, dim and reeking of sweat and smoke, the walls stained and peeling. The boss sat sprawled on a couch, a gold-toothed grin splitting his face, his presence suffocating. "Two for one," he chuckled, standing, his boots heavy on the floor. His guards shoved us forward, hands like vices on our arms, pinning us in place.

He stepped close, his breath sour, fingers trailing Mia's jaw, slow and deliberate. She jerked back, spitting, her eyes blazing defiance. He laughed, cold and sharp. "Feisty. I like that." His hand slid lower, brushing her collarbone, and I lunged, screaming, "Don't touch her!" A guard's fist cracked against my skull, stars bursting behind my eyes, pain blooming sharp and bright. The world tilted, then blackness swallowed me whole.

I woke back in the office cell, head throbbing like a drum, mouth dry and tasting of copper. The room was dim, the air stale, and my body ached, ribs sore, wrists raw from ropes, a dull pain radiating from my temple. My tank top hung loose, one strap snapped, the fabric stretched and stained. Mia huddled beside me, her dress torn at the shoulder, the hem frayed and uneven. Fresh bruises bloomed on her neck, purple and angry, and her arms bore red marks where hands had gripped too tight. Her eyes were glassy, staring at nothing, her face pale and hollow, like she'd retreated somewhere deep inside.

I scooted closer, ignoring the sharp pain in my side. "Mia," I whispered, voice cracking, raw and ragged. She flinched, then softened, her gaze flickering to me, haunted but alive. "I'm here," I said, reaching for her hand, my fingers trembling. She gripped it tight, her nails digging into my palm, grounding us both. "It was bad," she choked out, her voice barely a whisper, thick with unshed tears. "I know," I murmured, pulling her against me, her head resting on my shoulder. "But we're still here. Still us." She nodded, tears spilling, hot and silent, soaking into my torn top. I held her close, fury and love burning equal in my chest, the weight of what happened pressing down on us, unspoken but understood. "We're gonna get out," I said, voice shaky but fierce. "And they'll pay." Mia's hand tightened in mine, a silent promise, and for a moment, amidst the pain and the wreckage, we were whole, holding onto each other like an anchor.

Days smeared together. Scraps of food, gang taunts, but mostly they ignored us. Mia stayed close, her fire flickering back. One night, her lips found mine, soft and urgent, like she needed to feel something alive. I kissed her back, no white male lust, just me, raw and real. "What is this?" she murmured, breath warm. "I don't know," I said, "but I need you too." It felt right, then wrong. Sober me loved her as a friend, white male me wanted more. I couldn't untangle it.

Then, dumb luck: a gang guy tossed me a beer, smirking. "Chill out, princess." I caught it, silver can glinting. Mia's eyes widened. "Lila, don't," she said, too late. I cracked it, gulped, and the white male in me roared awake. "*ESCAPE—NOW—PLAN—*" I screamed inside, mind slicing through the fog of reality. My senses snapped sharp, every shadow a clue, every creak a threat. We weren't tied, sloppy guards, cocky. I scanned the room: desks, chairs, a flickering light, a door ajar. Mia huddled close, her breath shaky. "Follow me," I whispered, voice low, controlled. She nodded, trusting but scared.

I crept to the door, peeked out. Hallway empty, fluorescents buzzing. First floor, guards near stairs. I scratched in my notepad: *Stealth down exit.* We slipped out, hugging the walls, my boots silent on the tile. Mia's sandals scraped once, and I froze, but no one came. We ducked behind a filing cabinet as a guard strolled past, humming off-key. Lazy. Good. We waited, then moved, slipping into the stairwell. Each step echoed like a gunshot in my skull. Too loud, trap? But we made it to the second floor, shadows stretching long.

A locked door blocked the way. Keycard needed. I rifled a nearby desk, finding one under a coffee cup. Swiped it, but the lock beeped loud, red light flashing. Alarm, shit. Boots pounded from above, shouts cutting through. "Do not shoot the girls, take them alive!" a voice barked. Mia gasped, and I grabbed her hand, yanking her down the hall. We burst into an office, slamming the door. My eyes darted, a machete stabbed into a glowing monitor, strange symbols carved on the blade pulsing with eerie light bouncing off the screen. I snatched it, the weight heavy, familiar. "Stay back," I growled to Mia, who nodded, pale.

Door splinters, guards pour in. Swing blade, air whistles, then flesh tears. Blood sprays, hot, splatters my face, wall, floor. Skull cracks, wet cardboard sound. One down. More come. Paranoia spikes. Faces warp: MLK's glare, stern, then Obama's grin, twisted. Not real. Swing again, machete bites deep, neck snaps, gore slicks my hands. MLK charges, fists up, I slash, catch his arm, blood gushes, he staggers back roaring justice. Obama steps in, calm dodge, I lunge, blade grazes his chest, he laughs cold, calculated. Guard lunges, spin, slash throat, blood arcs like a fountain. Body hits floor, twitches, red pools.

Room blurs, motion, madness. Another charges, face shifts to Nelson Mandela, wise, weathered, eyes hollow, predatory. "*CONSPIRACY—LIES—TRAP!—*" rips from my throat, blade arcs down, cleaves shoulder. He staggers, grins, blood bubbles between teeth. Lunges again. Twist, dodge, swing sideways. Catches ribs, he crumples, face flickers between Mandela and a stranger. Unknown. Not cataloged. "WHO—YOU—SPY?—" Voice cracks, raw, loud. No answer. "Stop it!" I shout, voice breaking. "Stop looking at me like that!" They don't stop, never stop. Another guard, face melts into Malcolm X, glare intense. Voice cutting through my head: "You're the problem." Swing wild, machete hits temple, he drops like stone, voice lingers, bounces off walls, taunting. I pivot, slash again, catch his arm as he rises, blood sprays, he falls silent.

Room's a mess, screams, splintering wood, blood stink thick. Breathing hard, arms shake. Can't stop. They keep coming, faces shift, bodies relentless. Guard with Kanye West's smirk swings baton, I duck, air rushes past. Retaliate, machete upward, guts him, gasps, smirk falters. Yank blade free, blood sprays chest. "Not real!" I scream, hoarse. "None of you are real!" But blood's real, warm, sticky, bodies real, heavy, lifeless. Another guard, face shifts to Muhammad Ali, confident grin. Moves like a boxer, dodges swings easy. Swing again, he sidesteps, laughs. "Float like butterfly," he taunts. Lunge desperate, catch him this time, machete sinks into side, he grunts, grin falters. Twist blade, drops to knees, face flickers between Ali and a stranger. Yank free, he collapses, blood pools.

Silence now, save ragged breathing. Bodies litter floor, faces frozen in pain, disbelief. Look at hands, slick with blood. Nausea hits. What did I do? Who did I kill? Then, him. Doorway. Barack Obama, calm, composed. Steps forward, hands raised, peace gesture, eyes cold, calculating.

"It's over," he says, steady. "Put the blade down." Shake head, tears stream. "You're not real. Not him." "I'm as real as you want me to be," he replies, steps closer. "But this ends now."

Grip machete tight, heart pounds. He's lying, all part of the conspiracy, nightmare. Can't trust. "*LIAR—SETUP—TRAP!—*" Charge, swing with all strength. He sidesteps, fluid, precise, grabs my wrist, twists. Machete clatters, I stumble, legs give out. He catches me, grip firm, not unkind.

"It's okay," he whispers, soft. "It's over." But it's not, never over. Look into his eyes, truth hits hard. Not real, none of this real, neither am I.

Mia screamed, backing into a corner, eyes wide with horror. Then, bang. Loud, sharp. Guard grunts, falls off me, blood seeping from chest, eyes blank. Mia stands, shaky, holding a pistol, smoke curling from barrel. Grabbed it from a dead one. "Lila, up!" she yells, voice trembling but fierce. I gasp, lurch to my feet, arm stinging, ribs screaming. She shot him, saved me. "*MIA—GUN—FREE—*" I scribble mentally, no time for notepad now. I growl, lunge for stairwell.

We bolt, stairwell dark, steps slick with spilled beer, blood trailing behind. Feet pound concrete, hers slap, mine thud. Third floor, empty. Second, voices echo, but we duck behind crates, breath held. First floor, exit's there, glass door cracked, night air seeping in. Notepad slips from pocket, pages soak red. No time, keep moving. Push through, glass crunches underfoot, cool breeze hits hard. Outside, parking lot, shadows stretch long, cars gleam under streetlights. No guards yet, quiet, too quiet. "*TRAP?—RUN—NOW—*" Mind races, paranoia spikes, but Mia grabs my hand, pulls me forward.

We sprint, past the hotel, into the alley, gravel bites my soles. Her dress flaps torn, my tank top sticks wet with blood, sweat. Lungs burn, keep moving. City lights blur, neon, headlights, horns faint. Turn corner, hide behind dumpster, panting hard. Mia's grip tightens, her eyes wild but steady. "We're out," she whispers, voice raw. I nod, chest heaving, alive, free, together. For now.

\section{Rolling Through Debris}

The air in Mia's loft hung heavy, thick with dust and the faint tang of spilled wine from last week's chaos. I stumbled in, my boots crunching over broken glass, and slung my tote onto the couch. Mia was already at her closet, pulling out essentials: a stack of clothes, a wad of cash, her qipao, that stunning red silk piece embroidered with gold dragons, a tether to her Shanghai roots. She folded it with trembling hands, like it might vanish if she let go. I rummaged through the wreckage for my charm bracelet, spotting its tiny golden sun pendant peeking out from under a pile of crumpled sketches. My fingers closed around it, a small anchor in the storm. The loft was a disaster, overturned chairs, gutted drawers, that flickering neon "Good Vibes" sign on the wall glowing like a cruel joke now.

I froze, staring at it. Months back, when Mia moved in, this place was a different kind of mess, boxes stacked high, tape peeling, our laughter bouncing off bare walls. We'd hit a flea market that weekend, hunting for deals, and spotted those signs, two for the price of one. "Good Vibes," they screamed in pink neon, cheesy but perfect. "One for me, one for you," Mia had grinned, tossing her hair, Shanghai flair in her smirk. We lugged them home, giggling, tripping over packing peanuts, swearing they'd light up our lives. Now mine hung in my apartment, hers flickered here, a matched pair from a cleaner chaos.

"We're gone, babe," I said, voice quivering but edged with steel, snapping back to now. "San Gabriel Mountains. Secluded. Safe." Mia nodded, zipping up her bag, but her eyes darted to the shadows. Her parents' mafia connections loomed over us, a noose tightening. We had to move.

The door creaked, slow and deliberate, my heart slammed against my ribs. Ethan stepped in, his surfer-boy charm replaced by a predator's stare, cold and unblinking. His sleek silver watch caught the dim light, too techy for a beach bum. "Leaving so soon?" he purred, but his tone sliced like glass. Mia stiffened, clutching her bag. I squared my shoulders. "Back off, Ethan. We're done playing."

He smirked, stepping closer, his elbow clicked, a faint, unnatural sound. "You don't get to walk away." I snatched a lamp from the floor, chucked it at his head. He dodged, too fast, his body pivoting with eerie precision. Mia grabbed a vase, swung, but he sidestepped, fluid yet stiff, like a machine. His eyes flashed, a metallic glint, gone in an instant. Not right. Not human.

He lunged, I bolted for the kitchen, pulse roaring. My hand grazed a bottle, tequila, half-empty, glinting, half-empty, half-weapon. His boots thudded behind me. No time to think. Twisted the cap, gulped it down, fire exploded in my chest. The world sharpened, fractured. White male in me woke up. "*ETHAN—ROBOT?—KILL—*" screamed my brain, loud and jagged. I smashed the tequila bottle over his head, glass rained down, liquor splashed, a whirr sputtered from his neck. Spun, hurled a chair at him, it cracked against his side, wood splintering, he barely flinched. Too tough. Metal inside.

He grabbed me, fingers like steel clamps, cold and unyielding. I snarled, slammed my forehead into his nose, a dull crunch, no blood, just a hollow clang. Robot. Fact. I wrenched free, snatched a jagged glass shard from the floor, slashed his chest. Fabric ripped, exposing sparking wires, metal plates gleaming under fake skin. Real. See it. Stabbed again, he caught my wrist, twisted until I screamed, pain flared, white-hot.

"MIA—GO!—" I roared. She hesitated, eyes wide, bolted for the door. Ethan tossed me into the wall, plaster buckled, my ribs ached, he charged after her. I staggered up, tequila blazing, tackled him. We hit the ground hard, rolling through debris. He swung, fist cracking my jaw. Blood flooded my mouth, stars burst. I spat, grabbed a broken chair leg, smashed it into his shoulder. Metal groaned, sparks flew, his arm hung limp. He lunged, relentless, watch beeping shrill, urgent. Calling someone?

I grabbed the "Good Vibes" sign, ripped it from the wall, shoved it in front of me as he swung again. His fist punched through, neon flared, electric shock jolted him. Circuits popped, his body jerked unnatural, limbs twisting inhuman, flung him across the room. Smoke curled, silence fell, he lay still, twitching faintly. Panting, I tore his shirt wider, saw wires, circuits, a robotic core, then blinked, just blood, torn flesh, a dead man. Sober doubt crept in, was that real?

"Move. Now," I rasped, snagging our bags. Mia nodded, pale but moving. We stumbled to Ethan's ride, a sleek black beast, dashboard glowing with tech we didn't understand. Stolen, risky, but ours. We peeled out, LA's glitter shrinking in the rearview as dawn crept over the San Gabriel Mountains. The drive was a blur, city lights fading, roads twisting, pines looming tall and dark against a pink-streaked sky.

We stopped in a secluded clearing, stars dimming overhead. Hands shaking, we pitched a tent under the pines, the air crisp and quiet. I dug out a granola bar, split it with Mia, the crunch grounding us. Exhaustion clawed, tequila's edge softened, I leaned in, kissed her, soft, slow, tasting dust and defiance. She froze, then melted into it, hands light on my bruised cheeks. The buzz slipped away fully, I pulled back, smiling. "You're my bestie, babe." She laughed, shaky, we hugged, fierce and tight, friendship a tether. We crawled into the tent, sunrise spilling gold through the trees. Sleep took us, safe for now, but Ethan's wires, or was it blood, flickered in my mind, a riddle unanswered.
\end{document}