\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{The Glitch}
\author{}
\date{}

\begin{document}

\maketitle

\section*{As Usual at This Time}

I walk by the corner store—same as every day. It’s 8:47 a.m. I checked my watch twice because the second hand twitched. \textit{Or maybe my eyes are messing with me again.} There’s this Jew behind the counter. \textit{Why’s he staring like that?} His eyes are narrow—slicing through me like I’m hiding something I don’t even know about. I scribble it in my notebook: black leather, 5x7, tucked in my left coat pocket because the right one’s got a hole from that fence last Tuesday. His name tag says \textbf{Eli}—but that’s fake, right? \textit{They never use real names. Too dangerous.} He’s polishing a glass with a rag filthier than the counter. I note that too.

I don’t stop. Not today. I keep walking—head low—because if I pause, he’ll talk. I’ll answer—and he’ll know. \textit{Know what? No clue. Something.} My sneakers—gray with the left lace fraying—scrape the pavement. I count sidewalk cracks: one, two, three—then stop at four. \textit{Four’s bad. Too neat, too trapped.} I write it down. The air’s thick with burnt coffee and diesel from a truck across the street: blue cab, rusty fender, plate starts with K. \textit{K for “keep watching,” maybe.} Driver’s slouched—cap low. \textit{Binoculars?} I jot it: \textit{Truck, blue, K-plate, possible surveillance.} My pen’s dying—scraping instead of flowing. I need a new one—but not from \textbf{Eli}’s store. \textit{He’d rig it with a tracker.}

I turn left at the intersection—always—because routine’s my shield. Change it—and they notice. \textit{Who’s “they”? I’ll figure it out.} My notebook’s at 73 pages—single-spaced, front and back—since October 20th, 2024. That day—the streetlight flickered three times—not two. \textit{That’s when it started.} I wrote it then—and I’m still writing.

Up ahead—a woman walks with a black mutt—scruffy—pulling the leash. She’s in a red coat—too loud—screaming for attention. Mid-30s, bun, glasses like she’s faking smart. She nods at me. \textit{A nod?} I don’t know her. I flip back: October 28th—yellow scarf woman; November 14th—stroller lady. No red coat. New face. I write: \textit{Woman, red coat, black dog, nodded, 8:53 a.m.} The dog barks once—sharp. \textit{A signal?} I don’t look back. \textit{Looking back is fear—and I’m not afraid.} I’m watching.

The bus stop’s next. I don’t ride. \textit{Too many eyes.} But I check the schedule daily. It’s laminated—curling at the edges. Bus 42 is due at 8:55 a.m. It’s 8:56 now—and it’s not here. \textit{Late? Canceled? Tracking me?} I note: \textit{Bus 42, late, possible deviation.} An old man sits on the bench—hunched—newspaper in hand. He doesn’t look—but his fingers grip tighter. \textit{Faking it.} I write: \textit{Old man, newspaper, tense grip, 8:56 a.m.}

I keep going. My apartment’s six blocks away—12 minutes flat—14 if I dawdle. I won’t. Wind kicks up—leaves rattling—and a car horn blares two streets over: short, sharp. \textit{Code?} I’ll crack it later. I scribble: \textit{Horn, two streets west, single blast, 8:58 a.m.} My pen’s toast. Ink’s a ghost. I’ve got a pencil at home. \textit{Safer—no spills.}

Passing the alley behind the Chinese joint—it stinks. Trash—or worse. Two guys lean against the wall—hoods up—hands buried. One’s got a tattoo—dragon or snake—sneaking up his neck. They don’t look—but I feel it. I jot: \textit{Two men, alley, tattoo, 9:00 a.m. Gang vibe?} \textit{Maybe.} I’ll keep it in mind.

Next block—the old bookstore has a faded sign and grimy windows. There’s a new poster: “\textbf{A. Gore}, climate justice.” Half the name’s smeared—but I get it. \textit{Another jab at me: white, male—the world’s villain.} I write: \textit{Bookstore, Gore event, guilt push, 9:02 a.m.} Not my guilt. They shove it on me. \textit{Everywhere now—that blame.}

My building’s ahead: gray brick—four floors—buzzer’s shot. It’s 9:10 a.m. I scan my window—third floor, second left. Curtains still—but I squint. \textit{Shadow? Nothing?} I note: \textit{Window check, no movement, 9:10 a.m.} The lobby reeks of mildew and stale smoke. Mailbox 3B—mine—has a fresh scratch—diagonal—new since yesterday. I trace it—sharp under my finger. \textit{Marked.} I write: \textit{Mailbox 3B, new scratch, diagonal, 9:11 a.m.}

I take the stairs—not the elevator. \textit{Traps are for suckers.} It’s 28 steps to the third floor—always. My key turns twice—and the door eases open. Quiet inside. \textit{Too quiet?} I listen: clock ticks 9:13—fridge hums low—muttering. I write: \textit{Apartment entry, quiet, clock and fridge audible, 9:13 a.m.} Locks check out—chain’s on. For now.

At the table—wood, scratched, and wobbly—I grab the pencil: yellow, sharp. I start transcribing. Every detail—every hunch. The Jew—the dog woman—the late bus—the scratched mailbox. It’s all linked. I’ll connect it. They watch me—but I watch back. Proof’s here—in ink and lead—piling up page by page.

\section*{Quieter Than Yesterday}

February 21, 2025. 7:32 a.m. I wake up to the sound of dripping—slow and deliberate—like a metronome set to torment me. It’s coming from the bathroom sink—even though I tightened the faucet last night—three full turns with the wrench I keep under the sink. I checked it twice before bed and noted it at 11:47 p.m.: \textit{Faucet secured, no drip, wrench back in place.} Now it’s leaking again. \textit{Someone’s been here.} I grab the black leather 5x7 notebook—pencil still sharp from yesterday—and write: \textit{Drip started overnight, faucet tampered, 7:32 a.m.} I don’t fix it yet. I listen instead. Drip. Drip. Drip. Three seconds apart. \textit{A signal?} I count ten drops and stop—because eleven feels too complete—too final.

I don’t leave through the front door today. \textit{My routine’s compromised after the mailbox scratch;} someone knows my path. I take the fire escape instead—third floor—rusted rungs cold under my hands. The alley smells like wet cardboard and something sour—maybe rotting fruit from the dumpster. I scan the ground: cigarette butts—a candy wrapper—a feather. \textit{A feather?} Black—small—curved like a crow’s. I pick it up with my sleeve—not my fingers—and tuck it into my pocket. \textit{Evidence.} I write: \textit{Feather in alley, black, possible marker, 7:39 a.m.} \textit{Crows don’t just drop feathers. They’re messengers.} I’ll look that up later.

The street’s quieter than yesterday—no truck—no dog. I head east instead of west—toward the canal—less foot traffic—fewer eyes. My boots crunch on gravel—brown lace-ups—scuffed toes—and I notice the pebbles are uneven—like someone scattered them on purpose. \textit{A trail?} I crouch and inspect them: small—gray—some wet despite no rain overnight. I write: \textit{Gravel by canal, wet, arranged, 7:46 a.m.} Then I see it—a glint in the water—ten feet out. Metal—maybe glass—catching the sun. I squint—but it’s too far to tell. \textit{Binoculars would help—but I don’t have them.} Whoever’s watching probably does. I note: \textit{Object in canal, reflective, 7:48 a.m.}

A barge drifts by—slow—its engine rumbling low like a growl. The man steering it—bald—bearded—wearing an orange vest—stares straight ahead—but I see his hand twitch on the wheel. \textit{He’s avoiding me. Why?} I don’t know him—but he knows something. I write: \textit{Barge man, orange vest, twitchy hand, 7:51 a.m.} The water ripples behind him—and I count the waves: five—six—seven—before they fade. \textit{Seven’s a power number—too strong—too intentional.} I don’t like it.

I keep walking along the canal path—concrete cracked and mossy—until I reach the bridge. It’s old—iron—painted green but peeling in strips like shedding skin. There’s a lock on the railing—brass—shiny—no rust. New. I stop and stare at it. \textit{No one puts a lock here.} It’s not a lover’s bridge or a tourist spot. I touch it—cold and smooth—and feel a faint hum—like it’s alive. My pencil scratches fast: \textit{Lock on bridge, brass, new, humming, 7:59 a.m.} I look around—nobody—but the air feels thick—like it’s holding its breath. Then I hear it: a click—sharp—from under the bridge. I freeze and write: \textit{Click from below, source unknown, 8:00 a.m.}

I don’t go under. \textit{Too risky.} I backtrack instead—fast—past the barge—gone now—and the glinting thing in the water—still there—mocking me. My heart’s thumping—but I keep my steps even: four paces—pause—four paces—pause—so they won’t know I’m rattled. In the alley—I spot a marking on the wall—spray-painted—fresh—a half-moon with an arrow through it. Not there yesterday. I jot it down: \textit{Wall marking, half-moon with arrow, new, 8:05 a.m.} \textit{Could be a tag—could be a sign.} I’ll check my notes later for patterns.

Back in the alley—I climb the fire escape—check the feather in my pocket—still there but bent now—and slip inside. 8:14 a.m. The drip’s stopped. \textit{Stopped?} I run to the bathroom and stare at the sink. Dry. Not a drop. I didn’t fix it. I write: \textit{Drip gone, unexplainable, 8:15 a.m.}

Before sitting down—I glance out the kitchen window. A figure stands across the street—half-hidden by a lamppost—tall—coat too heavy for the weather—face shadowed. I note it quickly: \textit{Figure by lamppost, heavy coat, stationary, 8:16 a.m.} Then he turns and slips into the crowd—gone before I can blink. I add: \textit{Figure vanished, 8:17 a.m.}

I sit at the table—wood, scratched—wobbly leg—and spread the notebook open. The feather goes next to it—flat on the page—a dark slash against the white. I sketch it quickly: curved spine—frayed edges—then start transcribing: the drip—the feather—the gravel—the canal object—the barge man—the lock—the click—the wall marking—the figure. It’s not random. It’s a sequence—a message—a map. The dripping was a wake-up—the feather a pointer—the lock a key—literal or not—I’ll find out. They’re closing in—tightening the net—but I’m ahead. I’ve got the pieces—right here—in pencil and paper. I’ll decode it before they do. I have to.

\section*{Then a Third}

March 23, 2025. 4:17 p.m. It’s been weeks since I left the apartment—27 days—noted on page 89: \textit{Last outing, February 24, minimal contact, safe return.} Too much has piled up: the feather’s still on my table—shedding tiny barbs; the lock’s hum echoes in my skull; the drip started again three nights ago—irregular now—tapping out \textit{“they’re back”} in a code I can’t crack yet. I had to go out today—supplies low—no pencils left—just stubs too short to grip. I take the front door this time—no fire escape—because the alley’s too exposed after the last snow melted and left tracks I didn’t make. Notebook’s in my left pocket—5x7—pages curling from sweat and overuse. I lock the door—twice—chain on—and step into the street.

The city’s wrong. It’s swollen—buzzing—loud—pre-holiday madness—Easter or something—I don’t track calendars anymore. People swarm—elbows jabbing—bags swinging—voices clashing like static—boots churning slush into black streaks on the pavement. I write: \textit{Crowds, holiday prep, 4:19 p.m.} Red and yellow ribbons stretch across lampposts—dangling like nets ready to drop. A woman brushes past—green scarf—bracelets jingling—muttering “eggs, eggs, eggs” in a staccato rhythm. \textit{A signal?} I squint at her—then at the store windows: baskets—pastel colors—fake grass. \textit{It’s a cover—a distraction.} I note: \textit{Egg talk, possible code, 4:21 p.m.}

I head for the stationery shop—three blocks north—but the street’s clogged. A man in a rabbit costume—white—floppy ears—sign in hand—stands by a cart—handing out candy. His mask hides his eyes—but I feel them lock on me—mechanical—unblinking—like he’s programmed to track. \textit{Why a rabbit?} I write: \textit{Rabbit man, candy, observing, 4:24 p.m.} Kids swarm him—laughing—sticky hands grabbing. One drops a wrapper—shiny purple—landing near my boot. \textit{Could be laced—tagged—a plant.} I step over it—keep moving.

The air’s thick with cinnamon and exhaust—street vendors frying dough—shouting prices in monotone loops. A bell rings—sharp—from a church two streets over. Then another. Then a third. Three bells—uneven—like that night the streetlight flickered before it all started. I stop—pencil shaking—and write: \textit{Bells, three, staggered, 4:27 p.m.} \textit{A countdown.} My chest tightens. I push forward—past a woman with a stroller—twins staring at me—eyes glassy and fixed—and a guy on a phone—whispering fast. He says “package is close” twice—voice flat—like a script. I catch it and write: \textit{Man on phone, ‘package is close’ x2, 4:29 p.m.} \textit{For me? Has to be.}

The stationery shop’s ahead—but the crowd’s a wall—shoulders—hats—breath fogging the air. A horn blares—a white truck—no markings—cuts me off. The driver leans out—yells something garbled—cap low like the February guy—no K-plate now. I write: \textit{Truck, white, no plate visible, aggressive, 4:32 p.m.} The crowd shifts—shoving me sideways—notebook nearly slipping. I clutch it—heart hammering. \textit{They’re herding me.}

I turn back—home’s safer—but the street’s a maze now. Lights flicker on—strings of bulbs over doorways blinking in the drip’s rhythm. A carol starts—tinny—off-key—piped through hidden speakers—“peace on earth” warping into something I swear I’ve heard in a dream. I write: \textit{Lights blinking, carol, unnatural, 4:35 p.m.} A kid runs past—red balloon bobbing like a flare. It pops—loud. I flinch. Laughter ripples from behind—sharp—familiar—like the old man’s grip on the newspaper. I spin—but faces blur—too many—too close. I write: \textit{Balloon pop, laughter, targeted?, 4:37 p.m.}

Two blocks from home—every step’s a fight. A woman drops a bag of groceries—oranges roll—one hits my foot. I kick it away—hard. She glares—mutters something foreign—maybe “your fault” or “white trash”—\textit{did she mean me?} I can’t tell—but the guilt stings anyway—the kind they shove at you on every billboard. I write: \textit{Orange drop, intentional, foreign words, guilt jab?, 4:40 p.m.} The bells ring again—four this time. Four. I hate four. My head pounds—sweat stings my eyes. The rabbit man’s back—or another—same costume—ten feet away now—still as a mannequin—staring. I write: \textit{Rabbit man again, closer, stationary, 4:42 p.m.}

One block left. The crowd thins—but the air’s heavier—smoke or something chemical. A drone hums overhead—small—black—hovering right above me—lens glinting—then darting off between buildings. I freeze and write: \textit{Drone, black, circling, 4:44 p.m.} \textit{They’ve escalated.} My legs shake—but I force them forward. Home’s in sight—gray brick—four stories—but the windows glow—all of them—even mine—curtains twitching like someone’s there. I didn’t leave lights on. I write: \textit{Windows lit, intrusion, 4:46 p.m.}

The pencil snaps—lead rolls under my boot. I fumble for a stub—hands trembling—but a crack splits the air. Not a balloon—not a horn—louder—deeper—like the earth splitting. I drop the notebook—clap my hands over my ears—and everything slows: the crowd freezes—faces turn—the rabbit man tilts his head. My vision blurs—white—then black—and I’m falling—knees hitting pavement—notebook splayed open beside me—pages flapping like wings. Then nothing.

\section*{Like Mine but Torn}

March 23, 2025. Time unknown. I wake up—head throbbing like a drum—lights too bright—white—buzzing—stabbing my eyes. I’m on a bed—stiff sheets—metal rails. Hospital. \textit{How?} Last thing was the notebook falling—that crack splitting the air—pavement rushing up. I sit up fast—hands patting my coat—left pocket empty. Notebook’s gone. My chest tightens—breath catches. \textit{They took it.} The Jew from the corner store—the rabbit man—the drone—someone. I scan the room: pale walls—a tray with a cup—a window too high to reach. No clock—but the light’s dim outside—dusk maybe. \textit{I need to write. I need it back.}

I swing my legs off the bed—bare feet hitting cold tile—and check the bedside table: drawer’s empty—just dust and a bent paperclip. No notebook. My coat’s on a hook—gray—sleeve torn from the fall—but the pocket’s flat—searched. I dig anyway: lint—the feather’s barb still clinging—no 5x7 leather. \textit{Stolen. Evidence gone.} My hands shake—but I spot a red marker on the tray—cap scratched—and rolls of gauze stacked beside it—white—coiled—clean enough. I grab them—tear strips—and scribble across them: \textit{Woke in hospital, notebook missing, dusk?, red log started.} I wrap the gauze around my arms—chest—legs—words pressed under my coat—a full-body record—ink bleeding faintly through. \textit{It’s messy—strange—but it’ll do.}

Voices murmur outside—low—muffled—feet shuffling in loops. I crack the door: hallway—fluorescent flicker—a nurse at a desk—head down. She’s pale—fingers drumming slow—uneven—like she’s stuck in a pattern. I twist my wrist—write on the gauze: \textit{Nurse, pale, odd rhythm, time unknown.} I need out. Home’s safer—gray brick—locks I trust. I slip into the hall—coat pulled tight—red marker tucked in my fist. Signs point left: Elevator, Floors 1-3. Right: Stairs, Floors 4-6. I’m on 4—farthest from the exit. \textit{Planned—probably.} I choose stairs; \textit{elevators trap you—always have.}

Floor 4’s quiet—too quiet. A janitor mops ahead—slow—head tilted—dragging the handle like it’s scripted—like he’s resetting for the next pass. His eyes don’t lift—jaw slack—lips wet. I write: \textit{Janitor, slow, slack face, Floor 4.} I edge past—back to the wall—down the stairwell. Concrete’s cold—steps echo soft. A light buzzes—stutters: off—on—off. I note: \textit{Light flicker, Floor 4 stairs.} Halfway down—a man ascends—suit—tie loose—swaying stiffly. He grunts—low—guttural—like something’s stuck in his throat. I freeze—then sidestep. His hand brushes the rail—nails cracked—skin grayish. I write: \textit{Man, gray skin, grunt, Floor 3 stairs.} \textit{Something’s off—but I keep moving.}

Floor 3’s busier; patients shuffling—a doctor with a clipboard—all slow—like they’re on a loop. The doctor’s head jerks—sharp—then still—eyes locked ahead too long. I write: \textit{Doctor, twitch, Floor 3.} Air’s thicker here—sour—meaty—clogging my nose. I pull my collar up—breathe shallow. Exit’s two floors down—but the stairwell’s blocked: a cart—tipped—sheets spilled. I duck into a hall instead—past a woman in a gown—staring at nothing—drooling thin—her shuffle a perfect repeat. I write: \textit{Woman, drool, blank eyes, Floor 3.} My gauze is crowded; I tear another strip—wrap it higher: \textit{Continued log, Floor 3, air sour.}

A supply closet’s ahead—door ajar—dark inside. I slip in—find a shovel—wood handle—rusted blade—propped against a shelf. Heavy—but mine now. I note: \textit{Shovel acquired, Floor 3 closet.} Back in the hall—the doctor’s closer—clipboard dangling—mouth gaping—teeth yellow—jagged. I dodge left—toward the stairs. Floor 2 now—lights dimmer—a nurse stumbles past—arm dangling—skin peeling at the elbow—her steps too even—like she’s coded to roam. I write: \textit{Nurse, peeling, Floor 2.} \textit{Dots connect slow: pale—slack—gray—drool.}

Stairs to Floor 1—almost there. A man blocks the landing—big—orderly maybe—swaying—eyes milky—like a boss mob I’d flank. He moans—soft—then loud. I grip the shovel and write: \textit{Man, milky eyes, moan, Floor 2 landing.} He lunges—slow—clumsy—but I swing anyway—instinct kicking in. The blade cracks his skull—wet crunch—and he drops—twitching once. Blood’s black—thick—not right—like the gore filter in a game. Then it hits: not human—not anymore. \textit{Zombies.} All of them—bleeding from my old gaming runs into this nightmare. I write—hands shaking: \textit{Orderly, zombie, killed, Floor 2, shovel hit.} No time left—exit’s close—but they’ve seen me now.

\section*{Buzzer Still Broken}

March 23, 2025. Time still unknown—dusk fading. I’m out—hospital doors behind me—glass shattered—no alarm. Shovel in hand—blade sticky with black blood from the orderly. Floor 1 was a blur: two more came at me—a patient with one arm dangling—a guard with half his face gone. I swung twice: first hit cracked the patient’s jaw—second split the guard’s neck. They dropped—gurgling—not human anymore. I scrawled it fast on the gauze—wrist cramped: \textit{Patient, one arm, killed, Floor 1 / Guard, half face, killed, Floor 1, shovel hits.} No time to think—exit was there—and I took it.

Outside’s worse. The city’s dead but moving. Holiday lights blink—red—yellow—some smashed—casting shadows that twitch. Cinnamon’s gone; air’s rot now—thick—wet. I crouch behind a dumpster—green—dented—leaking something dark—and scan: street’s empty—then not. Shapes shamble—three—maybe four—near the vendor carts—dough cold—flies buzzing. I tear more gauze—wrap it higher on my arm: \textit{Escaped hospital, city rotting, 3-4 figures, dusk.} Shovel’s heavy—but I grip it tighter. Home’s six blocks south—gray brick—my locks—safe if I make it.

I move—low—along the alley—wet cardboard underfoot—quieter than pavement. A moan cuts through—left side. I freeze. It’s the rabbit man—costume torn—one ear missing—candy scattered around him. His mask’s off—face gray—eyes sunken—mouth dripping. He lurches—slow—but toward me. No choice. I swing—shovel catches his temple—skull caves in—he flops like a puppet cut loose. I jot it: \textit{Rabbit man, zombie, killed, alley, shovel hit.} Black blood splatters my coat—sleeve now. I wipe it on the wall—keep going.

Two blocks down—hiding’s harder. Street’s wider—lights flicker worse: on—off—on—like a signal I can’t read. A car’s stalled—door open—driver slumped over the wheel. She twitches—head snapping up as I pass—hair matted—teeth bared. I don’t wait. Shovel arcs down—cracks her crown—she slumps again—still. I record it—gauze tight against my skin: \textit{Driver, female, zombie, killed, street, shovel hit.} My arm aches—but I write it. Two kills now outside—four total. \textit{Patterns matter.}

Block four—I duck into a shop—stationery—irony not lost. Shelves tipped—pens spilled—no notebooks. A shuffle from the back: clerk—glasses cracked—dragging a leg. He groans—louder when he sees me. I sidestep—swing low—shovel takes his knee—then up to his head. He crumples—glasses skittering. I scribble: \textit{Clerk, zombie, killed, shop, shovel x2.} I grab a pencil—red—unsharpened—from the floor—shove it in my pocket. No time for more—moans echo outside—closer.

Last two blocks—I stick to shadows. Holiday ribbons hang limp—shredded—some stained dark. A kid’s balloon—red—deflated—rolls past—carried by wind that smells like death. I hear shuffling—too many feet—but I’m near—gray brick in sight—four stories—my window dark. Relief’s cut short: a figure staggers from the stoop—big—coat like mine but torn—the same one I glimpsed in the lobby weeks ago—always lurking near the mailboxes. Neighbor—maybe—or was. He turns—eyes white—jaw unhinged—and lunges. I swing hard—shovel bites his neck—nearly severs it. He falls—wet thud. I note it: \textit{Neighbor?, zombie, killed, stoop, shovel hit.}

I stumble to the door—buzzer still broken—good sign—and fumble the key. Inside—up the stairs—28 steps—counting keeps me sane—I lock myself in: deadbolt—chain. Apartment’s untouched—table scratched—feather still there—drip silent now. I collapse—shovel clattering—and unwrap the gauze: \textit{Home, 5 kills total, city overrun, time unknown.} Red ink’s smeared into my skin—lines of words bleeding under the surface—like the notes are part of me now. I pull out the pencil—sharpen it with a knife—slow—deliberate. They’re out there—shuffling—but I’m here. For now.

\section*{Symbols Staring Back}

March 24, 2025. Time unknown. I wake—curtains drawn—feather on the table—shovel by the door—then a crash. Door splinters—wood flies—and the back of a police shotgun swings at my face. Black steel—barrel scratched—too fast to dodge. It hits—cheekbone cracks—I’m down—sprawled on the floor—blood hot in my mouth. No gauze—no pencil—hands empty—coat torn off me in the fall. Can’t write. I yell notes to the universe: \textit{“SHOTGUN—POLICE—BROKE IN—FACE HIT”} Voice raw—echoing off walls. They’re here—finally—masks off.

Boots stomp—two—three pairs?—and I analyze: heavy tread—deliberate—not zombie-shuffle. A voice barks—“Stay down!”—male—clipped—no accent I can place. I squint through swelling eyes: uniforms—badges glint—but faces blur. Another hit—butt of the gun—temple this time—stars burst—I scream: \textit{“SECOND HIT—TEMPAL—BADGES”} Pain’s a wave—drowning me—but I keep tracking: blood pools under my jaw—warm—sticky; floor’s cold—scuffed—same scratches from yesterday. Third hit—ribs—I curl—scream: \textit{“RIBS—THIRD—COUNTING”} Then black swallows me—no edges—gone.

Time unknown again. Eyes flutter—hospital again—different. Bed’s hard—wrists wired to rails—tight—cutting skin. I jerk—but no give. Room’s dim—machines beep—slow—off-rhythm. Figures around me—white coats—zombie doctors—gray skin peeling—eyes dull like the clerk’s—a faint shuffle like something I’ve heard before. One leans close—teeth jagged—breath like rot. I thrash—wires bite deeper—scream: \textit{“ZOMBIE DOCTORS—WIRED—TRAPPED”} No shovel—no out. They don’t flinch—just shuffle—hands steady. One holds a syringe—clear liquid—needle glints. I twist—scream: \textit{“SYRINGE—INJECTION—NO”} It pierces my arm—cold floods in—vision warps—edges soften—gray fades.

Blink. Normal hospital now—white walls—antiseptic sting mixing with a whiff of rot that fades fast—no trace left. I’m bandaged—arms—chest—gauze thick with symbols: circles—slashes—scribbles I don’t know. Doctors human again—masked—moving fast. A monitor blinks—heart rate spiking. I try to scream notes—anything—but throat’s dry—voice cracks to nothing. \textit{Injection’s working—head swims—lights pulse too bright—too real.} Consciousness slips—a slow fade—out.

Time unknown—third wake. Concrete walls—no windows—bars enclose the prison cell. I’m slumped on a cot—bandaged—symbols etched into the gauze—circles—slashes—scribbles I can’t decipher—faint under the dim light. My wrists are free—but my hands tremble—no pencil—no gauze—nothing to write with—just the itch of the fabric against my skin. A man sits across—pastor—black robe draped loose—beard patchy—eyes fixed on me—unblinking—steady as if measuring something beneath my flesh. He leans forward—voice low—deliberate—a mix of English and Slavic church tones: “My child, \textit{pokoj} be yours—peace in soul. What do you see when you close your eyes?” His words roll slow—heavy—like he’s tuning me—fishing for a signal. \textit{I don’t trust it—too precise—too probing.} I yell notes into the void: \textit{“PASTOR—PEACE—SEE—CELL”}

He nods—slight—measured—hands folded in his lap. “Good, \textit{ditko}—little one. \textit{Slava} shines—glory of light. What do you hear in this \textit{tishina}—this silence?” His tone’s calm—a cadence like he’s reciting lines—waiting for me to echo back—to give him something useful. My chest tightens—\textit{he’s digging—calibrating—not praying.} I scream—repeating his bait: \textit{“GLORY—SILENCE—HEAR”} He tilts his head—eyes narrowing just a fraction—voice steady: “Yes, \textit{molitva}—prayer rises. Tell me—what burns in your heart, \textit{ohn}?” His mix of words—half sermon—half Slavic chant—feels like he’s syncing me—pulling data from my bones.

\textit{Suspicion creeps in—why’s he asking? What’s he after?} I scream louder—notes twisting: \textit{“PRAYER—FIRE—WHAT”} He shifts—robe rustling—voice edging up: “Speak, \textit{brat}—brother! \textit{Bezpeka v dushi}—safety in soul—where is it?” His calm frays—hands unclasp—fingers twitch like he’s losing a signal. I scream back—defiance rising: \textit{“SAFETY—WHERE—TRICK”} His face hardens—eyes glint sharp—and he leans closer—breath sour: “\textit{Hovory pravdu}—speak truth! \textit{Slid grixa}—trace of sin—show me!” The church mask slips—urgency breaking through—spit flecking his lips.

I catch it—\textit{he’s not saving me—he’s mining me.} My gut twists—paranoia flares. I scream: \textit{“TRUTH—SIN—LIE”} He jolts up—robe flapping—voice spiking: “\textit{Proklyattya tebe}—curse on you! \textit{Zhertva}—victim—why hide?” His hands curl—spit sprays my bandages—calm gone to rage. I match him: \textit{“CURSE—VICTIM—HIDING”} He’s shouting now—full tilt: “\textit{Pokara}! \textit{Zlo v tobi}—evil in you! \textit{Krivda}—falsehood!”—beard quivering—robe tearing at the hem as he lurches. I scream: \textit{“PUNISH—EVIL—FALSE”}

We’re locked in it—voices crashing. He bellows: “\textit{Slava rozbiy}—glory breaks! \textit{Chort tebe}—devil take you!”—spit lands on my arm—hands flail like he’s clawing out answers. I scream back: \textit{“GLORY—DEVIL—TAKE”} He presses on—wild: “\textit{Molitva pade}—prayer falls! \textit{Pokay}—repent now!”—his eyes burn—robe frays—words tangle into a snarl. I scream: \textit{“PRAYER—REPENT—NO”} It’s a storm—no sense—just noise piling up—his fingers twist—spit stains my cot—beard shakes like static. My head pounds—symbols pulse on the bandages—or I imagine they do—no telling anymore. No escape—no record—just this—shouting into a void that shouts back—louder—madder—endless.

\section*{Stole My Ramen}

April 2, 2025. 6:13 a.m.—I think. Time’s slippery here—cell’s got no clock—just a slit window too high to see sun or stars. I wake on the cot—concrete biting through the thin mattress—bandages still on—symbols faded but there. Been days since the pastor—his Slavic yells echoing in my skull. Counted three so far: three meals of gray mush—watery and cold—three nights of no sleep—just staring at the ceiling—tracing cracks like code. Hands stopped shaking yesterday—but the need to write claws at me. Screaming isn’t enough. I yell notes to the universe: \textit{“WORDS NEED PAPER—ORDER—PROOF”} Voice hoarse—bouncing off walls—useless without ink. I trace the cracks again—seventeen jagged lines—and scream: \textit{“CRACKS—CODE—WATCHING”} No one answers—just silence and the pastor’s gibberish looping in my head.

Third day—guard bangs the bars—grunts “Library.” No cuffs—no shove—just a nod. \textit{Suspicious.} Down the hall—gray—peeling paint—lights buzzing—I find it: shelves sparse—books torn—but a notebook sits on a table—blue—spiral-bound—8x10—bigger than my old 5x7—pen clipped to it—tip dulled. No one else here—just dust and silence. I take it—no questions—mine now. First entry—scrawled fast: \textit{Prison library, day 3, blue notebook acquired, 10:22 a.m.} Feels like breathing again—pen on paper—control back. Flash of the 5x7 slipping from my pocket on that cracked pavement stings—but this’ll do.

Back in my cell—I catch up—days blurred but memory’s sharp when it matters. I write: \textit{Day 1: Pastor, Slavic gibberish, ‘proklyattya,’ screaming duel, no escape. Day 2: Silence, no visitors, mush at noon, cracks in ceiling = 17, possible pattern. Day 3: Library, notebook, this.} Then a clank—door unlocks—loud—metal grinding. I freeze—pen mid-word. No guard—no voice—just open. \textit{A test?} I jot: \textit{Cell door unlocked, no cause, 11:07 a.m.} Shove the notebook in my waistband—bandages itch under it—and step out.

Hallway’s dim—flickering bulbs—air stale with sweat and rust. Doors line both sides—cells—bars rusted—faces behind them. First one: thin guy—sunken cheeks—staring. I squint—too familiar. High school—10th grade—\textbf{Tim Grayson}—pale kid who doodled skulls in math—smirked when I flunked. Now he’s here—eyes locked on mine—hollow. I write: \textit{Cell 1, Tim Grayson, school, staring, 11:09 a.m.} Next cell: woman—curly hair—mid-20s. University—\textbf{Lena} from psych class—argued Freud was trash—pen tapping like a drum. She’s silent now—head tilted—watching. I note: \textit{Cell 2, Lena, uni psych, still, 11:10 a.m.}

Doors keep opening ahead—closing behind—clang—clang—like a machine knows I’m coming. No guards—no sound but my steps and the locks. Third cell: bald guy—glasses smudged with faint grid lines he’d mock me for missing. Job at the AI startup—\textbf{Mark}—coder—neural net freak—scoffed at my data entry gig. He grips the bars—knuckles white—staring through me. I write: \textit{Cell 3, Mark, AI startup, tense, 11:12 a.m.} Pulse quickens—past piling up. Fourth cell: big guy—beard—wild hair. World of Warcraft—clan master—\textbf{ThrummSkull}—led our guild—yelled at me for missing raids—pacing now like a raid boss loop. I scribble: \textit{Cell 4, ThrummSkull, WoW, pacing, 11:14 a.m.}

I stop—notebook out—pen flying—connections forming—too neat—too wrong. Fifth cell: old woman—hunched—knitting something gray. \textbf{Mrs. Carter}—7th-grade teacher—caught me writing notes once—called it “peculiar.” She looks up—needles still—mouth a thin line. I record: \textit{Cell 5, Mrs. Carter, 7th grade, knitting, 11:16 a.m.} Sixth: skinny kid—acne scars—\textbf{Jake}—dorm roommate—stole my ramen—laughed it off. He rocks back and forth—staring. I jot: \textit{Cell 6, Jake, uni dorm, rocking, 11:17 a.m.}

Doors keep going—open—close—open—close—leading me deeper. Seventh: suit—slick hair—startup boss—fired me for “overanalyzing”—a pin on his lapel glinting with the company logo. He leans on the bars—smirking like before. I write: \textit{Cell 7, Boss, startup, smirking, 11:19 a.m.} Eighth: blonde girl—chewing gum—\textbf{Sarah}—high school crush—never saw me. Now she does—eyes wide—gum still. I note: \textit{Cell 8, Sarah, school, staring, 11:20 a.m.} Ninth: wiry guy—tattoos—\textbf{RazorEdge}—WoW rival—trashed me in PvP. He claws the air—growling low. I scribble: \textit{Cell 9, RazorEdge, WoW, hostile, 11:22 a.m.}

Ten cells—then twenty—I lose count—notebook filling fast. Faces blend: classmates—coworkers—guildmates—some half-remembered—like the uni janitor whistling off-key—still at it behind bars. I write: \textit{Cell 14, Janitor, uni, whistling, 11:25 a.m.} Every door opens before I reach it—closes after—herding me. A guard finally—end of the hall—faceless in shadow—points right. I turn—no choice—noting: \textit{Guard, shadow, directed right, 11:29 a.m.}

New hall—more cells. Professor—\textbf{Dr. Kline}—AI ethics—droned about sentience—sits cross-legged—stare cold like he’s running numbers on me. I write: \textit{Cell 21, Dr. Kline, uni, calm, 11:31 a.m.} Next—kid from middle school—\textbf{Bobby}—threw my backpack in a dumpster—now clawing at his bars. I jot: \textit{Cell 22, Bobby, school, frantic, 11:32 a.m.} Then—chill down my spine—\textbf{Eli}—The Jew from the corner store—polishing a nonexistent glass—clink faint—same narrow eyes. He nods—slow—like he knows. I write it twice: \textit{Cell 23, Eli, store, polishing, 11:34 a.m. Eli, here, knows.}

Pages flip—half the notebook’s gone—ink smudging from sweat. Faces pile up: WoW healer who ghosted us—startup intern who spilled coffee on my desk—teacher who failed me in history. I scribble: \textit{Cell 27, Healer, WoW, blank / Cell 28, Intern, startup, twitchy / Cell 29, Mr. Hayes, school, stern, 11:39 a.m.} Doors keep moving—open—close—like a pulse—guiding me nowhere. Last cell I note: woman with the red coat—nodded at me months ago—stroking the air where her dog should be. I write: \textit{Cell 35, Red Coat, dogless, stroking, 11:45 a.m.}

I stop—breathless—notebook trembling. Every face—past—present—locked here—watching me. \textit{A puzzle—a trap—a mirror.} Why? Who? Doors clang shut behind—no guard now—just silence and eyes. I write: \textit{Faces from life, all cells, connected?, 11:47 a.m.} No answers—just the weight of it all—pressing in.

\section*{Your Decadence Birthed}

April 2, 2025. Time unknown—irrelevant now. I wake strapped—arms—legs—chest—leather biting skin—metal chair cold under me. Electric chair—wires hum—faint—like that lock on the bridge months back. No notebook—no gauze—hands pinned—can’t write—can’t grip. Panic claws—sweat pools under the straps—but I yell notes to the void: \textit{“ELECTRIC CHAIR—STRAPPED—WIRES”} Head jerks—eyes dart—room’s dim—circular—a theater of judgment. Faces in the stands—not shadows—not zombies—famous—impossible faces—staring down—judging me—one guy—white—straight—alone.

\textbf{Obama}’s first—suit crisp—voice smooth but sharp: “You redneck divider—split my nation—trashed my green agenda!” I scream back: \textit{“OBAMA—BLAMES ME—CLIMATE”} Before I finish—\textbf{Greta} cuts in—eyes blazing—fists clenched: “You gas-guzzling boomer—melted my ice caps with your big dumb truck!” Her voice cracks—shrill. I scream: \textit{“GRETA—ICE CAPS—ME”} \textbf{MLK} steps up—calm but heavy: “You silent bigot—kept my marchers down—stalled my dream with your privilege!” \textit{“MLK—INJUSTICE—SILENCE”}

They don’t wait. \textbf{Bill Gates} leans forward—glasses glinting: “You anti-vax yokel—spread plague with your ignorance—my cure’s wasted on you!” \textit{“GATES—VIRUSES—LEGACY”} \textbf{Kamala} interrupts—laughing sharp: “You entitled slouch—built the glass ceiling I shattered—equality’s lost on you!” \textit{“KAMALA—SYSTEM—WOMEN”} \textbf{Al Gore}’s next—red-faced: “You coal-loving slob—drowned my coasts—laughed at my charts!” \textit{“GORE—COASTS—FOOTPRINT”}

\textbf{Bill Maher} smirks—cutting in: “You brain-dead chump—killed truth with your fake news—I’m stuck fixing your mess!” \textit{“MAHER—REASON—NEWS”} \textbf{Osama bin Laden}—beard gray—voice low: “You burger-eating infidel—your TV bred my jihad—forced my holy fight!” \textit{“OSAMA—WAR—INFIDEL”} \textbf{Xi Jinping} stands—stern: “You lazy capitalist dog—your flops let China win—my order trumps your chaos!” \textit{“XI—CHAOS—FALL”}

More pile on. \textbf{Nelson Mandela}—slow—grave: “You apartheid clone—locked freedom in your white fists—betrayed my rainbow!” \textit{“MANDELA—FREEDOM—GHOST”} \textbf{Oprah}’s voice booms: “You misogynist nobody—muted my sisters—my billions rose despite your hate!” \textit{“OPRAH—VOICELESS—HATE”} \textbf{AOC} glares—fast and fierce: “You gentrifying bro—priced out my people—wrecked the Bronx with your greed!” \textit{“AOC—HOUSING—GREED”}

They overlap—shouting—\textbf{Greta} screeches over \textbf{Gates} about emissions—\textbf{MLK} buries \textbf{Xi} in justice—\textbf{Maher} snaps at \textbf{Osama} about dogma—\textbf{AOC} drowns in rent rants. I scream louder—notes piling: \textit{“ALL—BLAME—WORLD—ME—CHAOS”} It’s a storm—absurd—twisted—me—one man—white—straight—taking the fall for it all? Ice caps—wars—viruses—dreams—rent hikes—like every protest I skipped—every deal I didn’t sign—every screen I watched pinned it on me.

They point—accuse—\textbf{Obama} says my pickup broke unity—\textbf{Greta} calls me a coal-chugging pawn—\textbf{Kamala} ties me to plantation chains—\textbf{Bin Laden} blames my sitcoms for terror. I scream: \textit{“UNITY—COAL—SLAVERY—JIHAD”} Head’s splitting—throat raw—but I track it—wild—like I’m the root of everything. \textbf{Maher} yells I sank comedy—\textbf{Gore} says I swamped Florida—\textbf{Oprah} claims I choked her voice—\textbf{AOC} snaps I stole her block—\textbf{Xi} calls me a flabby pig. \textit{“COMEDY—FLORIDA—VOICE—BLOCK—PIG”}

Then silence slices through. A figure moves—hooded—white—KKK robe—slow steps from the shadows—a faint whir under the cloth—like gears ticking—not flesh. Crowd freezes—eyes shift—\textbf{Obama}’s jaw tightens—\textbf{Greta} gasps—\textbf{MLK}’s fists clench. Hooded figure stops at the switch—wooden lever—wires sparking faint—robe brushing the floor with a stiff scrape. I scream: \textit{“KKK—SWITCH—HERE”} No one speaks—just stares—\textbf{Gates} adjusts his glasses—\textbf{Harris} shifts—\textbf{Bin Laden} smirks—\textbf{Musk} tilts his head like he’s scanning. Figure’s hand hovers—gloved—a metallic glint peeking from the sleeve—steady or trembling—I can’t tell. I scream again: \textit{“HAND—SWITCH—NOW”} Voices gone—just the hum—my breath—their eyes—rigged—waiting.

\section*{Crisp, Local IPAs}

April 2, 2025. Time irrelevant—end near. Sparks crackle—electricity bites—slow—not instant like they say. Chair hums—wires spit blue—burning my wrists—leather straps sizzling. Process drags—\textit{why?} Long enough to think—to scream final notes into the void: \textit{“SPARKS—SLOW—CHAIR—BURNS”} \textbf{Obama}’s eyes widen—\textbf{Greta} flinches—\textbf{MLK} grips the rail—\textbf{Xi}’s stone-still. The KKK figure pulls the switch harder—current surges—my teeth rattle—I scream: \textit{“SURGE—TEETH—FINAL”} Vision blurs—white—black—screen cuts in.

Words fade onto the screen: \textit{Simulation Terminated. Thank you for experiencing ‘Life as Another: Virtual Identity Trial.’ Exit Menu.}

A soft hum fades. \textbf{Lila} blinks—eyes adjusting—22—golden hair tumbling over her shoulders as she slips off the sleek silver VR helmet—wires snaking to the sleep-pod by her bed. Her room glows pastel pink and white—LA sun spilling through gauzy curtains—a neon \textit{Good Vibes} sign buzzing over a shelf of succulents. She stretches—a sleepy grin curling her lips—and chirps—“Okay—who’d pick being a white dude? That was wild.” Her voice is light—bubbly—a little smug—she’d chosen the “realistic-identity” trial for the thrill.

April 2, 2025. Morning. It’s Friday—and \textbf{Lila}’s day blooms like an Insta reel. She hops out of bed—bare feet kissing polished hardwood—and glides to her closet: a flowy sundress—cream with tiny daisies—layered with dainty gold necklaces and chunky tan sandals. Breakfast is smashed avocado on artisanal sourdough—chili flakes dusting it like red confetti—paired with a latte she foams herself—oat milk swirling into a heart—humming \textbf{Taylor Swift}’s latest. She spritzes rosewater mist over her face—cheeks glowing—and twirls in the mirror: tan skin—green eyes sparkling—a total vibe. She admires how the sunlight catches her tan skin—making it glow—and thinks—“Looking this good should be illegal.” A quick smirk—her beauty has always opened doors—snagged free drinks—turned heads. But today—it feels like armor—a shield against whatever weirdness the VR trial left behind. She snaps a mirror selfie—captioning it \textit{“golden hour glow”} for Insta. Grabs her \textit{Be Kind} canvas tote—lip gloss—reusable straw—a peony petal peeking out—and floats out—LA humming soft around her.

Santa Monica’s alive—ocean air brushing \textbf{Lila}’s cheeks as she strolls the pier. Waves lap gentle against the pilings—seagulls swoop overhead—and she snaps pics: ferris wheel spinning against a sherbet sky—her giggling with a strawberry ice cream cone—pink sweetness dripping down a golden waffle edge—fingers sticky with summer vibes. Lunch is at a vegan café with \textbf{Mia}—her bestie—a quinoa bowl bursting with roasted beets—kale ribbons—and a glossy tahini drizzle—paired with iced hibiscus tea—ruby-red in a mason jar—condensation beading like jewels. Over their quinoa bowls—\textbf{Mia} leans back—eyeing \textbf{Lila}’s effortlessly tousled hair. “God—you always look like you stepped out of a magazine. It’s unfair!” \textbf{Lila} laughs—waving it off. “Says the girl who could model those qipaos like a runway star. You’re stunning—babe.” \textbf{Mia} rolls her eyes—but her smile widens—she knows her sleek black hair and sharp cheekbones turn heads—even if she plays it down. Their beauty is a shared language—a quiet confidence between them. “That VR thing was insane,” \textbf{Lila} giggles—tossing her hair. “I was this basic white guy—all conspiracies nonstop. Total rush.” \textbf{Mia}—sleek black hair flipping with Shanghai flair—leans in—eyes bright. “Whoa—I’d kill to try that—swap lives for a day? Sign me up.” She smirks—twirling her straw. “Reminds me of Lunar New Year—when I went home to Shanghai with my parents. You were obsessed with those silk qipaos at the party—red—gold dragons snaking down ‘em. I could’ve grabbed one for you—but you didn’t say—and now I’m stuck here ‘cause Mom and Dad’s latest blowout has all my flights on hold. They dragged me there for some family business mess—won’t spill what.” \textbf{Lila} pouts—“Ugh—next time—babe”—and they sip smoothies—mango-passionfruit swirls—chia speckling the top like tiny stars—swapping ideas for a glowy night of palo santo and rooftop tarot under the LA stars.

Afternoon’s a dreamy whirl. She browses a boutique for rose quartz earrings—teardrop gems catching the light—then hits the farmer’s market: lavender soap bars stacked like lilac bricks—a bouquet of peonies—pink and plush—spilling over her arm. At a rooftop juice bar with \textbf{Mia}—they scoop acai bowls—purple swirls crowned with edible pansies—scrolling Insta for crystal meditation ideas—laughing about \textbf{Mia}’s \textit{“parental chaos she won’t spill.”} \textbf{Lila} texts \textbf{Ethan}—her date—tall—surfer vibes—dimples deep—confirming 7 p.m. at a rooftop bar downtown. Back home—she curls her hair into loose waves—slips into a sage-green dress that hugs her curves just right—and dots vanilla perfume behind her ears—a sweet cloud trailing her. Mirror winks back: radiant—LA’s golden girl—living her sweetest frame.

Sun dips low as she arrives—rooftop strung with fairy lights—music pulsing soft—skyline glittering like a filter. \textbf{Ethan}’s there. When \textbf{Ethan} greets her—his “Hey—you look amazing” isn’t just polite—it’s laced with a stare that lingers a beat too long on her curves—her glossed lips. \textbf{Lila}’s used to it—the way her beauty pulls focus—but something about his gaze feels off—like he’s scanning her—not just admiring. She brushes it aside—chalking it up to nerves—but the unease sticks. They order beers—crisp local IPAs—amber glowing in frosted glasses—and clink—giggling over his surf wipeout tale. He adjusts his ear once—\textit{odd for a sec}—then grins again. She takes a sip—cool and bitter—then a slow gulp—then a bigger one.

A chill creeps in—world tilts. Eyes narrow—she scans: music’s off-key—lights flicker wrong—\textbf{Ethan}’s grin too stiff. “Somethin’s not right,” she mutters under her breath. Far end of the bar—the bartender—dark hair—narrow eyes from somewhere—polishes a glass—same slow swipe she’s seen before—staring over it. \textit{Why’s he watching?} She chugs the bottle—slams it down. No notebook—hands slap her dress—empty. Panic hits—she screams: \textit{“BARTENDER—STARING—BAR—NO NOTES”} \textbf{Ethan} blinks—“Lila—you good?”—voice steady—but his wrist flicks to a sleek watch—too high-tech for a surfer. \textit{“TRAP—SET—WATCHING”} she yells—bolting for the back—through the kitchen—past cooks flipping sizzling patties. A knife glints on the counter—she grabs it—slips—and it slices her palm. Pain stings—but no blood—wires spark—metal gleams under torn skin—a faint blue glow pulsing. She freezes—screams: \textit{“HAND—WIRES—ROBOT—WHAT”}

\textbf{Ethan}’s voice fades—“Lila—wait!”—but she’s staring: gears whir—no blood—just a hum. \textit{Android? Cyborg?} Mind reels: \textit{“EXPERIMENT—ME—MACHINE”} She drops the knife—staggers to the back room—screaming: \textit{“MACHINE—TRAP—TEST”} A small window’s there; she shoves it open—glass scraping her arms—and tumbles out into a dark alley—pavement wet—shadows thick. She scrambles up—dress ripped—hand sparking faint—screams: \textit{“ALLEY—DARK—ESCAPE”} Looks back—bar lights pulse—figures loom slow—too slow. Runs—barefoot—into the night—machine or not—something’s hunting—no notebook—no answers—just flight.

\end{document}