\documentclass[12pt,oneside]{book} % 'oneside' removes separate recto/verso formatting

% UTF-8 and color
%\usepackage[utf8]{inputenc}
\usepackage{xcolor}

% Page geometry
\usepackage{geometry}
\geometry{
  paperwidth=6in,
  paperheight=9in,
  margin=1in,         % simpler margins, more "web-like"
}

% Microtypography
\usepackage{microtype}

% Web-like paragraph spacing: remove indentation, add small vertical skip
\usepackage{parskip}
\setlength{\parskip}{0.7em}
\setlength{\parindent}{0pt}
\setlength{\headheight}{14.5pt}

% Slight line spacing
\usepackage{setspace}
\setstretch{1.15}

% For custom headings
\usepackage{titlesec}

% Use a modern or futuristic sans font for the body text
% (Install locally or pick something included, e.g. 'Roboto', 'Fira Sans', 'ShareTechMono', etc.)
\usepackage{fontspec}
\setmainfont{Roboto} % Or any installed TTF/OTF font you like

% If you want a monospaced typewriter vibe, try this:
%\setmainfont{Share Tech Mono}

% For fancy frames if you want them
\usepackage{mdframed}

% Hyperlinks without ugly boxes
\usepackage[hidelinks]{hyperref}

% Minimalist page headers/footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} 
\fancyhead[C]{\textsf{\thepage}}  % page number in the center, in sans
\renewcommand{\headrulewidth}{0pt}

\newcommand{\note}[1]{\texttt{#1}}

% Make chapter titles big & neon, remove "Chapter X" if desired
\titleformat{\chapter}[display]%
  {\huge\bfseries\color{black}\sffamily} % Font setup, color
  {}                                        % We can omit "Chapter \thechapter"
  {0pt}{\Huge}                              % Additional formatting

% Similarly for sections
\titleformat{\section}[block]%
  {\Large\bfseries\color{black}\sffamily}
  {\thesection}{1em}{}

% Book metadata
\title{\color{black}WMD: To Glitch}
\author{\color{gray}Vladimir Sumarov}
\date{\today}

\begin{document}

% Title page
\maketitle

\begin{mdframed}[linewidth=2pt,linecolor=black]
\begin{center}
    {\Large \bfseries Content Warning}
\end{center}

This book is a work of speculative fiction containing unsettling themes,
strong language, violence (sometimes graphic), mental health struggles,
and potentially offensive or bigoted viewpoints expressed by characters
for the sake of realism. These do not represent the author’s personal beliefs.

\textbf{Reader discretion is advised} if you feel uncomfortable with:
\begin{itemize}
    \item References to paranoia, conspiracy, and psychological distress
    \item Explicit or graphic violence
    \item Potentially offensive or bigoted language
    \item Surreal or disorienting narrative techniques
\end{itemize}

All characters, events, and institutions are fictional. Any resemblance
to real persons or entities is unintentional. The author disclaims all
liability for any harm or distress caused by reading this material.
\end{mdframed}

\tableofcontents

\part{The Overexposed Memory}

\chapter{As Usual at This Time}

I walk by the corner store as usual at this time of day. 8:47 a.m., to be exact, I checked my watch twice because the second hand seemed to stutter. \textit{Or maybe it’s my eyes playing tricks again.} And there’s this Jew. \textit{Why he look at me like that?} His eyes, narrow and sharp, like they’re peeling me open layer by layer, looking for something I didn’t even know I hid. I scribble this down in my notebook: black leather, 5x7, the one I keep in my left coat pocket because the right one’s got a hole from when I snagged it on the fence last Tuesday. The Jew’s standing there, behind the counter, polishing a glass with a rag that’s probably dirtier than the glass itself. He’s got a name tag \textnormal{"Eli"}, but I bet that’s not his real name. \textit{They never use real names, do they? Too risky, too telling.}

I don’t go in. Not today. I just keep walking, head down, because if I stop, he’ll ask me something, and then I’ll have to answer, and then he’ll know. \textit{Know what? I don’t know what. But something.} My shoes scuff the pavement, gray sneakers, laces fraying on the left one, and I count the cracks in the sidewalk: one, two, three, stop at four because four’s a bad number. \textit{Too square, too even, too much like a cage.} I write that down too, in case it means something later.

The air smells like burnt coffee and diesel, probably from the truck idling across the street: blue cab, rust on the fender, license plate starts with a K. \textit{K for “keep watching,” maybe.} The driver’s slumped in the seat, cap pulled low. \textit{Binoculars under there?} I jot it down: \note{Truck, blue, K-plate, possible surveillance.} My pen’s running low on ink; I can feel it scraping the paper instead of gliding. Have to get a new one soon, but not from \textnormal{Eli}’s store. \textit{He’d probably sell me one with a chip in it, something to track my writing.}

I turn left at the intersection, same as always, because routine keeps me safe. \textit{If I change it, they’ll notice.} Who’s “they”? I don’t know yet. I’ll figure it out when I have more data. My notebook’s got 73 pages filled already, single-spaced, front and back, since I started this three months ago. October 20th, 2024, the day the streetlight outside my apartment flickered three times instead of two. \textit{That’s when I knew something was off.} I wrote it down then, and I’ve been writing ever since.

There’s a woman walking her dog up ahead: black mutt, scruffy, tugging the leash. She’s in a red coat, too bright, like she wants to be seen. I squint at her: mid-30s, maybe, hair in a bun, glasses perched on her nose like she’s pretending to read the world. She nods at me as I pass. \textit{A nod. Why a nod?} I don’t know her. Never seen her before, or have I? I flip back through my notebook: October 28th, woman in yellow scarf, November 14th, woman with stroller, but no red coat. \textit{New player, then.} I write: \note{Woman, red coat, black dog, nodded at me, 8:53 a.m.} The dog barks once, sharp, like it’s signaling something. I don’t look back. \textit{Looking back shows you’re scared, and I’m not scared. I’m aware.}

The bus stop’s next. I don’t take the bus, too many eyes, too many variables, but I pass it every day to check the schedule. It’s taped to the pole, laminated, but the edges are curling up like it’s tired of being there. Bus 42 is due at 8:55 a.m. Except it’s not there yet, and it’s 8:56 now. \textit{Late. Or canceled. Or rerouted to follow me.} I note it: \note{Bus 42, late, possible deviation.} There’s a man sitting on the bench, old, hunched, reading a newspaper. He doesn’t look up, but I see his fingers tighten on the pages. \textit{He’s pretending, I bet.} I write: \note{Old man, newspaper, tense grip, 8:56 a.m.}

I keep moving. My apartment’s six blocks from here, 12 minutes if I don’t stop, 14 if I do. I won’t stop. The wind picks up, rattling the leaves in the gutter, and I hear a car horn two streets over, short, sharp, like a code. \textit{I don’t know the code yet, but I’ll figure it out.} Everything’s a pattern if you look hard enough. My pen scratches as I write: \note{Horn, two streets west, single blast, 8:58 a.m.} The ink’s almost gone now; I can barely read the last letters. I’ll have to switch to pencil when I get home. \textit{Pencil’s safer anyway, no ink to spill, no evidence to leak.}

I pass the alley behind the Chinese joint, and the air reeks. Trash, or something worse. Two guys lean against the wall, hoods up, hands buried in their pockets. One’s got a tattoo, dragon or snake, curling up his neck like it’s alive. They don’t look at me, but I feel their eyes anyway. \textit{They’re watching, aren’t they?} I jot it down: \note{Two men, alley, tattoo, 9:00 a.m. Gang vibe?} \textit{Maybe.} I’ll keep it in mind for later, when the pieces start fitting together. \textit{They will. They have to.}

I walked by the next block. Bookstore was there, of course, sign all but bleached out, windows like eyes peering out from behind a film of dust. Always felt like they were watching you from in there.  New paper slapped on the front: 'A. Gore, climate justice.' Words half gone, ink bleeding like a wound down the page. Took a second to make it out.  \textbf{Gore} - like a twisted message just for me.  Scribbled it down: \note{Bookstore, Gore thing, pressure point?, 9:02 a.m.}  Not falling for it.  They push, though.  Always pushing.  It's that feeling again, isn't it?  Everywhere now.  In the air you breathe. Closing in. I can feel it. I can feel it.

By the time I reach my building, gray brick, four stories, buzzer’s broken again, it’s 9:10 a.m. I check the windows first. Mine’s third floor, second from the left. Curtains are still drawn, same as I left them, but I squint anyway. \textit{Could be a shadow, could be nothing.} I write: \note{Window check, no movement, 9:10 a.m.} The lobby smells like mildew and stale cigarettes. Mailbox 3B, mine, has a new scratch on it, thin, diagonal, fresh. Not there yesterday. I run my finger over it, feel the edge. \textit{Someone’s marking me.} I note it: \note{Mailbox 3B, new scratch, diagonal, 9:11 a.m.}

Up the stairs, elevator’s a trap, always has been, I count the steps: 28 to the third floor, same as always. Key in the lock, turn twice, push the door slow. Inside, it’s quiet. \textit{Too quiet?} I stand there, listening, pen hovering over the page. The clock ticks, 9:13 a.m., and the fridge hums low, like it’s whispering secrets. I write: \note{Apartment entry, quiet, clock and fridge audible, 9:13 a.m.} Then I check the locks again, both of them, and the chain. All secure. For now.

I sit at the table, wood, scratched, wobbly leg, and flip open the notebook to a fresh page. Pen’s dead, so I grab the pencil from the drawer, green, sharpened yesterday. I start transcribing the day, every detail, every thought, because if I don’t, they’ll slip away, and then I’ll miss something. \textit{Something big.} The Jew at the store, the woman with the dog, the late bus, the gang, the poster, the scratched mailbox, it’s all connected. I just haven’t cracked it yet. But I will. I’ll write it all down, and I’ll figure it out. They can watch me all they want, but I’m watching them too. \textit{And I’ve got the proof right here, in black ink and pencil lead, page after page after page.}

\chapter{Quieter Than Yesterday}

February 21, 2025. 7:32 a.m. I wake up to the sound of dripping, slow, deliberate, like a metronome set to torment me. It’s coming from the bathroom sink, even though I tightened the faucet last night, three full turns with the wrench I keep under the sink. I checked it twice before bed, noted it at 11:47 p.m.: \note{Faucet secured, no drip, wrench back in place.} Now it’s leaking again. \textit{Someone’s been here.} I grab the notebook, black leather, 5x7, pencil still sharp from yesterday, and write: \note{Drip started overnight, faucet tampered, 7:32 a.m.} I don’t fix it yet. I listen instead. Drip. Drip. Drip. Three seconds apart. \textit{A signal?} I count ten drops, then stop, because eleven’s too complete, too final.

I don’t leave through the front door today. \textit{Routine’s compromised after the mailbox scratch.} Someone knows my path. I take the fire escape instead, third floor, rusted rungs cold under my hands. The alley smells like wet cardboard and something sour, maybe rotting fruit from the dumpster. I scan the ground, cigarette butts, a candy wrapper, a feather. \textit{A feather?} Black, small, curved like a crow’s. I pick it up with my sleeve, not my fingers, tuck it into my pocket. \textit{Evidence.} I write: \note{Feather in alley, black, possible marker, 7:39 a.m.} \textit{Crows don’t just drop feathers. They’re messengers.} I’ll look that up later.

The street’s quieter than yesterday, no truck, no dog. I head east instead of west, toward the canal, less foot traffic, fewer eyes. My boots crunch on gravel, brown lace-ups, scuffed toes, and I notice the pebbles are uneven, like someone scattered them on purpose. \textit{A trail?} I crouch, inspect them: small, gray, some wet despite no rain overnight. I write: \note{Gravel by canal, wet, arranged, 7:46 a.m.} Then I see it, a glint in the water, ten feet out. Metal, maybe glass, catching the sun. I squint, but it’s too far to tell. \textit{Binoculars would help, but I don’t have them.} They’d have them, though. Whoever’s watching. I note it: \note{Object in canal, reflective, 7:48 a.m.}

A barge drifts by, slow, engine rumbling low like a growl. The man steering it, bald, bearded, orange vest, stares straight ahead, but I see his hand twitch on the wheel. \textit{He’s avoiding me. Why?} I don’t know him, but he knows something. I write: \note{Barge man, orange vest, twitchy hand, 7:51 a.m.} The water ripples behind him, and I count the waves, five, six, seven, before they fade. \textit{Seven’s a power number, too strong, too intentional.} I don’t like it.

I keep walking along the canal path, concrete cracked and mossy, until I reach the bridge. It’s old, iron, painted green but peeling in strips like shedding skin. There’s a lock on the railing, brass, shiny, no rust. New. I stop, stare at it. \textit{No one puts a lock here.} It’s not a lover’s bridge, not a tourist spot. I touch it, cold, smooth, and feel a hum, faint, like it’s alive. My pencil scratches fast: \note{Lock on bridge, brass, new, humming, 7:59 a.m.} I look around, nobody, but the air feels thick, like it’s holding its breath. Then I hear it: a click, sharp, from under the bridge. I freeze. Write: \note{Click from below, source unknown, 8:00 a.m.}

I don’t go under. \textit{Too risky.} I backtrack instead, fast, past the barge, gone now, and the glinting thing in the water, still there, mocking me. My heart’s thumping, but I keep my steps even, four paces, pause, four paces, pause, so they won’t know I’m rattled. In the alley, I spot a marking on the wall, spray-painted, fresh, a half-moon with an arrow through it. Not there yesterday. I jot it down: \note{Wall marking, half-moon with arrow, new, 8:05 a.m.} \textit{Could be a tag, could be a sign.} I’ll check my notes later for patterns.

Back in the alley, I climb the fire escape, check the feather in my pocket, it’s still there, bent now, and slip inside. 8:14 a.m. The drip’s stopped. \textit{Stopped?} I run to the bathroom, stare at the sink. Dry. Not a drop. I didn’t fix it. I write: \note{Drip gone, unexplainable, 8:15 a.m.}

Before sitting down, I glance out the kitchen window. A figure stands across the street, half-hidden by a lamppost, tall, coat too heavy for the weather, face shadowed. I note it quick: \note{Figure by lamppost, heavy coat, stationary, 8:16 a.m.} Then he turns, slips into the crowd, gone before I can blink. I add: \note{Figure vanished, 8:17 a.m.}

I sit at the table, wood, scratched, wobbly leg, and spread the notebook open. The feather goes next to it, flat on the page, a dark slash against the white. I sketch it quick, curved spine, frayed edges, then start transcribing: the drip, the feather, the gravel, the canal object, the barge man, the lock, the click, the wall marking, the figure. It’s not random. It’s a sequence, a message, a map. The dripping was a wake-up, the feather a pointer, the lock a key, literal or not, I’ll find out. They’re closing in, tightening the net, but I’m ahead. I’ve got the pieces, right here, in pencil and paper. I’ll decode it before they do. I have to.

\chapter{Then a Third}

March 23, 2025. 4:17 p.m. It’s been weeks since I left the apartment, 27 days, noted on page 89: \note{Last outing, February 24, minimal contact, safe return.} Too much has piled up: the feather’s still on my table, shedding tiny barbs; the lock’s hum echoes in my head; the drip started again three nights ago, irregular now, like Morse code I can’t crack. \textit{They’re back.}

I had to go out today, supplies low, no pencils left, only stubs too short to grip. I take the front door this time, no fire escape, because the alley’s too exposed. A car’s been sitting there, engine off but not silent—radio static leaking through the cracks.. Notebook’s in my left pocket, 5x7, pages curling at the edges from sweat and overuse. I lock the door, twice, chain on, and step into the street.

The city’s wrong. It’s swollen, buzzing, loud, pre-holiday madness, Easter or something, I don’t keep calendars anymore. People everywhere, elbows jabbing, bags swinging, voices overlapping like static, boots churning slush into black streaks on the pavement. I write: \note{Crowds, holiday prep, 4:19 p.m.} They’ve got ribbons up, red and yellow, strung across lampposts like nets waiting to drop. A woman brushes past me, green scarf, jingling bracelets, muttering about eggs. \textit{Eggs?} I squint at her, then at the store windows: baskets, pastel colors, fake grass. \textit{It’s a distraction, a cover.} I note: \note{Egg talk, possible code, 4:21 p.m.}

I head for the stationery shop, three blocks north, but the street’s clogged. A man in a rabbit costume, white, floppy ears, holding a sign, stands by a cart, handing out candy. His eyes are hidden behind the mask, but I feel them tracking me, mechanical, unblinking, like he’s programmed to track. \textit{Why a rabbit?} I write: \note{Rabbit man, candy, observing, 4:24 p.m.} Kids swarm him, laughing, sticky hands grabbing. One drops a wrapper, shiny, purple, lands near my boot. \textit{Could be laced, tagged, a plant.} I don’t pick it up. I step over it, keep moving.

The air’s thick with cinnamon and exhaust, street vendors frying dough, shouting prices in monotone loops. A bell rings, sharp, from a church two streets over. Then another. Then a third. Three bells, uneven, like that night the streetlight flickered before it all started. I stop, pencil shaking: \note{Bells, three, staggered, 4:27 p.m.} \textit{A signal, a countdown.} My chest tightens. I push forward, past a woman with a stroller, twins staring at me, eyes glassy and fixed, and a guy on a phone, whispering fast. He says “package is close” twice. I catch it, write: \note{Man on phone, ‘package is close’ x2, 4:29 p.m.} \textit{Package for me? Has to be.}

The stationery shop’s ahead, but the crowd’s a wall now, shoulders, hats, a sea of breath fogging the air. A horn blares, delivery truck, white, no markings, cuts me off. The driver leans out, yells something I don’t catch. His cap’s pulled low, like the truck guy from February, but no K-plate this time. I write: \note{Truck, white, no plate visible, aggressive, 4:32 p.m.} The crowd shifts, shoves me sideways, notebook nearly slipping from my pocket. I clutch it, heart hammering. \textit{They’re herding me.} 

I turn back, home’s safer than this, but the street’s a maze now. Lights flicker on, strings of bulbs dangling over doorways, blinking in patterns I can’t read. A carol starts, tinny, off-key, piped through speakers I didn’t see before. I write: \note{Lights blinking, carol, unnatural, 4:35 p.m.} A kid runs past, balloon tied to his wrist, red, bobbing like a flare. It pops, loud, and I flinch. Laughter ripples from behind, sharp, familiar. I spin, but faces blur, too many, too close. My pencil scratches: \note{Balloon pop, laughter, targeted?, 4:37 p.m.}

I’m two blocks from home, but it’s slow, every step’s a fight. A woman drops a bag of groceries, oranges roll, one hits my foot. I kick it away, hard. She glares, mutters something foreign, maybe “your fault” or “white trash”. \textit{Intentional? Did she mean me?} I write: \note{Orange drop, intentional, foreign words, 4:40 p.m.} The bells ring again, four this time. Four. I hate four. My head’s pounding, sweat stinging my eyes. The rabbit man’s back, or another one, same costume, ten feet away now, still as a mannequin, staring. I write: \note{Rabbit man again, closer, stationary, 4:42 p.m.}

One block left. The crowd thins, but the air’s heavier, smoke, maybe something chemical. A drone hums overhead, small, black, hovering right above me, then darting off between buildings. I freeze, watch it vanish. I write: \note{Drone, black, circling, 4:44 p.m.} \textit{They’ve escalated.} My legs shake, but I force them forward. Home’s in sight, gray brick, four stories, but the windows glow, all of them, even mine, curtains twitching like someone’s there. I didn’t leave lights on. I write: \note{Windows lit, intrusion, 4:46 p.m.}

The pencil snaps, lead breaks clean off, rolling under my boot. I fumble for another stub, hands trembling, but a loud crack splits the air. Not a balloon, not a horn, louder, deeper, like the earth splitting. I drop the notebook, clap my hands over my ears, and everything slows: the crowd freezes, faces turn, the rabbit man tilts his head. My vision blurs, white, then black, and I’m falling, knees hitting pavement, notebook splayed open beside me, pages flapping like wings. Then nothing.

\chapter{Like Mine but Torn}

March 23, 2025. Time unknown. I wake up, head throbbing like a drum, lights too bright, white, buzzing, stabbing my eyes. I’m on a bed, stiff sheets, metal rails. Hospital. \textit{How?} Last thing, notebook falling, crack splitting the air, pavement. I sit up fast, hands patting my coat, left pocket empty. Notebook’s gone. My chest tightens, breath short. \textit{They took it.} The Jew from the corner store, the rabbit man, the drone, someone. I scan the room: pale walls, a tray with a cup, a window too high to reach. No clock, but the light’s dim outside, dusk maybe. \textit{I need to write. I need it back.}

I swing my legs off the bed, bare feet, cold tile, and check the bedside table: drawer’s empty, just dust and a bent paperclip. No notebook. My coat’s on a hook, gray, sleeve torn from the fall, but the pocket’s flat, searched. I dig anyway: lint, the feather’s barb, no 5x7 leather. \textit{Stolen. Evidence gone.} My hands shake, but I spot a red marker on the tray, cap scratched, and rolls of gauze stacked beside it, white, coiled, clean enough. I grab both, tear a strip of gauze, and scribble: \note{Woke in hospital, notebook missing, dusk?, red log started.} I wrap the gauze around my arms, chest, legs, words pressed under my coat, a full-body record, ink bleeding faintly through. \textit{It’s messy, strange, but it’ll do.}

Voices outside, low, muffled, shuffling feet. I crack the door, hallway, fluorescent flicker, a nurse at a desk, head down. She’s pale, fingers drumming slow, uneven, like she’s stuck in a pattern. I note it on the gauze, twisting my wrist to write: \note{Nurse, pale, odd rhythm, time unknown.} I need out. Home’s safer, gray brick, locks I trust. I slip into the hall, barefoot, coat pulled tight, red marker tucked in my fist. Signs point left: Elevator, Floors 1-3. Right: Stairs, Floors 1-6. I’m on 4, farthest from the exit. \textit{Planned, probably.} I choose stairs; \textit{elevators trap you, always have.}

Floor 4’s quiet, too quiet. A janitor mops ahead, slow, head tilted, dragging the handle like it weighs a ton. His eyes don’t lift, but his jaw’s slack, lips wet. I write: \note{Janitor, slow, slack face, Floor 4.} I edge past, back to the wall, down the stairwell. Concrete’s cold, steps echo soft. A light buzzes, stutters, off, on, off. I note: \note{Light flicker, Floor 4 stairs.} Halfway down, a man ascends, suit, tie loose, swaying like he’s drunk. He grunts, low, guttural, like something’s stuck in his throat. I freeze, then sidestep. His hand brushes the rail, nails cracked, skin grayish. I write: \note{Man, gray skin, grunt, Floor 3 stairs.} \textit{Something’s off, but I keep moving.}

Floor 3’s busier, patients shuffling, a doctor with a clipboard, all slow, like they’re underwater. The doctor’s head jerks, sharp, then still, eyes locked ahead too long. I write: \note{Doctor, twitch, Floor 3.} Air’s thicker here, sour, like meat left out, clogging my nose. I pull my collar up, breathe shallow. Exit’s two floors down, but the stairwell’s blocked, a cart, tipped, sheets spilled. I duck into a hall instead, past a woman in a gown, staring at nothing, drooling thin. I write: \note{Woman, drool, blank eyes, Floor 3.} My gauze is crowded; I tear another strip, wrap it a second layer: \note{Continued log, Floor 3, air sour.}

A supply closet’s ahead, door ajar, dark inside. I slip in, find a shovel, wood handle, rusted blade, propped against a shelf. Heavy, but mine now. I note: \note{Shovel acquired, Floor 3 closet.} Back in the hall, the doctor’s closer, clipboard dangling, mouth open wider than before. Teeth yellow, jagged. I dodge left, toward the stairs again. Floor 2 now, lights dimmer, a nurse stumbles past, arm dangling, skin peeling at the elbow, her steps too even, like she’s coded to roam. I write: \note{Nurse, peeling, Floor 2.} \textit{Dots connect slow, pale, slack, gray, drool.} Escape first.

Stairs to Floor 1, almost there. A man blocks the landing, big, orderly maybe, swaying, eyes milky. He moans, soft, then loud. I grip the shovel, write: \note{Man, milky eyes, moan, Floor 2 landing.} He lunges, slow, clumsy, but I swing anyway, instinct kicking in. The blade cracks his skull, wet crunch, and he drops, twitching once. I stare, blood black, thick, not right, like the gore filter in a game. Then it hits: not human, not anymore. \textit{Zombies. All of them.} I write, hands shaking: \note{Orderly, zombie, killed, Floor 2, shovel hit.} No time left, exit’s close, but they’ve seen me now.

\chapter{Buzzer Still Broken}

March 23, 2025. Time still unknown, dusk fading. I’m out, hospital doors behind me, glass shattered, no alarm. Shovel in hand, blade sticky with black blood from the orderly. Floor 1 was a blur, two more came at me, a patient with one arm dangling, a guard with half his face gone. I swung twice: first hit cracked the patient’s jaw, second split the guard’s neck. They dropped, gurgling, not human anymore. I wrote it fast on the gauze, wrist cramped: \note{Patient, one arm, killed, Floor 1 / Guard, half face, killed, Floor 1, shovel hits.} No time to think, exit was there, and I took it.

Outside’s worse. The city’s dead but moving. Holiday lights blink, red, yellow, some smashed, casting shadows that twitch. Cinnamon’s gone; air’s rot now, thick, wet. I crouch behind a dumpster, green, dented, leaking something dark, and scan: street’s empty, then not. Shapes shamble, three, maybe four, near the vendor carts, dough cold, flies buzzing. I tear more gauze, wrap it higher on my arm: \note{Escaped hospital, city rotting, 3-4 figures, dusk.} Shovel’s heavy, but I grip it tighter. Home’s six blocks south, gray brick, my locks, safe if I make it.

I move, low, along the alley, wet cardboard underfoot, quieter than pavement. A moan cuts through, left side. I freeze. It’s the rabbit man, costume torn, one ear missing, candy scattered around him. His mask’s off, face gray, eyes sunken, mouth dripping. He lurches, slow, but toward me. No choice. I swing, shovel catches his temple, skull caves in, he flops like a puppet cut loose. I write: \note{Rabbit man, zombie, killed, alley, shovel hit.} Black blood splatters my coat, sleeve now. I wipe it on the wall, keep going.

Two blocks down, hiding’s harder. Street’s wider, lights flicker worse, on, off, on, like a signal I can’t read. A car’s stalled, door open, driver slumped over the wheel. She twitches, head snapping up as I pass, hair matted, teeth bared. I don’t wait. Shovel arcs down, cracks her crown, she slumps again, still. I record it, gauze tight against my skin: \note{Driver, female, zombie, killed, street, shovel hit.} My arm aches, but I write it. Two kills now outside, four total. \textit{Patterns matter.}

Block four, I duck into a shop, stationery, irony not lost. Shelves tipped, pens spilled, no notebooks. A shuffle from the back, clerk, glasses cracked, dragging a leg. He groans, louder when he sees me. I sidestep, swing low, shovel takes his knee, then up to his head. He crumples, glasses skittering. Scribble: \note{Clerk, zombie, killed, shop, shovel x2.} I grab a pencil, red, unsharpened, from the floor, shove it in my pocket. No time for more, moans echo outside, closer.

Last two blocks, I stick to shadows. Holiday ribbons hang limp, shredded, some stained dark. A kid’s balloon, red, deflated, rolls past, carried by wind that smells like death. I hear shuffling, too many feet, but I’m near, gray brick in sight, four stories, my window dark. Relief’s cut short, a figure staggers from the stoop, big, coat like mine but torn, maybe the guy I glimpsed near the mailboxes weeks ago, always lurking near the mailboxes. Neighbor, maybe, or was. He turns, eyes white, jaw unhinged, and lunges. I swing hard, shovel bites his neck, nearly severs it. He falls, wet thud. I write: \note{Neighbor?, zombie, killed, stoop, shovel hit.}

I stumble to the door, buzzer still broken, good sign, and fumble the key. Inside, up the stairs, 28 steps, counting keeps me sane, I lock myself in: deadbolt, chain. Apartment’s untouched, table scratched, feather still there, drip silent now. I collapse, shovel clattering, and unwrap the gauze: \note{Home, 5 kills total, city overrun, time unknown.} Red ink’s smeared into my skin, lines of words bleeding under the surface, like the notes are part of me now. I pull out the pencil, I sharpen it with a knife, slow, deliberate. They’re out there, shuffling, but I’m here. For now.

\chapter{Symbols Staring Back}

March 24, 2025. Time unknown. I wake, curtains drawn, feather on the table, shovel by the door, then a crash. Door splinters, wood flies, and the back of a police shotgun swings at my face. Black steel, barrel scratched, too fast to dodge. It hits, cheekbone cracks, I’m down, sprawled on the floor, blood hot in my mouth. No gauze, no pencil, hands empty, coat torn off me in the fall. Can’t write. I scream instead, notes to the universe: \note{SHOTGUN—POLICE—BROKE IN—FACE HIT—} Voice raw, echoing off walls. They’re here, finally, masks off.

Boots stomp, two, three pairs?, and I analyze: heavy tread, deliberate, not zombie-shuffle. A voice barks, \textit{Stay down!}, male, clipped, no accent I can place. I squint through swelling eyes: uniforms, badges glint, but faces blur. Another hit, butt of the gun, temple this time, stars burst, I scream: \note{SECOND HIT—TEMPAL—BADGES—} Pain’s a wave, drowning me, but I keep tracking: blood pools under my jaw, warm, sticky; floor’s cold, scuffed, same scratches from yesterday. Third hit, ribs, I curl, scream: \note{RIBS—THIRD—COUNTING—} Then black swallows me, no edges, gone.

\subsection*{Hospital Again}

Time unknown again. Eyes flutter, hospital again, different. Bed’s hard, wrists wired to rails, tight, cutting skin. I jerk, but no give. Room’s dim, machines beep, slow, off-rhythm. Figures around me, white coats, zombie doctors, gray skin peeling, eyes dull like the clerk’s. One leans close, teeth jagged, breath like rot. I thrash, wires bite deeper, scream: \note{ZOMBIE DOCTORS—WIRED—TRAPPED—} No shovel, no out. They don’t flinch, just shuffle, hands steady. One holds a syringe, clear liquid, needle glints. I twist, scream: \note{SYRINGE—INJECTION—NO—} It pierces my arm, cold floods in, vision warps, edges soften, gray fades.

Blink. Normal hospital now, white walls, antiseptic sting, no rot. I’m bandaged, arms, chest, gauze thick with symbols: circles, slashes, scribbles I don’t know. Doctors human again, masked, moving fast. A monitor blinks, heart rate spiking. I try to scream, notes, anything, but throat’s dry, voice cracks to nothing. \textit{Injection’s working, head swims, lights pulse, too bright, too real.} Consciousness slips, a slow fade, out.

\subsection*{Concrete walls}
Time unknown, third wake. Concrete walls, no windows, bars enclose the prison cell. I’m slumped on a cot, bandaged, , symbols staring back, etched into the gauze, circles, slashes, scribbles I can’t decipher, faint under the dim light. My wrists are free, but my hands tremble, no pencil, no gauze, nothing to write with, just the itch of the fabric against my skin. A man sits across, pastor, black robe draped loose, beard patchy, eyes fixed on me, unblinking, steady as if measuring something beneath my flesh. He leans forward, voice low, deliberate, a mix of English and Slavic church tones: \textit{My child, pokoj be yours, peace in soul. What do you see when you close your eyes?} His words roll slow, heavy, like he’s tuning me, fishing for a signal. \textit{I don’t trust it, too precise, too probing.} I yell notes into the void: \note{PASTOR—PEACE—SEE—CELL—}

He nods, slight, measured, hands folded in his lap. \textit{Good, ditko, little one. Slava shines, glory of light. What do you hear in this tishina, this silence?} His tone’s calm, a cadence like he’s reciting lines, waiting for me to echo back, to give him something useful. My chest tightens. \textit{He’s digging, calibrating, not praying.} I scream, repeating his bait: \note{GLORY—SILENCE—HEAR—} He tilts his head, eyes narrowing just a fraction, voice steady: \textit{Yes, molitva, prayer rises. Tell me, what burns in your heart, ohn?} His mix of words, half sermon, half Slavic chant, feels like he’s syncing me, pulling data from my bones.

\textit{Suspicion creeps in, why’s he asking? What’s he after?} I scream louder, notes twisting: \note{PRAYER—FIRE—WHAT—} He shifts, robe rustling, voice edging up: \textit{Speak, brat, brother! Bezpeka v dushi, safety in soul, where is it?} His calm frays, hands unclasp, fingers twitch like he’s losing a signal. I scream back, defiance rising: \note{SAFETY—WHERE—TRICK—} His face hardens, eyes glint sharp, and he leans closer, breath sour: \textit{Hovory pravdu, speak truth! Slid grixa, trace of sin, show me!} The church mask slips, urgency breaking through, spit flecking his lips.

I catch it. \textit{He’s not saving me, he’s mining me.} My gut twists, paranoia flares. I scream: \note{TRUTH—SIN—LIE—} He jolts up, robe flapping, voice spiking: \textit{Proklyattya tebe, curse on you! Zhertva, victim, why hide?} His hands curl, spit sprays my bandages, calm gone to rage. I match him: \note{CURSE—VICTIM—HIDING—} He’s shouting now, full tilt: \textit{Pokara! Zlo v tobi, evil in you! Krivda, falsehood!}, beard quivering, robe tearing at the hem as he lurches. I scream: \note{PUNISH—EVIL—FALSE—}

We’re locked in it, voices crashing. He bellows: \textit{Slava rozbiy, glory breaks! Chort tebe, devil take you!}, spit lands on my arm, hands flail like he’s clawing out answers. I scream back: \note{GLORY—DEVIL—TAKE—} He presses on, wild: \textit{Molitva pade, prayer falls! Pokay, repent now!}, his eyes burn, robe frays, words tangle into a snarl. I scream: \note{PRAYER—REPENT—NO—} It’s a storm, no sense, just noise piling up, his fingers twist, spit stains my cot, beard shakes like static. My head pounds, symbols pulse on the bandages, or I imagine they do, no telling anymore. No escape, no record, just this, shouting into a void that shouts back, louder, madder, endless.

\chapter{Stole My Ramen}

April 2, 2025. 6a.m., I think. Time’s slippery here, cell’s got no clock, just a slit window too high to see sun or stars. Woke on the cot again, concrete biting through the thin mattress, bandages still on, symbols faded but there. Been days since the pastor, his Slavic yells echoing in my skull. Counted three so far, three meals of gray mush, watery and cold, three nights of no sleep no reality either, just staring at the ceiling, tracing cracks like code. Hands stopped shaking yesterday, but the need to write clawed at me.  Screaming isn’t enough. I yell notes to the universe: \note{WORDS NEED PAPER—ORDER—PROOF} Voice hoarse, bouncing off walls, useless without ink. I trace the cracks again, seventeen jagged lines, and scream: \note{CRACKS—CODE—WATCHING} No one answers, just silence and the pastor’s gibberish looping in my head.

Third day, guard bangs the bars, grunts \textit{Library}. No cuffs, no shove, just a nod. \textit{Suspicious.} Down the hall, gray, peeling paint, lights buzzing, I find it: shelves sparse, books torn, but a notebook sits on a table, blue, spiral-bound, 8x10, bigger than my old 5x7, pen clipped to it, tip dulled. No one else here, just dust and silence. Took it, no questions, mine now. First entry, scrawled fast: \note{Prison library, day 3, blue notebook acquired, 10:22 a.m.} Felt like breathing again, pen on paper, control back. Flash of the 5x7 slipping from my pocket on that cracked pavement stings, but this’ll do.

\subsection*{Death Row}
Back in my cell, I start catching up, days blurred, but memory’s sharp when it matters.I write \note{Day 1: Pastor, Slavic gibberish, ‘proklyattya,’ screaming duel, no escape. Day 2: Silence, no visitors, mush at noon, cracks in ceiling = 17, possible pattern. Day 3: Library, notebook, this.} Then a clank, door unlocks, loud, metal grinding. I freeze, pen mid-word. No guard, no voice, just open. \textit{A test?} New note: \note{Cell door unlocked, no cause, 11:07 a.m.} Shove the notebook in my waistband, bandages itch under it, and step out.

Hallway’s dim, flickering bulbs, air stale with sweat and rust. Doors line both sides, cells, bars rusted, faces behind them. First one: thin guy, sunken cheeks, staring. I squint, familiar, too familiar. High school, 10th grade, Tim Grayson, pale kid, always doodling skulls in math. He’d smirk at me when I got answers wrong. Now he’s here, eyes locked on mine, no smirk, just hollow. I write: \note{Cell 1, Tim Grayson, school, staring, 11:09 a.m.} Next cell: woman, curly hair, mid-20s. University, Lena from psych class, argued Freud was a fraud. She’d tap her pen like a drum, drove me nuts. Now she’s silent, head tilted, watching. \note{Cell 2, Lena, uni psych, still, 11:10 a.m.}

Doors keep opening ahead, closing behind, clang, clang, like a machine knows I’m coming. No guards, no sound but my steps and the locks. Third cell: bald guy, glasses smudged. Job at the AI startup, Mark, coder, obsessed with neural nets, scoffed at my data entry gig. He’s gripping the bars, knuckles white, staring through me. Write: \note{Cell 3, Mark, AI startup, tense, 11:12 a.m.} My pulse quickens, past’s piling up, faces I buried. Fourth cell: big guy, beard, wild hair. World of Warcraft, clan master, ThrummSkull, led our guild, yelled at me for missing raids. He’s pacing now, muttering, eyes flicking to me. Note: \note{Cell 4, ThrummSkull, WoW, pacing, 11:14 a.m.}

I stop, notebook out, pen flying, connections forming, too neat, too wrong. School, uni, job, game, timeline of me, locked here. Fifth cell: old woman, hunched, knitting something gray. Mrs. Carter, 7th-grade teacher, caught me writing notes once, called it “peculiar.” She looks up, needles still, mouth a thin line. \note{Cell 5, Mrs. Carter, 7th grade, knitting, 11:16 a.m.} Sixth: skinny kid, acne scars, Jake, dorm roommate, stole my ramen, laughed it off. He rocks back and forth, staring. I wrote \note{Cell 6, Jake, uni dorm, rocking, 11:17 a.m.}

Doors keep going, open, close, open, close, leading me deeper, past more cells. Seventh: suit, slick hair, boss at the startup, fired me for “overanalyzing” He’s leaning on the bars, smirking like before. I write \note{Cell 7, Boss, startup, smirking, 11:19 a.m.} Eighth: girl, blonde, chewing gum, Sarah, high school crush, never saw me. Now she does, eyes wide, gum still. I note \note{Cell 8, Sarah, school, staring, 11:20 a.m.} Ninth: wiry guy, tattoos, RazorEdge, WoW rival, trashed me in PvP. He’s clawing the air, growling low. Saved: \note{Cell 9, RazorEdge, WoW, hostile, 11:22 a.m.}

Ten cells, then twenty, I lose count, notebook filling fast. Faces blend, classmates, coworkers, guildmates, some I barely recall, like the janitor from uni who whistled off-key, now whistling again behind bars. I write \note{Cell 14, Janitor, uni, whistling, 11:25 a.m.} Every door opens before I reach it, closes after, herding me. A guard finally, end of the hall, faceless in shadow, points right. I turn, no choice, noting: \note{Guard, shadow, directed right, 11:29 a.m.}

New hall, more cells. A professor, Dr. Kline, AI ethics, droned about sentience, sits cross-legged, stare cold like he’s running numbers on me. I write \note{Cell 21, Dr. Kline, uni, calm, 11:31 a.m.} Next, a kid from middle school, Bobby, threw my backpack in a dumpster, now clawing at his bars. \note{Cell 22, Bobby, school, frantic, 11:32 a.m.} Then, chill down my spine, Eli, the Jew from the corner store, polishing a nonexistent glass, clink faint, same narrow eyes. He nods, slow, like he knows. I write it twice: \note{Cell 23, Eli, store, polishing, 11:34 a.m.} \note{Eli, here, knows.}

Pages flip, half the notebook’s gone now, ink smudging from sweat. Faces pile up: a WoW healer who ghosted us, a startup intern who spilled coffee on my desk, a teacher who failed me in history. I scribble \note{Cell 27, Healer, WoW, blank / Cell 28, Intern, startup, twitchy / Cell 29, Mr. Hayes, school, stern, 11:39 a.m.} Doors keep moving, open, close, like a pulse, guiding me nowhere. Last cell I note: woman with the red coat, black dog, nodded at me months ago, now stroking the air where the dog should be. \note{Cell 35, Red Coat, dogless, stroking, 11:45 a.m.}

I stop, breathless, notebook trembling. Every face, past, present, locked here, watching me. \textit{A puzzle, a trap, a mirror.} Why? Who? Doors clang shut behind, no guard now, just silence and eyes. I write: \note{Faces from life, all cells, connected?, 11:47 a.m.} No answers, just the weight of it all, pressing in.

\chapter{Your Decadence Birthed}

April 2, 2025. Time unknown, irrelevant now. I wake strapped, arms, legs, chest, leather biting skin, the cold slab searing my spine. Wires hum beneath me, pulsing with menace. No notebook, no gauze, hands pinned, can’t write, can’t grip. Panic claws my gut. I scream, throat raw: \note{STRAPS—WIRES—TRAPPED—} Head jerks, eyes dart, room’s dim, circular, walls curving in, a theater of judgment. Faces in the stands, not shadows, not zombies, famous, impossible faces, staring down, judging me, condemning, one guy, white, straight, alone.

Barack Obama emerges, voice smooth but laced with venom: \textit{Your silence didn’t just mute my vision, it crushed a generation’s dreams beneath your cowardice.}

I thrash against the bonds, voice cracking. \textit{I didn’t mean to let you down. I was drowning, searching for solid ground.} My words hang, pathetic, as his gaze cuts through me, unyielding.

Kamala Harris strides in, heels cracking like thunder, words slicing: \textit{Your privilege wasn’t just a shield, it was the lock on my cage, your indifference the chain on my rebellion.} My mind splinters. I yell, desperate: \textit{I didn’t cage you! Look at me, I’m the one trapped here!} Rage boils, chest ablaze.

Laverne Cox steps forward, fierce and unapologetic, voice a blade: \textit{Your apathy propped up their rigid world, man, woman, nothing else, and left me invisible, erased by your quiet complicity.} I choke out, \textit{I, I didn’t erase you!} Her stare doesn’t waver, my defense crumbling.

Joaquin Phoenix charges, wild-eyed, dreadlocks flailing, voice a guttural roar: \textit{You fed on their lives, raised them, loved them, then slit their throats. Tell me, would you butcher your own dog for a meal? Could you watch it bleed out and call it necessity?}

His words slam into me, like a sledgehammer cracking open something raw and jagged. My chest tightens, and suddenly I’m not here. I’m eight again, barefoot on the farm, the earth warm and gritty under my soles. Rusty’s at my side, my shaggy mutt with his lopsided grin, tongue flapping as he chases the sun across the yard. The chickens cluck and scatter, a flurry of feathers glinting gold as I toss grain from a dented tin bucket, their tiny beaks tapping the dirt. Dad’s off-key whistle floats from the tractor, a tuneless thread stitching the morning together, steady as the thrum of his engine. Mom’s voice drifts out too, a soft hum curling around the snap of wet sheets on the line, their clean cotton scent mingling with hay and manure. The pigs are nosing my hands now, their bristly snouts damp and insistent, snuffling for scraps. I laugh, a high, bright sound swallowed by the vastness of the day. The barn looms behind us, its red paint chipped but proud, a fortress of warmth and safety. Then the air splits: \textit{Fire! Fire! Fire!} A wall of heat slams me back. Smoke claws down my throat, thick and acrid, stinging my eyes as the fields erupt in orange and black. The animals scream, pigs thrashing, chickens flapping uselessly, Rusty’s bark choking into a whimper. Flames lick up the barn’s walls, devouring it plank by plank. I reach for him, for anything, but my hands grasp only ash. Everything collapses inward, swallowed by a roaring void. All black.

The memory doesn’t fade, it fractures. A jolt rips through me, straps biting into my wrists and chest, pinning me to cold metal. My pulse hammers, sweat stings my eyes, and the farm’s smoke lingers in my nostrils, a ghost I can’t shake. Voices bleed in, sharp and accusing, pulling me back to the now. Greta Thunberg’s glare pierces through the haze, her words slicing like a blade: \textit{…all Burn. Your greed lit the match, your waste turned my future to ash!} I try to scream, but my throat locks, the sound trapped—a silent, endless howl: \note{FIRE—ALWAYS—FIRE—}

They keep coming. Harry Reid: \textit{Your stillness choked my voice.} Alexandria Ocasio-Cortez: \textit{Your hoarded excess starved my streets.} Their accusations pile on, relentless. I’m breaking, throat locked, screams trapped: \note{WHY—ME—TOO—MUCH—} I’m unraveling, pleading for it to stop.

Silence crashes down, heavy, suffocating. A figure moves, hooded, white, KKK robe, slow steps from the shadows, a mechanical whir beneath. It stops at a switch. Wires spit sparks. I rasp, \textit{Who are you?} No one speaks, just stares. I scream: \note{KKK—SWITCH—HERE—} The figure turns. Eyes blaze from the hood. He grips the lever, hesitates. A low rumble builds in the walls, the air thickens with static. My chest tightens, breath shallow, as shadows shift in the stands. Are they moving closer? The hum crescendos, a promise of something vast and unescapable. Figure’s hand hovers, gloved, a metallic glint peeking from the sleeve, steady or trembling, I can’t tell. The lever still unpulled. Voices gone, just the hum, my breath, their eyes, rigged, waiting. Sparks flare brighter, a storm brews unseen, and I’m left hanging on the edge, unmoored, waiting for the fall.

\chapter{Crisp, Local IPAs}

April 2, 2025. End is near. Sparks crackle, electricity bites, slow, not instant like they say. Chair hums, wires spit blue, burning my wrists, leather straps sizzling. Process drags. \textit{Why?} Long enough to think, to scream final notes into the void: \note{SPARKS—SLOW—CHAIR—BURNS—} Obama’s eyes widen, Greta flinches, MLK grips the rail, Xi’s stone-still. The KKK figure pulls the switch harder, current surges, my teeth rattle, I scream: \note{SURGE—TEETH—FINAL—} Vision blurs, white, black, screen cuts in.

Words fade onto the screen: \textbf{Simulation Terminated. Thank you for experiencing ‘Life as Another: Virtual Identity Trial.’ Exit Menu.}

A soft hum fades. Lila blinks, eyes adjusting, 22, golden hair tumbling over her shoulders as she slips off the sleek silver VR helmet, wires snaking to the sleep-pod by her bed. Her room glows pastel pink and white, LA sun spilling through gauzy curtains, a neon \textbf{Good Vibes} sign buzzing over a shelf of succulents. She stretches, a sleepy grin curling her lips, and chirps, \textit{Okay, who’d pick being a white dude? That was wild.} Her voice is light, bubbly, a little smug, she’d chosen the “realistic-identity” trial for the thrill.

\subsection*{kill to try that}

April 2, 2025. Morning. It’s Friday, and Lila’s day blooms like an Insta reel. She hops out of bed, bare feet kissing polished hardwood, and glides to her closet: a flowy sundress, cream with tiny daisies, layered with dainty gold necklaces and chunky tan sandals. Breakfast is smashed avocado on artisanal sourdough, chili flakes dusting it like red confetti, paired with a latte she foams herself, oat milk swirling into a heart, humming Taylor Swift’s latest. She spritzes rosewater mist over her face, cheeks glowing, and twirls in the mirror: tan skin, green eyes sparkling, a total vibe. She admires how the sunlight catches her tan skin, making it glow, and thinks - \textit{Looking this good should be illegal}. A quick smirk, her beauty has always opened doors, snagged free drinks, turned heads. But today, it feels like armor, a shield against whatever weirdness the VR trial left behind. She snaps a mirror selfie, captioning it - \textit{“golden hour glow”} for Insta. Grabs her "Be Kind" canvas tote, lip gloss, reusable straw, a peony petal peeking out, and floats out, LA humming soft around her.

Santa Monica’s alive, ocean air brushing Lila’s cheeks as she strolls the pier. Waves lap gentle against the pilings, seagulls swoop overhead, and she snaps pics: ferris wheel spinning against a sherbet sky, her giggling with a strawberry ice cream cone, pink sweetness dripping down a golden waffle edge, fingers sticky with summer vibes. Lunch is at a vegan café with Mia, her bestie, a quinoa bowl bursting with roasted beets, kale ribbons, and a glossy tahini drizzle, paired with iced hibiscus tea, ruby-red in a mason jar, condensation beading like jewels. Over their quinoa bowls, Mia leans back, eyeing Lila’s effortlessly tousled hair. \textit{God, you always look like you stepped out of a magazine. It’s unfair!} Lila laughs, waving it off. \textit{Says the girl who could model for anything like a runway star. You’re stunning, babe} Mia rolls eyes, but her smile widens, she knows her sleek black hair and sharp cheekbones turn heads, even if she plays it down. Their beauty is a shared language, a quiet confidence between them. \textit{“That VR thing was insane,”} Lila giggles, tossing her hair. \textit{I was this basic white guy, all conspiracies nonstop. Total rush.} Mia, sleek black hair flipping with Shanghai flair, leans in, eyes bright. \textit{Whoa, I’d kill to try that, swap lives for a day? Sign me up.} She smirks, twirling her straw. \textit{Reminds me of Lunar New Year, when I went home to Shanghai with my parents. You were obsessed with those silk qipaos at the party, red, gold dragons snaking down ‘em. I could’ve grabbed one for you, but you didn’t say, and now I’m stuck here ‘cause Mom and Dad’s latest blowout has all my flights on hold. They dragged me there for some family business mess, won’t spill what.} Lila pouts, \textit{Ugh, next time, babe, maybe I go with you} and they sip smoothies, mango-passionfruit swirls, chia speckling the top like tiny stars, swapping ideas for a glowy night of palo santo and rooftop tarot under the LA stars.

Afternoon’s a dreamy whirl. She browses a boutique for rose quartz earrings, teardrop gems catching the light, then hits the farmer’s market: lavender soap bars stacked like lilac bricks, a bouquet of peonies, pink and plush, spilling over her arm. At a rooftop juice bar with Mia, they scoop acai bowls, purple swirls crowned with edible pansies, scrolling Insta for crystal meditation ideas, laughing about Mia’s \textit{“parental chaos she won’t spill”} Lila texts Ethan her date, tall, surfer vibes, dimples deep, confirming 7 p.m. at a rooftop bar downtown. Back home, she curls her hair into loose waves, slips into a sage-green dress that hugs her curves just right, and dots vanilla perfume behind her ears, a sweet cloud trailing her. Mirror winks back: radiant, LA’s golden girl, living her sweetest frame.

Sun dips low as she arrives, rooftop strung with fairy lights, music pulsing soft, skyline glittering like a filter. Ethan’s there. When Ethan greets her, his \textit{Hey, you look amazing} isn’t just polite, it’s laced with a stare that lingers a beat too long on her curves, her glossed lips. Lila’s used to it, the way her beauty pulls focus, but something about his gaze feels off, like he’s scanning her, not just admiring. She brushes it aside, chalking it up to nerves, but the unease sticks. They order beers, crisp local IPAs, amber glowing in frosted glasses, and clink, giggling over his surf wipeout tale. He adjusts his ear once, odd for a sec, then grins again. She takes a sip, cool and bitter, then a slow gulp, then a bigger one.

A chill creeps in, world tilts. Eyes narrow, she scans: music’s off-key, lights flicker wrong, Ethan’s grin too stiff. \textit{Somethin’s not right} - she mutters under her breath. Far end of the bar, the bartender, dark hair, narrow eyes from somewhere, polishes a glass, same slow swipe she’s seen before somewhere, staring over it. \textit{Why’s he watching?} She chugs the bottle, slams it down. No notebook, hands slap her dress, empty. \textit{Where this panic came from?}, she screams: \note{BARTENDER—STARING—BAR—NO NOTES—} Ethan blinks, \textit{Lila, you good?}, voice steady, but his wrist flicks to a sleek watch, too high-tech for a surfer. \note{TRAP—SET—WATCHING—} she yells, bolting for the back, through the kitchen, past cooks flipping sizzling patties. A knife glints on the counter, she grabs it, slips, and it slices her palm. Pain stings, but no blood, wires spark, metal gleams under torn skin, a faint blue glow pulsing. She freezes, screams: \note{HAND—WIRES—ROBOT—WHAT—}

Ethan’s voice fades, \textit{Lila, wait!}, While she’s staring at her palm for another second: gears whir, no blood, just a hum. \textit{Android? Cyborg?} Mind reels: \note{EXPERIMENT—ME—MACHINE—} She drops the knife, staggers to the back room, screaming: \note{MACHINE—TRAP—TEST—} A small window’s there; she shoves it open, glass scraping her arms, and tumbles out onto fire escape ladder, a dark alley, pavement wet, shadows thick. She scrambles up, dress ripped, hand sparking faint, screams: \note{ALLEY—DARK—ESCAPE—} Looks back, bar lights pulse, figures loom slow, too slow. Runs, barefoot, into the night, machine or not, something’s hunting, no notebook, no answers, just flight.

\part{The Echoes to Reality}

\chapter{Awakening and Escape}

I woke up to the smell of rotting takeout and something sticky in my hair. \textit{Gross.} My head pounded like I’d been hit by a truck, and the sunlight stabbing through the dumpster lid wasn’t helping. \textit{Wait, dumpster?} Oh, right. Last night. The bar, the beer, the… hand thing. I shuddered, pushing the memory down. \textit{Not now.}

I climbed out, wincing as my torn dress caught on the edge. My sage-green sundress, once perfect for rooftop vibes, was now ripped at the hem and stained with something I hoped was just ketchup. My feet were bare, sandals long gone, lost in the chaos at Ethan’s. I glanced at my reflection in a puddle, hair a tangled mess, mascara smudged, dress ripped. Total disaster. But hey, still slay. I struck a pose, just to remind myself who I was. Lila, golden girl of LA, not some paranoid wreck.

\textit{Speaking of paranoid,} I checked my hand. Last night, I’d sworn I saw wires, gears, and a faint blue glow under my skin. My heart raced as I turned my palm over, but there was just a jagged, red cut, no wires, no sparks, just my usual tan skin smudged with dirt. I let out a shaky breath, relieved but still haunted by the memory. \textit{Maybe it was the alcohol, or that weird VR trial messing with my head.} I couldn’t trust that white male persona, and asking someone else? No way. \textit{What if they saw something? Or worse, what if they didn’t?} I wasn’t ready to find out.

I shook it off and started walking home. The alley opened to my street, palm trees swaying like they were waving me back to reality. Pastel cafes were opening, chalkboard signs advertising matcha lattes and avocado toast. The smell of fresh coffee wafted by, and for a second, I felt like myself again. Then I noticed the barista. He was wiping down tables, but his eyes locked on me, lingering too long. \textit{Was it my messy hair, or did he know something?} I quickened my pace, heart thudding. \textit{Maybe I was just paranoid. Maybe not.}

At my building, my stomach dropped. The door was ajar, the lock hanging loose like a broken promise. I pushed it open, and chaos greeted me. Furniture flipped, drawers yanked out, papers scattered like confetti. My neon \textbf{Good Vibes} sign flickered, half-dark, like it was mocking me. Succulents lay toppled, dirt spilled across the floor. Even my vanity mirror was cracked, a jagged line splitting my reflection.

I snapped a quick selfie, me pouting, chaos in the background. \textit{"Vibes even in chaos" - I’d caption it later.} It was silly, but it grounded me. I grabbed my phone, charger, my favorite cream sundress with the tiny daisies, and my charm bracelet from Mia. The little golden sun pendant glinted, a reminder of better days. I clutched it tight, needing that connection.

I texted Mia: \textit{SOS. Place wrecked. Can I crash?} Her reply came fast: \textit{Can’t talk, parents’ mess.}. What? Mia was always there for me. Something was wrong, but I couldn’t deal with it now. So, Ethan. \textit{Hey, can I crash at your place? Emergency}. His reply was almost instant: \textit{Come over, babe}. Too fast, maybe, but I was desperate. I stuffed my tote, spritzed vanilla perfume, \textit{confidence in a bottle}, and headed out.

I ran through LA, bare feet slapping the pavement, sandals still missing. The sunset painted everything gold, glass buildings glowing like they were on fire. A street performer strummed a guitar, singing about love and loss. People stared at my messy hair and torn dress. A skateboarder slowed down, eyeing me. A woman with a stroller gave me a disapproving look. \textit{Let them stare.} I flipped my hair, chin up. Still gorgeous.

But then I saw him, a bartender across the street, leaning against a doorframe, polishing a glass. His narrow eyes watched me, just like the guy from last night. \textit{Creepy.} I made a mental note: \note{possible stalker}.

I reached Ethan’s bungalow, out of breath. He opened the door before I knocked, smiling wide. \textit{Too wide, maybe.} His watch caught the light, glinting oddly, too fancy for a surfer. \textit{Thanks for letting me crash}, I said, forcing a smile. \textit{Anytime, babe}, he replied, leading me to the basement. \textit{You’ll be safe here}. Safe? I hoped so, but something felt off. I brushed it aside, too exhausted to care. I needed sleep, a shower, and answers. \textit{Tomorrow.}

\chapter{Vacay Vibes}

I settled into Ethan’s basement, and okay, it was kind of adorable. Fairy lights crisscrossed the ceiling, casting a soft, golden glow over the futon where I’d be crashing. There was a mini-fridge humming in the corner, a stack of old magazines, and a fluffy blanket that screamed cozy vibes. But then I clocked the weird stuff: cameras mounted high in the corners, a server rack blinking with tiny green lights, and a router that looked way too fancy for a surfer’s basement. \textit{Like, what even?} It felt more like a tech nerd’s lair than Ethan’s chill hangout spot. I snapped a quick pic for Insta, futon, fairy lights, the works, and captioned it \textit{“hideout goals”}, but the tech gear? It made my stomach twist. \textit{What was Ethan hiding?}

\textit{Speaking of Ethan,} he popped in to check on me, flashing that dimpled smile that usually made me melt. But his watch caught my eye again, sleek, silver, definitely not a surfer’s vibe. And then he did this weird thing where he adjusted his ear, like he was listening to something. \textit{Super odd.} I made a mental note but didn’t say anything. \textit{Maybe he was just quirky, right?}

I needed answers after last night, so I grabbed my phone and started scrolling news apps. \textit{Something was up, I could feel it,} and I wasn’t about to sit here clueless. First hit: a vague blurb about a \textit{“disturbance at a downtown bar.”} No names, no details, just noise. Typical. Then a sharper headline: \textit{“Cargo Ship Sinks Off Coast, Suspected Trafficking Bust.”} The article was thin, something about dozens of Asian illegals feared dead, Coast Guard scrambling, no clear culprit. My chest tightened. \textit{Trafficking?} Next up: \textit{“Gang Clash Leaves Five Dead in Chinatown.”} Chinese and Haitian crews tearing into each other, knives and guns, a bloody mess over \textit{“territory.”} Cops were baffled, locals spooked. Then, buried in a sidebar: \textit{“Hospital Overrun After Terror Attack Rumors.”} No specifics, just chaos at some ER, patients flooding in, whispers of \textit{“VR trial subjects”} tied to it, whatever that meant. \textit{Wait, VR trial? Like mine?}

My palms got sweaty as I swiped between articles, headlines piling up like puzzle pieces I couldn’t fit. The ship, trafficking, Asian ties. The gang fight, Chinese vs. Haitian, raw and violent. The hospital, vague, unconnected, but that \textit{“VR trial”} bit gnawed at me. \textit{Was this tied to last night? To Mia’s “parents’ mess”?} I flipped to Insta for a breather, but Mia’s story was just a black screen captioned \textit{“chaos.”} No help there. I tossed my phone onto the futon, head spinning. \textit{Too many dots, no lines.}

I raided the mini-fridge, snagging a frozen pizza. Popped it in the microwave, the gooey cheese melting into something comforting. Then I spotted a margarita machine in the closet, dusty but begging for action. \textit{Vacay vibes}, I thought, giggling as I mixed a pink, frothy drink. I sipped it, the sweetness masking the tequila’s bite. But then the room tilted, and my vision blurred. \textit{Oh no. The alcohol.} It was happening again.

Suddenly, everything snapped into focus, but not in a good way. My mind raced, stitching those headlines into a jagged web. The cameras in here, the server blinking, Ethan’s fancy watch, the ship sinking, the gangs fighting, Mia’s cryptic post, it all felt linked. I grabbed a napkin and scribbled: \note{Ship + gangs = Mia’s parents? VR hospital clue?} My hand shook as I wrote, the memory of wires in my palm flashing back, sharp, blue, unreal. I couldn’t shake it. I had to tell Ethan. \textit{Maybe he knew something.} Napkin’s a mess, ink smeared, clutched tight. Scribbles screaming: \note{Ethan’s a rat? Phone call, trap? Mia’s next?} Head spins, margarita sloshes in gut, sour and sticky. Legs feel like rubber, but brain’s buzzing, cameras wink red, fairy lights pulse. Overheard him upstairs, voice low, calm. \textit{Trap. All of it. VR. Hospital. Mia.} Gotta tell him I know.

Stumble up basement stairs, walls tilt, grip railing, slips, wet palms. Napkin flaps, \textit{proof in my face.} Living room’s bright, Ethan’s there, phone down, eyes narrow. Too cool, too slick. My mouth opens, words sludge out, thick, useless. "You... set... up..." Tongue’s fat, drunk, failing. Screw it, scream it, like always. Lungs rip open: \textit{TRAP—ETHAN—RAT—} Voice booms, sloppy, raw. \textit{PHONE—LIAR—WATCHING—} Napkin shakes, fist slams air, words hit hard, good enough.

Ethan blinks, slow, hands up. \textit{Lila, relax, you’re drunk.} Calm, too damn calm. \textit{He's fake}. Smirk hiding, I see it. Conspiracy. Step back, legs wobble, heart’s a hammer. \textit{SHUT—UP—TRAP—} Scream’s louder, throat’s fire, alcohol fuels it. He moves, slow, toward me, control move, obvious. Panic hits, sharp, electric. \textit{Run. Now.}

Twist, crash down stairs, basement smells, damp, wires, pizza crust. Door bangs shut, lock’s loud, too loud. Cameras stare, lights flicker, watching me. Napkin drops, ink bleeds on floor, no time. Second exit, back wall, small door to kitchen. \textit{Spotted it before}, half-blocked, cluttered. Shove through, hands scrape wood, knees bang, pain’s dull, drunk-dumb.

Kitchen’s a blur, pizza grease, spilled lime, sink’s wet. Counter’s slick, climb it, slip, crash into cups, they shatter, loud. Window’s open, tight fit. Squeeze out, shirt rips, hit grass, cold, rough. City’s alive, lights smear, horns blare far off. Feet slap ground, running, breath’s short, lungs sting. Ethan yells, faint, \textit{Lila, stop!}, cool, too cool, trap voice. Screw him. Sprint harder, city swallows me, shadows twist, lights blind. Gone. For now.

\chapter{Her Eyes Shift}

City’s a kaleidoscope, lights smear into wet pavement, reds, blues, yellows pooling like blood. Bare feet slap concrete, sandals ditched at Ethan’s, lost in the scramble. Alcohol’s heavy, sloshing in my brain, blurring edges. Legs shake, but thoughts race, cameras in the hospital, Ethan’s watch glinting, Mia’s texts buzzing cryptic. \textit{It’s a web.} VR trial, attack, Mia’s place, gotta get there. But my head’s a sieve, leaking details. \textit{Need a notebook. Need to write it down.} Can’t trust my mind, not now.

Street bends, neon buzzes. Vendor cart ahead, stacked with junk, pens, cheap spiral notebooks, crumpled gum wrappers. Guy’s got a beard, squinting at me. Face flickers, Ethan’s smirk slides over his jaw, then back. Blink hard. \textit{Not real?} Alcohol’s screwing me up. Grab a notebook, black, flimsy, five bucks. Fumble Ethan’s cash from my pocket, crumpled bills. "This enough?" Voice slurs, thick, sloppy. He nods, slow, eyes linger. \textit{Too long. Too damn long.} Is he Ethan? \textnormal{Eli} from the store? The Jew’s sharp nose cuts across his face, then gone. Paranoia’s a torch, burning white-hot. Scream rips out: \textit{"WHO—YOU—SPY?"} Voice cracks, raw, echoes off brick. He flinches, steps back, \textit{guilty move, obvious.} Stuff the notebook in my tote, bolt.

\textit{Pen, need a pen.} Dig through the bag, past a tampon, a lighter, there, blue ballpoint. Scribble fast: \note{Vendor = Ethan? Eli? Watching me.} Heart’s hammering, breath’s shallow. Alcohol’s fading, but this, this shift in me, it’s sharper now. \textit{Like a switch flipped when I drank.} Not used to it, not yet, but it’s keeping me moving.

Alley looms, dark, wet. Shadows twist, someone’s there. Ethan? No, just a kid, kicking a can. But his jaw shifts, Ethan’s dimples, then back. \textit{Hallucination.} Note it: \note{Kid = Ethan? Following?} Like agents swapping faces, tracking me. Can’t trust my eyes. Keep running, notebook clutched tight. Streetlights blink: one, two, three. Stop. \textit{Four’s a signal, means they’re close.} Note it: \note{Lights, three blinks, possible code.}

Crowd ahead, faces swivel. Torn dress, wild hair, I’m a mess, sticking out. A guy steps up, "Hey, you lost?" His voice dips, Ethan’s drawl, then normal. Back off, fast. \textit{"STAY—BACK—SETUP—"} He flinches, hands up. Push through, elbows sharp. Woman next, holding a phone, filming? Her eyes shift, \textnormal{Eli}’s glint, then gone. Note it: \note{Woman = Eli? Spying.} Everyone’s a threat, every face a mask.

Taxi rolls up, headlights stab the dark. Driver leans out, "Need a lift?" \textit{Too easy. Trap.} Scream it: \textit{"NO—TAXI—NO—"} He peels away, tires squeal. No taxis, no buses, public stuff’s a cage. They’d pin me down, track me. Feet keep pounding, raw now, stinging. Bar ahead, "Cold Beer" sign flickering. Bartender outside, wiping a glass, same squint as the vendor, as \textnormal{Eli}. Face morphs, Ethan’s stubble, then back. Note it: \note{Bartender = Ethan? Eli? Tailing me.} Duck right, past a dumpster, reek of garbage, sour booze. Stomach lurches, hold it down.

Car horn blares, three short bursts. \textit{Code?} Note it: \note{Horns, three, signal.} Head’s spinning, pavement dips. Grab a wall, bricks scrape my palm. Flashback hits, hospital, shovel swinging, blood splattering tiles. \textit{Real?} News said attack, but holes in the story. Alcohol’s messing with me, or this persona is. It’s like I’m him, the white male from before, paranoid, scribbling, running. But I’m not him. Not yet.

Mia’s building rises, glass, gleaming, fifth floor. Almost there. Alley shortcut, trash bags glisten, a rat skitters. Figure ahead, Ethan? Tall, broad shoulders, moving fast. Or not, streetlight hits, it’s just a jogger. Face shifts, Ethan’s grin, \textnormal{Eli}’s stare, then normal. Note it: \note{Jogger = Ethan? Eli? Can’t tell.} Notebook’s pages are full, ink smudged, paranoia in blue scrawl. Legs burn, lungs ache. Alcohol’s draining, slow, like mud settling. This shift, I get it now. \textit{Booze triggers it,} turns me jagged, watchful. \textit{Useful, maybe,} but I’m not ready for it.

Steps to Mia’s door, concrete bites my soles. Rail’s icy, pull myself up. Breath’s a wheeze, head’s a drumbeat. Knock, sharp, three times. Silence. Mia’s here. \textit{Maybe answers. Maybe not.} Notebook’s heavy in my hand, \textit{proof I’m not losing it. Yet.}

\chapter{Tangled in This}

I stumbled into Mia’s loft, my chest heaving from the sprint across the city, bare feet stinging against the hardwood. The buzz from Ethan’s margarita was gone, leaving me sober but jittery, my tote banging against my hip. Mia’s place was my haven, exposed brick, fairy lights, that vintage vibe she loved, but now it felt wrong, like the air itself was holding its breath.

I froze. The room was trashed. Couch cushions were slashed open, stuffing spilling out like snow. A lamp lay shattered by the wall, and papers, receipts, sketches, random notes, littered the floor. My eyes caught on a torn qipao near the coffee table, its red silk shredded into jagged strips. Mia had worn that dress last Lunar New Year, laughing as she spun under the lanterns. Seeing it wrecked hit me like a punch.

Then I saw them, my old sneakers, shoved under the couch, scuffed gray with frayed laces. A memory flickered: that rare LA rain last spring, Mia giggling as we splashed through streets turned to rivers. \textit{“We’ve got umbrellas, babe, we’re prepared!”} she’d said, but the downpour soaked us anyway. I’d kicked off my drenched shoes here to dry, forgotten them after a night of takeout and tarot cards. I slipped them on now, the familiar fit grounding me, a piece of us before everything went south.

I stepped closer, heart thudding. On the counter, Mia’s phone glowed, unlocked. I snatched it up. Three missed calls from Ethan glared back at me, and my stomach flipped. Texts from an unknown number followed: \textit{“Family debts can’t wait”} and \textit{“Keep quiet, or it gets worse.”} Then I saw it, a sticky note on the fridge, half-ripped, with an address scrawled in Mia’s handwriting: \textit{“Red Lantern Lounge, Chinatown.”}

My mind raced. Mia’s parents had always dodged questions about their \textit{“business,”} but this, debts, threats, a struggle, screamed something darker. \textit{Drugs? Trafficking? Money laundering tied to the Chinese mafia?} And Ethan’s name on her phone? He wasn’t just some creep from the basement; he was tangled in this. I couldn’t call the cops, his betrayal made me paranoid about who he knew, how far his reach went.

I needed to think sharper, faster. That’s when it clicked: the alcohol. It flipped a switch in me, turning me into this hyper-analytical, paranoid version of myself I’d started calling \textit{“WMD”}, White Male Drunk, a twisted side effect from that VR trial. It scared me, especially after what I’d seen, or thought I’d seen, in my hand at the bar. \textit{Wires, maybe,} glowing faintly blue. I hadn’t looked since, too afraid to confirm it, but Mia was in danger. I’d risk it for her.

I spotted a sleek tequila bottle on Mia’s bar cart, the glass cool against my fingers as I poured a shot. My hand hovered, trembling. \textit{You don’t have to do this.} But I did. For Mia. I tipped it back, the burn searing my throat, and waited. The shift hit fast, my thoughts splintered, then locked into place, razor-sharp. The room snapped into focus: the slashed cushions, the torn qipao, the sticky note. I grabbed a notepad from Mia’s desk and scribbled: \note{Red Lantern Lounge, Mia taken? Ethan’s calls, tracking her? Family debts, money laundering?}

My hand shook as I wrote, and in the dim light, I caught a flicker, something blue under my skin. I yanked my gaze away. \textit{Not now. Mia first.} The white male mode churned: the address was a lead, the lounge a front, Ethan a threat. I had to move.

I bolted out of the loft, sneakers pounding the pavement, the LA night swallowing me whole. Neon signs buzzed overhead, casting jagged shadows on graffiti-tagged walls. My tote bounced against my side, the air thick with salt and exhaust. I was tense, every corner hiding Ethan or some goon he’d sent. First stop: the Red Lantern Lounge in Chinatown. Mia was counting on me, and I wasn’t stopping now.

First stop: the Chinatown bar from the note. It crouched behind red lanterns, their glow painting the street crimson. A bouncer loomed out front, arms crossed, a dragon tattoo curling up his neck, \textit{mafia vibes screaming loud.} I scribbled in my notepad: \note{Bar, front for something? Basement door, voices. Mia here?} The WMD mode scanned everything: his rigid stance, the way people slipped inside, heads low, the faint hum from below. My paranoia spiked, \textit{every shadow could be a trap}, but I clenched my jaw. Mia was counting on me, and I wasn’t stopping now.

\chapter{Hot Across My Face}

Red Lantern Lounge squats in Chinatown, neon pulsing, red glow slashing shadows across wet pavement. Sneakers pound concrete, tequila cuts every edge sharp. Bouncer hulks at the door, dragon tattoo coils up his neck, scales flash like a blade. \textit{Mafia mark.} I shove in, eyes sweep fast: smoke hangs thick, glasses clink low, voices mutter tight.

I snag a booth, notepad gripped hard, I scan: silk jacket guy growls at the bartender. “Traffickers botched it. Took the girl. Boss says trade her back or we’re bled dry,” he spits, voice low, venom dripping. \textit{Mia’s family? Money crew?} Pen digs in: \note{Lounge, front for cash game, Mia snagged by traffickers, trade talk.}

Place reeks of gang. Dealers slump at the bar, girls in tight skirts glide, eyes cold, working the room. \textit{Controlled, no chaos.} Silk-suit guy keeps going: “Boss says trade the cash, get her free. Traitors want her for leverage.” My pen races: \note{Zhangs bargaining, Mia hostage, trafficking crew’s play.} Family’s desperate, not running this show. Tequila burns, paranoia spikes. \textit{Every face hides a knife.}

Harbor Street sprawls dark, warehouses loom like graves. Number 47 gapes, windows black, padlock swings loose. I circle, pry a board, slip in. Oil and dust choke me, crates stack high, Chinese script stamped deep. First one’s junk: clothes, bottles, nothing. Second’s the same: papers, trash. Third’s heavy, I crack it, dig past crates of rice, hit a false bottom: cash stacks, ledgers, fake passports. Names, dates, sums glare up, Zhangs scrawled bold. \textit{Family’s dirty, laundering cash, not moving bodies.} Pen flies: \note{Warehouse, Zhangs run money, not trafficking.}

Footsteps thud, I duck behind a crate, pulse slams. Two suits shuffle in, grumble low. “Traffickers want payment, holding her till we cough it up,” one says. Mia. One’s face warps, \textnormal{Eli}’s eyes glint, then blink out. Tequila’s claws dig, I jot: \note{Mia hostage, traffickers’ leverage, family’s cornered.} I slide out, heart pounding, trail their voices two blocks.

Golden Dragon Enterprises looms, door ajar, light leaking. I creep in, hallway stretches into dark. Fluorescents buzz, drilling my skull. Doors line up, locked, cold. One’s open, voices slip out, Mandarin, clipped. “Girl’s with the trafficking crew. Pay up or she’s gone.” Mia. I flatten against the wall, notepad ready, peek through. Two inside: suit pacing, desk guy buried in papers. Third mutters into a phone.

\textit{Need in.} Shadow shifts, I duck into a broom closet, shelves jab my ribs. Phone guy stalks past, voice cuts: “Bullshit. They was under our boss, till higher up split us, to demonopolize they said, now we have internal war on our hands.” Mia’s their chokehold, family’s desperate. He locks the office, splits. I’m pinned, rifle the closet, find a vent, knee-high, grate loose. \textit{Old trick,} I yank it, metal squeals, crawl through, dust gags me, elbows bang steel. Duct spits me into an empty office, door ajar.

Inside’s a mess: files spill, mug’s tipped, photos pinned up. I dig, adrenaline spiking. Manifest lists cash drops, ports, codes. Photo: silk-suit guy from the lounge, shaking hands with some stiff in a suit. \textit{Family ally?} Paper scraps in English: \textit{“Secure the Triad split.”} Pen scratches: \note{Zhangs’ faction link?} Computer glows, login taunts. Type “password”, dead. “Zhang”, nothing. “Mia2008”, screen flares. \textit{Idiots.} Files flood: emails, blurry stills, map with pins, ports, warehouses, hotel off the 405. Email bites: \textit{“Pay the traffickers or she’s done.”} Mia’s their pawn. I hit print, machine hums, map spits out. Stuff it in my tote, ears strain. Keys jingle. Kill the screen, dive behind a filing cabinet. Suit guy storms back, nose twitching. \textit{Smells me?} I freeze, tequila sweat stinks. He curses in Mandarin, locks up, splits.

Breath shakes out. Map crinkles in my tote, pins glare. Hotel pin, circled twice, red ink, room 12. Mia’s there. Has to be. Photo’s noise, \textit{“Triad split”} is family bullshit. Mia’s no spy, just leverage. Trafficking crew’s got her, not Zhangs. I rip the notepad out, scribble hard: \note{Hotel, 405, Room 12, Mia hostage, trafficking split, not family.} Pen trembles, ink smears. Focus. Hotel. Now.

Step out, alley stink fades. Hotel’s a mile, past docks. Walkable. No cabs, \textit{tracked too easy.} Legs shake, tequila thins. Head clears, paranoia hums. \textit{Good.} Need it sharp.

Docks reek of salt and rot, ships groan in the black. I hug shadows, eyes dart. Dockworker glances, face flickers, \textnormal{Eli}’s nose, then gone. \textit{“ELI—HERE—WATCHING—”} I scream in my head, hands twitch for the notepad, too fast to stop. Keep moving.

Red Lotus Hotel sign buzzes, “Vacancy” flickers. Room 12’s light glows, curtains twitch. Someone’s in. Mia? \textit{Trap?} I creep close, heart slams. Figure paces inside, sharp shadow. Not Mia. Too tall. Gang thug. \textit{Guarding? Waiting?} Scribble quick: \note{Room 12, guard, not Mia, trap?}

\textit{Need closer.} Alley behind the hotel’s dark, quiet. Sneak spot. I slip around, sneakers hushed on gravel. Back door’s ajar, light bleeds. Voices growl, low: “Keep her quiet. Boss wants her breathing for the trade.” Mia. Alive. Relief stabs, then rage. They’ve got her. Here.

\textit{Need to see.} Window’s grimy, half-open. Peer in, Mia’s tied to a chair, gag biting her mouth, eyes wide. Two guys inside: one paces, one cleans a gun. Blood boils. WMD rage claws up. \textit{End them. Now.} Flip the notepad, pen gouges: \note{Mia, tied, two men, gun, kill them.} Rage shakes my hand, blue glow pulses under skin, \textit{real or not.}

First, the guard outside. He steps out, cigarette flares. Same bastard from before. My prey. I stalk, silent, into the alley. Dead-end ahead. \textit{Perfect.}

He stops, lights another. I lunge, hands lock his neck. “Where’s Mia?” I snarl. He thrashes, elbow slams my ribs. Pain bursts, breath’s gone. “Crazy bitch!” he spits, fist flies. I duck, knuckles graze my temple, skin splits, blood trickles warm.

Reel back, vision swims, fire roars louder. \textit{“KEY—WHERE—GIVE—”} I scream, voice rips raw. He laughs, wet, mocking, swings again. Dodge tight, slam my elbow into his kidney. He grunts, lurches. Grab his collar, yank, smash his face into the wall. Bone cracks, blood sprays, tooth skitters across pavement. He roars, flails, nose gushes. Hook my arm around his throat, squeeze hard. Nails claw my skin, blood wells, arms burn. \textit{“TELL—ME—MIA—”} I bellow, scream splits my skull, need answers, need keys. Kicks fade, he slumps, fakes it. Let go, step back. He whirls, fist crashes my jaw. Blood floods my mouth, copper sharp, stars explode.

Spit red, charge. Knee rams his gut, he doubles, gags. Snatch a brick off the ground, swing. Skull cracks, wet, sick thud, blood splatters hot across my face. He screams, gurgling, I swing again. Cheekbone caves, teeth fly, one sticks in the wall, blood streaks. Again, eye socket crushes, orb pops, jelly mixes crimson. Again, jaw shatters, bone shards pierce flesh, teeth scatter like gravel. Last swing, skull caves, brain splashes the alley floor. He twitches, stills, a wrecked heap.

Panting, drop to my knees beside him, hands slick with gore. Stench hits, blood, piss, sweat. \textit{Need keys, keycard, anything.} Dig his jacket, left pocket: receipts, lighter, trash. Right: cash roll, twenties, tens. Stuff it in my tote, hands shake. Pants: gum, condom, nothing. Wallet’s cheap, peeling, fake ID, \textnormal{John Lon}, 23, dead cards, dog pic. Useless. Toss it, check socks, shoes, rip his shirt. Nothing. No key. No card. Just a dead nobody. Paranoia claws my chest, \textit{has to be something.} Nothing. \textit{“NO—KEY—WASTED—ALL—”} I scream, throat raw, sound splits the night.

Stand, trembling, brick clunks down. Gore coats me, blood, brain, bits of him. Head throbs, tequila fades, clarity cuts cold. \textit{Useless kill. No lead. Just meat.} He earned it, gang trash, took her, paid up. Thought slices sharp. Then: \textit{His blood’s on me. Face gone. What’d I do?} Snap back: \textit{Justice.} Scum gets no mercy. Means to an end. Softer: \textit{A guy, maybe. Not in it. Dead for nothing.} Cold: \textit{Collateral.} She’s worth it. Focus. Guilt creeps: \textit{Worth this? I’m not this.} Or am I? Truth hits: \textit{You are now. Live it. Find her or lose her.}

Map in my tote shifts, crinkles. Hotel pin. Next move. Head clears. Step on. Thoughts lock there. Nod, steady, limp out, ruin stays behind.

\chapter{Cry From My Throat}

The alley’s blood-stink clung to me, the thug’s smashed skull a ghost in my head. I slumped against a dumpster a block from the hotel, my tote heavy with the map and his cash. Tequila buzzed, fading slow, making my hands twitch, my thoughts jagged. I’d waited it out, \textit{as long as it takes}, until the edge dulled, the world around stopped being so suspicious, the blue glow under my skin dimming to nothing. My breath steadied, the pounding in my skull eased. No more screams, no more brick swings. I was me again, \textnormal{Lila}, the LA girl with the golden curls and killer smile. The hotel pin, Room 12 off the 405, burned in my mind. Mia was there, tied up, scared. I’d seen her. Killing that thug got me nothing but gore. Time to be smart.

I smoothed my sage-green dress, ripped at the hem but still clinging to my curves. My tank top was fresh from the tote, white, tight, a little faded, replacing the blood-soaked shirt I’d ditched. Hair wild, I flipped it back, letting it catch the streetlight. \textit{"Still gorgeous."} That was my ticket now. The gang wouldn’t clock a flirty party girl as the one who’d bashed their buddy’s brains out. I headed in, sandals crunching gravel, the neon “Vacancy” sign flickering ahead.

The hotel parking lot thrummed with bass, cars scattered across the cracked asphalt under dim streetlights. Neon pulsed from the lounge inside, laughter and bottles clinking over the noise. A guy leaned against a sedan, joint glowing, dragon tattoo curling up his arm, \textit{gang muscle.} I sauntered over, hips swaying, grin bright. "Hey, this the party? Heard it’s wild." My voice dripped charm, light and teasing.

He smirked, eyes raking me up and down. "You got something for us, princess?" I giggled, pulling a crumpled twenty from the thug’s stash, twirling it. "Cash for drinks. I’m fun, promise." He nodded, stepping aside. "Get in."

Inside, the air was thick, a heady mix of sweat, weed, and spilled beer. No feverish crowd here, just gang blood and their girls lounging lazy, coiled tight. Neon lights bathed the room in a pulsing glow, pink and blue streaks sliding over tattooed skin and leather cuts. A table groaned under the weight of empty bottles, and pills as confetti across the wood. I needed to go deeper, past the guards, closer to Mia. My target, my mission.

A group of guys, tattooed, drunk, and loud, lounged near the bar, passing a joint between them. Their laughter was sharp, their eyes predatory. \textit{Perfect.} I zeroed in, flashing a smile that promised trouble, tossing my hair like a weapon. "Hey, boys," I called, my voice dripping with honeyed mischief. "Room for one more?" They erupted into cheers, pulling me into their circle. Hands found my waist, my hips, fingers brushing against my skin with a boldness that made my pulse quicken. I laughed, low and throaty, leaning into their touch, letting them think I was theirs for the taking. "Got anything fun?" I purred, my gaze flicking to the pills scattered like Halloween candies.

One of them, bald with a jagged scar across his cheek, grinned and shoved a shot glass into my hand. "Drink up, sweetheart," he slurred, his eyes dark with intent. I laughed, twirling away from him, holding the glass up like a prop. "Come on, guys, I’m too young for alcohol, you know? Give a girl something to start the night." I winked, popping a bright blue pill from the table into my mouth before he could argue, letting it sit on my tongue for a beat, sharp, chemical, erratic, then swallowing with a dramatic shiver. Another guy slid his arm around me, his breath hot and damp against my neck. "Stick with us, baby," he murmured, his hand slipping lower, testing my boundaries. I giggled, twisting out of his grip, spinning into the lap of the next guy, a wiry man with a gold chain and hungry eyes. \textit{Strategy, not surrender.}

The vibe shifted fast. The bald guy grabbed my wrist, pulling me back to him, his hand sliding up my thigh with a possessiveness that made my skin prickle. I played along, heart racing, straddling him for a moment, my lips brushing his ear. "You’re trouble," I whispered, my voice a sultry tease, before slipping away, laughing as I moved to the next. The wiry guy grabbed my ass, his grip firm, and I swayed against him, letting him think he had me. The group closed in around me, hands roaming my chest, my hips, my thighs, each touch a calculated risk. I danced between them, a whirlwind of heat and temptation, their laughter turning guttural, their hunger palpable. But I needed one, not all.

Then I saw him. Across the room, he stood like a storm waiting to break, tall, lean, radiating a chaotic energy that made the air hum with electricity. His black tank clung to his torso, a second skin stretched taut over every chiseled ridge of muscle, the fabric damp with sweat that glistened under the dim lights. His ripped jeans slung low, teasing the sharp V of his hips, a dangerous promise of what lay beneath. A jagged scar sliced down his forearm, raw and brutal, a testament to battles carved into his flesh. No polished charm, no sleek watch. Just pure, unfiltered danger, a man who wore his wildness like a crown.

He cut through the room like a beast on the hunt, broad shoulders shoving bodies aside with a guttural growl that vibrated in my bones. "She’s mine tonight," he snarled, his voice a rough, possessive rasp that coiled around my spine and squeezed. Before I could blink, his hand clamped around my wrist, yanking me into him with a strength that stole my breath. The others scattered, their muttered curses fading into the haze as I collided with his chest, my palms flattening against the searing heat of him. His scent, leather, smoke, and something darker, flooded my senses, intoxicating and primal. I tilted my head, lips grazing the shell of his ear, my voice a sultry purr dripping with sin. "Hey, big guy." The words hung between us, thick with invitation, and his grin flashed, feral, untamed, a predator savoring its prey. In one swift move, he dragged me through a side door into a dim room, bare except for a stained mattress and a flickering bulb.

The door slammed shut, and he had me, back against the wall, rough hands shoving my dress up, hem bunching high. Cool air kissed my exposed flesh, but his heat consumed me, his hard body pressed flush against mine, cock thick and grinding through denim, shameless intent clear. His fingers sank into my curves, bruising and claiming, pinning me as his breath rasped hot on my throat. I arched into him, helpless against his tidal wave, pulse hammering. His teeth grazed my neck, a sharp, deliberate bite drawing a gasp from my lips, the sting igniting a molten rush pooling low in my belly. My nails clawed his back, shredding his tank, raking skin, leaving angry red streaks. He groaned, a deep, animal sound shuddering through me, setting every nerve alight.

The air crackled between us, a live wire of dominance and surrender. His hands ripped under my tank, calluses scraping ribs, thumbs teasing my breasts, cruel and slow till I whimpered. A moan tore out, raw, wild, unstoppable. His mouth crashed into mine, a bruising collision of lips and tongues, all heat and hunger. I bit back, tasting sweat, violence, melting under his grip. Fingers twisted my hair, yanked my head back, throat bare, and he devoured it, sucking, biting, marking me his, stubble burning sweet against my skin.

He was everywhere, scent choking me, hands claiming every inch, hips slamming a rhythm screaming ruin. Thighs shook as he kicked my legs apart, denim grinding my soaked panties, dragging a cry from my throat. He growled, dark eyes blazing triumph, then shoved me onto the mattress. Pants hit the floor, his cock sprung free, thick, hard, veins pulsing. No words, just a snarl as he tore my panties aside and drove in. Hot, stretching me tight, warmth flooding down my legs, slick and messy. I clawed the sheets, gasping, his thrusts deep, relentless, pounding me into the filthy bed. Sweat dripped, his growl mixed with my moans, room spinning as he fucked me raw, wild, brutal, no mercy. Teetering on the edge, body screaming, mind blank but for him, he pushed harder, claiming every shudder till I broke, a ragged cry ripping free.

Panting, he pulled out, smirking feral, cum dripping down my thighs. My mind flickered, Ethan’s voice cutting through the haze, steady and smooth, too damn perfect. "You’re okay, Lila." A rehearsed lie, cool, distant, a handler’s tone. My head spun, Ethan wasn’t just shady, he was pulling strings, maybe this whole mess. This guy was the opposite, chaos incarnate, his touch a wildfire scorching doubt clean. I shoved up, breathless, giggling to mask it. "Need a sec, stud." He swaggered out, back to the lounge. I stumbled to the hall, heart slamming, bass fading. A “Storage” door gaped, a closet with boxes stacked, a mop leaning crooked. I slipped in, quiet, safe. Waited hours till the place went dead. That pill’d keep me wired till dawn. Dug through a box, found a half-empty bottle of whiskey and a red pill, jagged edge. Slammed both down, the burn snapping the white male awake.

\textit{"MIA—NEAR—FIND—NOW—"} roared in my skull, pen scratching the notepad: \note{Rooms check Mia close.} Blue glow flickered under my skin. \textit{Not real.} Time to hunt.

\chapter{Tracing Lazy Circles}

The whiskey stink hit my throat, a hot burn waking the beast inside. The closet door banged open behind me, party noise fading to a dull hum. I stumbled into the hallway, boots scuffing the carpet, eyes darting. Room 12 loomed ahead, door cracked, light bleeding out. I shoved in. Empty. Mia’s chair tipped over, ropes limp like dead snakes. A girl cowered in the corner, all shaky limbs and big eyes. "Where’s Mia?" I barked, voice rough, too loud.

"Basement," she mumbled, pointing down the hall. "They took her." Her words twisted in my skull. \textit{Liar? Trap?} I scratched fast in my notepad: \note{Girl basement Mia check} and bolted down the hall. The stairwell door creaked open, concrete steps dropping into shadow. Each echo bounced like the VR trial prison, rusted bars and cold floors flashing back. My pulse thudded. \textit{Same vibe. Setup?}

The basement stretched out, a row of doors like jail cells. First one: a girl, bruised, not Mia. She reached through the bars, eyes pleading. "Help me," she whispered. I froze, heart hammering. \textit{Save her? Save Mia?} Second door: another girl, staring blank, not Mia. Third: Mia, slumped against the wall, wrists red from ropes. "Mia!" I rasped, dropping beside her, clawing at her ties. Her head lifted, eyes foggy but alive. "\textnormal{Lila}? You’re weird." I growled, "No time. Out. Now."

But the other doors loomed. More girls. All trapped. Eyes wide, hands gripping bars. \textit{Save them? Save Mia? Both?} Time ticked. Gang upstairs. Move fast. I scratched in my notepad: \note{Girls save? risk.} Mia tugged my arm. "\textnormal{Lila}, let’s go." But the girl in the first cell whimpered, reaching out. My chest tightened. \textit{Leave them? Come back later? Police?} Police couldn’t be trusted, gang might have connections. They’d move the girls, or worse. I darted to the first cell, fumbled with the lock. "I’ll get you out," I muttered, but the lock stuck, rusted shut. Boots pounded closer, shouts echoing down the stairs. Mia hissed, "They’re coming!"

I glanced back, shadows on the stairwell. No time. Save Mia. Come back later. "Sorry," I choked, grabbing Mia’s hand. We bolted for the exit, but the doors burst open. Black-clad figures stormed in, Haitian gang with masks and rifles. They grabbed girls, one barking, "Do not shoot the girls, take them alive!" I lunged for Mia, but a rifle butt cracked my skull, lights popping. \textit{"HOSTAGE—TAKEN—MIA—"} I screamed inside as darkness ate me.

I blinked awake, head pounding, tied to a chair in a dusty office. Dim light seeped through boarded windows, gang voices rumbling outside. Mia sat next to me, wrists bound, her gaze fierce despite the fear. The alcohol buzz lingered, fading slow, keeping me sharp yet raw. My sage-green dress clung damp to my skin, glitter smudged from the party. I tugged the ropes, loose enough to shift but biting my wrists, wincing. "Mia," I whispered, "you okay?" She nodded, barely, then leaned close. "What’s wrong with you? You’re not you."

I bit my lip, the LA-girl gloss long gone. "It’s the alcohol. Turns me into someone else, that personality from VR. Sharp, but crazy." Mia’s hand brushed mine, warm, steady. "You’re still \textnormal{Lila}," she said, voice low. "Just... stronger." Her fingers tightened, and my heart tripped over itself. A spark flared, new and scary, not the bestie vibe I knew. I didn’t pull away.

Mia leaned closer, her breath soft against my cheek, warm and shaky. "I need you," she whispered, and it wasn’t just words, it was a tether, raw and desperate. I nodded, my own need echoing hers, loud in the silence. Our lips met, tentative at first, then urgent, like we were drowning and this was air. I tugged her ropes free, her wrists red but loose, and her hands slid under my torn dress, tracing my skin with a tenderness that made me ache, her touch grounding me. She wrapped her arms around me, pulling me close, her body warm against mine. The world narrowed to her touch, her warmth, the quiet sounds we made, soft gasps, whispers, the rustle of fabric. It was quick, messy, perfect, a stolen moment in the chaos, not about the act but about clinging to each other, finding comfort in the storm.

When it was over, we lay tangled, breathless, her head on my chest, my fingers tracing lazy circles on her shoulder. "What are we now?" she murmured, voice barely above a whisper, fingers brushing my arm. I kissed her forehead, no answers, just the steady beat of her heart against mine. The room felt smaller, quieter, but for a moment, we were safe in each other’s arms.

The next day, the air hung heavy, thick with dread. The door flew open, a gang guy swaggering in, eyes glinting mean. "Boss wants a treat," he sneered, grabbing Mia. "No!" I yelled, thrashing against my ropes, the coarse fibers biting into my wrists loosened from before. She kicked, fierce as ever, but another guard grabbed me, his grip bruising, hauling me up with her. They dragged us to a back room, dim and reeking of sweat and smoke, the walls stained and peeling. The boss sat sprawled on a couch, a gold-toothed grin splitting his face, his presence suffocating. "Two for one," he chuckled, standing, his boots heavy on the floor. His guards shoved us forward, hands like vices on our arms, pinning us in place.

He stepped close, his breath sour, fingers trailing Mia’s jaw, slow and deliberate. She jerked back, spitting, her eyes blazing defiance. He laughed, cold and sharp. "Feisty. I like that." His hand slid lower, brushing her collarbone, and I lunged, screaming, "Don’t touch her!" A guard’s fist cracked against my skull, stars bursting behind my eyes, pain blooming sharp and bright. The world tilted, then blackness swallowed me whole.

I woke back in the office cell, head throbbing like a drum, mouth dry and tasting of copper. The room was dim, the air stale, and my body ached, ribs sore, wrists raw from ropes, a dull pain radiating from my temple. My tank top hung loose, one strap snapped, the fabric stretched and stained. Mia huddled beside me, her dress torn at the shoulder, the hem frayed and uneven. Fresh bruises bloomed on her neck, purple and angry, and her arms bore red marks where hands had gripped too tight. Her eyes were glassy, staring at nothing, her face pale and hollow, like she’d retreated somewhere deep inside.

I scooted closer, ignoring the sharp pain in my side. "Mia," I whispered, voice cracking, raw and ragged. She flinched, then softened, her gaze flickering to me, haunted but alive. "I’m here," I said, reaching for her hand, my fingers trembling. She gripped it tight, her nails digging into my palm, grounding us both. "It was bad," she choked out, her voice barely a whisper, thick with unshed tears. "I know," I murmured, pulling her against me, her head resting on my shoulder. "But we’re still here. Still us." She nodded, tears spilling, hot and silent, soaking into my torn top. I held her close, fury and love burning equal in my chest, the weight of what happened pressing down on us, unspoken but understood.

"We’re gonna get out," I said, voice shaky but fierce. "And they’ll pay." Mia’s hand tightened in mine, a silent promise, and for a moment, amidst the pain and the wreckage, we were whole, holding onto each other like an anchor.

Days smeared together. Scraps of food, gang taunts, but mostly they ignored us. Mia stayed close, her fire flickering back. One night, her lips found mine, soft and urgent, like she needed to feel something alive. I kissed her back, no white male lust for Asian chick, just me, raw and real. "What is this?" she murmured, breath warm. "I don’t know," I said, "but I need you too." It felt right, then wrong. Sober me loved her as a friend, white male me wanted more. I couldn’t untangle it.

Then, dumb luck: a gang guy tossed me a beer, smirking. "Chill out, princess." I caught it, silver can glinting. Mia’s eyes widened. "\textnormal{Lila}, don’t," she said, too late. I cracked it, gulped, and the white male in me roared awake. \textit{"ESCAPE—NOW—PLAN—"} I screamed inside, mind slicing through the fog of reality. My senses snapped sharp, every shadow a clue, every creak a threat. We weren’t tied, sloppy guards, cocky. I scanned the room: desks, chairs, a flickering light, a door ajar. Mia huddled close, her breath shaky. "Follow me," I whispered, voice low, controlled. She nodded, trusting but scared.

I crept to the door, peeked out. Hallway empty, fluorescents buzzing. First floor, guards near stairs. I scratched in my notepad: \note{Stealth down exit.} We slipped out, hugging the walls, my boots silent on the tile. Mia’s sandals scraped once, and I froze, but no one came. We ducked behind a filing cabinet as a guard strolled past, humming off-key. \textit{Lazy.} Good. We waited, then moved, slipping into the stairwell. Each step echoed like a gunshot in my skull. \textit{Too loud, trap?} But we made it to the second floor, shadows stretching long.

A locked door blocked the way. Keycard needed. I rifled a nearby desk, finding one under a coffee cup. Swiped it, but the lock beeped loud, red light flashing. \textit{Alarm, shit.} Boots pounded from above, shouts cutting through. "Do not shoot the girls, take them alive!" a voice barked. Mia gasped, and I grabbed her hand, yanking her down the hall. We burst into an office, slamming the door. My eyes darted, a machete stabbed into a glowing monitor, strange symbols carved on the blade pulsing with eerie light bouncing off the screen. I snatched it, the weight heavy, familiar. "Stay back," I growled to Mia, who nodded, pale.

Door splinters, guards pour in. Swing blade, air whistles, then flesh tears. Blood sprays, hot, splatters my face, wall, floor. Skull cracks, wet cardboard sound. One down. More come. Paranoia spikes. Faces warp: \textnormal{MLK}’s glare, stern, then \textnormal{Obama}’s grin, twisted. \textit{Not real.} Swing again, machete bites deep, neck snaps, gore slicks my hands. \textnormal{MLK} charges, fists up, I slash, catch his arm, blood gushes, he staggers back roaring justice. \textnormal{Obama} steps in, calm dodge, I lunge, blade grazes his chest, he laughs, cold, calculated. Guard lunges, spin, slash throat, blood arcs like a fountain. Body hits floor, twitches, red pools.

Room blurs, motion, madness. Another charges, face shifts to \textnormal{Nelson Mandela}, wise, weathered, eyes hollow, predatory. \textit{"CONSPIRACY—LIES—TRAP!—"} rips from my throat, blade arcs down, cleaves shoulder. He staggers, grins, blood bubbles between teeth. Lunges again. Twist, dodge, swing sideways. Catches ribs, he crumples, face flickers between \textnormal{Mandela} and a stranger. \textit{Unknown. Not cataloged.} \textit{"WHO—YOU—SPY?—"} Voice cracks, raw, loud. No answer.

"Stop it!" I shout, voice breaking. "Stop looking at me like that!" They don’t stop, never stop. Another guard, face melts into \textnormal{Malcolm X}, glare intense. Voice cutting through my head: \textit{"You’re the problem."} Swing wild, machete hits temple, he drops like stone, voice lingers, bounces off walls, taunting. I pivot, slash again, catch his arm as he rises, blood sprays, he falls silent.

Room’s a mess, screams, splintering wood, blood stink thick. Breathing hard, arms shake. Can’t stop. They keep coming, faces shift, bodies relentless. Guard with \textnormal{Kanye West}’s smirk swings baton, I duck, air rushes past. Retaliate, machete upward, guts him, gasps, smirk falters. Yank blade free, blood sprays chest. "Not real!" I scream, hoarse. "None of you are real!" But blood’s real, warm, sticky, bodies real, heavy, lifeless.

Another guard, face shifts to \textnormal{Muhammad Ali}, confident grin. Moves like a boxer, dodges swings easy. Swing again, he sidesteps, laughs. "Float like butterfly," he taunts. Lunge desperate, catch him this time, machete sinks into side, he grunts, grin falters. Twist blade, drops to knees, face flickers between \textnormal{Ali} and a stranger. Yank free, he collapses, blood pools.

Silence now, save ragged breathing. Bodies litter floor, faces frozen in pain, disbelief. Look at hands, slick with blood. Nausea hits. \textit{What did I do? Who did I kill?} Then, him. Doorway. \textnormal{Barack Obama}, calm, composed. Steps forward, hands raised, peace gesture, eyes cold, calculating.

"It’s over," he says, steady. "Put the blade down."

Shake head, tears stream. "You’re not real. Not him."

"I’m as real as you want me to be," he replies, steps closer. "But this ends now."

Grip machete tight, heart pounds. He’s lying, all part of the conspiracy, nightmare. Can’t trust. \textit{"LIAR—SETUP—TRAP!—"} Charge, swing with all strength. He sidesteps, fluid, precise, grabs my wrist, twists. Machete clatters, I stumble, legs give out. He catches me, grip firm, not unkind.

"It’s okay," he whispers, soft. "It’s over."

But it’s not, never over. Look into his eyes, truth hits hard. \textit{Not real, none of this real, neither am I.}

Mia screamed, backing into a corner, eyes wide with horror. Then, bang. Loud, sharp. Guard grunts, falls off me, blood seeping from chest, eyes blank. Mia stands, shaky, holding a pistol, smoke curling from barrel. Grabbed it from a dead one. "\textnormal{Lila}, up!" she yells, voice trembling but fierce. I gasp, lurch to my feet, arm stinging, ribs screaming. She shot him, saved me. \textit{"MIA—GUN—FREE—"} I scribble mentally, no time for notepad now. I growl, lunge for stairwell.

We bolt, stairwell dark, steps slick with spilled beer, blood trailing behind. Feet pound concrete, hers slap, mine thud. Third floor, empty. Second, voices echo, but we duck behind crates, breath held. First floor, exit’s there, glass door cracked, night air seeping in. Notepad slips from pocket, pages soak red. No time, keep moving. Push through, glass crunches underfoot, cool breeze hits hard.

Outside, parking lot, shadows stretch long, cars gleam under streetlights. No guards yet, quiet, too quiet. \textit{"TRAP?—RUN—NOW—"} Mind races, paranoia spikes, but Mia grabs my hand, pulls me forward. We sprint, past the hotel, into the alley, gravel bites my soles. Her dress flaps torn, my tank top sticks wet with blood, sweat. Lungs burn, keep moving. City lights blur, neon, headlights, horns faint. Turn corner, hide behind dumpster, panting hard. Mia’s grip tightens, her eyes wild but steady. "We’re out," she whispers, voice raw. I nod, chest heaving, alive, free, together. For now.

\chapter{Rolling Through Debris}

The air in Mia’s loft hung heavy, thick with dust and the faint tang of spilled wine from last week’s chaos. I stumbled in, my boots crunching over broken glass, and slung my tote onto the couch. Mia was already at her closet, pulling out essentials: a stack of clothes, a wad of cash, her qipao, that stunning red silk piece embroidered with gold dragons, a tether to her Shanghai roots. She folded it with trembling hands, like it might vanish if she let go. I rummaged through the wreckage for my charm bracelet, spotting its tiny golden sun pendant peeking out from under a pile of crumpled sketches. My fingers closed around it, a small anchor in the storm. The loft was a disaster, overturned chairs, gutted drawers, that flickering neon "Good Vibes" sign on the wall glowing like a cruel joke now.

I froze, staring at it. Months back, when Mia moved in, this place was a different kind of mess, boxes stacked high, tape peeling, our laughter bouncing off bare walls. We’d hit a flea market that weekend, hunting for deals, and spotted those signs, two for the price of one. "Good Vibes", they screamed in pink neon, cheesy but perfect. \textit{"One for me, one for you,"} Mia had grinned, tossing her hair, Shanghai flair in her smirk. We lugged them home, giggling, tripping over packing peanuts, swearing they’d light up our lives. Now mine hung in my apartment, hers flickered here, a matched pair from a cleaner chaos.

"We’re gone, babe," I said, voice quivering but edged with steel, snapping back to now. "San Gabriel Mountains. Secluded. Safe." Mia nodded, zipping up her bag, but her eyes darted to the shadows. Her parents’ mafia connections loomed over us, a noose tightening. We had to move.

The door creaked, slow and deliberate, my heart slammed against my ribs. Ethan stepped in, his surfer-boy charm replaced by a predator’s stare, cold and unblinking. His sleek silver watch caught the dim light, too techy for a beach bum. "Leaving so soon?" he purred, but his tone sliced like glass. Mia stiffened, clutching her bag. I squared my shoulders. "Back off, Ethan. We’re done playing."

He smirked, stepping closer, his elbow clicked, a faint, unnatural sound. "You don’t get to walk away." I snatched a lamp from the floor, chucked it at his head. He dodged, too fast, his body pivoting with eerie precision. Mia grabbed a vase, swung, but he sidestepped, fluid yet stiff, like a machine. His eyes flashed, a metallic glint, gone in an instant. \textit{Not right. Not human.}

He lunged, I bolted for the kitchen, pulse roaring. My hand grazed a bottle, tequila, half-empty, glinting, half-weapon. His boots thudded behind me. No time to think. Twisted the cap, gulped it down, fire exploded in my chest. The world sharpened, fractured. White male in me woke up. \textit{"ETHAN—ROBOT?—KILL—"} screamed my brain, loud and jagged. I smashed the tequila bottle over his head, glass rained down, liquor splashed, a whirr sputtered from his neck. Spun, hurled a chair at him, it cracked against his side, wood splintering, he barely flinched. Too tough. \textit{Metal inside.}

He grabbed me, fingers like steel clamps, cold and unyielding. I snarled, slammed my forehead into his nose, a dull crunch, no blood, just a hollow clang. \textit{Robot. Fact.} I wrenched free, snatched a jagged glass shard from the floor, slashed his chest. Fabric ripped, exposing sparking wires, metal plates gleaming under fake skin. \textit{Real. See it.} Stabbed again, he caught my wrist, twisted until I screamed, pain flared, white-hot.

\textit{"MIA—GO!—"} I roared. She hesitated, eyes wide, bolted for the door. Ethan tossed me into the wall, plaster buckled, my ribs ached, he charged after her. I staggered up, tequila blazing, tackled him. We hit the ground hard, rolling through debris. He swung, fist cracking my jaw. Blood flooded my mouth, stars burst. I spat, grabbed a broken chair leg, smashed it into his shoulder. Metal groaned, sparks flew, his arm hung limp. He lunged, relentless, watch beeping shrill, urgent. \textit{Calling someone?}

I grabbed the "Good Vibes" sign, ripped it from the wall, shoved it in front of me as he swung again. His fist punched through, neon flared, electric shock jolted him. Circuits popped, his body jerked unnatural, limbs twisting inhuman, flung him across the room. Smoke curled, silence fell, he lay still, twitching faintly. Panting, I tore his shirt wider, saw wires, circuits, a robotic core, then blinked, just blood, torn flesh, a dead man. Sober doubt crept in, \textit{was that real?}

"Move. Now," I rasped, snagging our bags. Mia nodded, pale but moving. We stumbled to Ethan’s ride, a sleek black beast, dashboard glowing with tech we didn’t understand. Stolen, risky, but ours. We peeled out, LA’s glitter shrinking in the rearview as dawn crept over the San Gabriel Mountains. The drive was a blur, city lights fading, roads twisting, pines looming tall and dark against a pink-streaked sky.

We stopped in a secluded clearing, stars dimming overhead. Hands shaking, we pitched a tent under the pines, the air crisp and quiet. I dug out a granola bar, split it with Mia, the crunch grounding us. Exhaustion clawed, tequila’s edge softened, I leaned in, kissed her, soft, slow, tasting dust and defiance. She froze, then melted into it, hands light on my bruised cheeks. The buzz slipped away fully, I pulled back, smiling. "You’re my bestie, babe." She laughed, shaky, we hugged, fierce and tight, friendship a tether.

We crawled into the tent, sunrise spilling gold through the trees. Sleep took us, safe for now, but Ethan’s wires, or was it blood, flickered in my mind, a riddle unanswered.

\part{Ping the Source}

\chapter{Wires One Second}

The tent glowed pink with the sunrise, a soft, dreamy light spilling over Mia's sleeping face. I propped myself on one elbow, watching her breathe, her chest rising and falling like the gentle tide at Venice Beach. My charm bracelet dangled from my wrist, the tiny golden sun pendant catching the dawn, glinting like a beacon of simpler times—days of iced lattes, sandy toes, and Mia's laughter ringing through the boardwalk. Now, we were fugitives, tucked away in the San Gabriel Mountains, the crisp pine-scented air a fragile shield against the chaos we'd left behind in LA. Ethan's death, or whatever that was, clung to me like a shadow, heavy and cold.

I slipped out of the tent, barefoot on the cool earth, the tall pines stretching dark against the sky. The quiet felt tense, like the world was holding its breath, waiting for the next disaster. Ethan's car sat a few yards off, a sleek black monster that didn’t belong here, its high-tech sheen screaming secrets. I hugged my arms around myself, the sage-green dress I’d worn since the loft hanging loose and torn at the hem. My curls were a mess, wild from sleep, but the golden streaks still caught the light. \textit{At least I’ve still got my glow}, I thought, vain even now, a flicker of the old Lila refusing to fade.

Mia stirred behind me, her sleek black hair spilling over the sleeping bag as she sat up. \textit{Morning, babe}, she mumbled, rubbing her eyes. Her voice was steady, but I saw the flicker of fear in her dark gaze, the weight of her family’s mafia ties pressing down. I gave her a small smile, kneeling to check on her. \textit{You okay?} She nodded, brushing my hand with hers, a quick, warm touch that made my heart skip. We were different now—closer, rawer—teetering on something I couldn’t name.

\textit{I need to look at his car}, I said, standing. \textit{There’s something off about Ethan. I can’t shake it.} Mia’s brow furrowed, but she didn’t argue, just grabbed her jacket and followed me. The car’s leather interior was cool against my skin as I slid into the driver’s seat, Mia leaning over from the passenger side. The dashboard was a futuristic puzzle—buttons, screens, way beyond anything a surfer boy should have. I pressed a random control, and a screen flickered to life, glowing with a message: coordinates to a rural Mexican town and a name - \textnormal{Dr. Ruiz}. My breath caught. \textit{Who the hell is Dr. Ruiz?}

Mia’s eyes sharpened, her family related expirience with black deals what mafia has just kicking in. \textit{Sounds like a lead. Let me see that.} She tapped the screen, pulling up a map, her fingers quick and sure. \textit{Mexico. Not far from the border. Why would Ethan have this?} I bit my lip, memories of the fight flashing back, the neon sign sparking, Ethan’s body whirring with wires one second, then just blood and flesh the next. \textit{He wasn’t normal, Mia. I saw circuits, I think. But then it was gone. Was I imagining it?}

She studied me, her gaze steady. \textit{You were not sober when we left. If you saw it, it’s migh not be real. But his watch, this car—it’s all too advanced. Maybe he was a robot, or it was implants.} I twisted the bracelet on my wrist, the golden sun spinning. \textit{How big in can be? The VR trial is a key?} Mia nodded, pulling out her phone. \textit{Let’s check the car more. There might be something else.}

We rummaged through the console, maps, a charger, nothing useful, until Mia pressed a hidden panel under the dash. A faint \textit{click}, and a digital log flickered on the screen, timestamped days ago. \note{Coordinates confirmed}, it read, followed by, \note{Dr. Ruiz, AI startup contact}. My pulse quickened. \textit{AI startup. Like the one that ran the trial?}

Mia’s fingers flew over her phone, testing the weak mountain signal. \textit{Got a bar. Let’s look him up.} She typed \textnormal{Dr. Ruiz AI startup}, and a social media profile popped up—Dr. Alejandro Ruiz, a scientist with sharp features and a nerdy grin, posting photos from a dusty Mexican town. Recent shots showed him in front of a rustic building, captioned \textnormal{\#researchlife} and \textnormal{\#newworlds}. The town matched the coordinates. \textit{He’s there}, Mia said, pointing. \textit{And look—his bio mentions neural interfaces. That’s VR tech.}

I stared at the screen, my mind drifting back to the VR trial, those prison cells I’d walked through as the white male. Faces flashed, Tim from high school, Lena from psych class, Mark from the startup and then a chill hit me. Dr. Kline, that professor from uni, sitting cross-legged in a cell, his cold stare running numbers on me like I was code to crack. I’d noted him then: \textit{Cell 21, Dr. Kline, uni, calm, 11:31 a.m.} “Wait,” I said, voice trembling. \textit{I know someone tied to this. Dr. Kline, he was in the trial, a prisoner watching me. What if he’s connected to Ruiz?}

Mia scrolled further, her voice firm. \textit{Let’s see.} She dug into Ruiz’s profile, finding an older post, a conference photo, Ruiz grinning beside a familiar face: Dr. Kline, captioned \textnormal{“Colleagues in neural frontiers, pushing boundaries with old friend Kline.”} \textit{Jackpot}, Mia muttered. \textit{Kline’s from the startup too. If he was in your trial and Ruiz is linked to him, this is deeper than we thought. Ethan, the trial, your hand, it’s all tied.}

My hand. I flexed it, avoiding the urge to look too close, terrified of that blue glow I’d glimpsed. \textit{You think Ruiz knows what’s happening to me?} Mia met my eyes, pragmatic as ever. \textit{He might. Kline was in your head during the trial; Ruiz could’ve built it with him. If Ethan was their puppet, Ruiz is our shot at figuring out who’s after us, my family, the mafia, whoever sent that thing.} She tapped the phone off, decisive. \textit{We need to find him.}

I glanced at the tent, the mountains cradling us in deceptive peace. \textit{Mexico’s risky. Cartels, your parents’ enemies...} Mia cut in, her tone hard. \textit{Staying here’s riskier. The Zhangs won’t stop, and whatever Ethan was, someone’s coming for his mess. Ruiz might have answers, why the trial, why you’re different.} She softened, touching my arm. \textit{We’ve got his car. We can do this, Lila. Together.}

I swallowed, the stakes sinking in. My sober self wanted to hide, to vanish into the pines with Mia and pretend we were safe. But she was right, our lives were still in danger, and answers were our only way out. I thought of the trial again, the pastor’s wild questions in that cell - \textit{What burns in your heart?}, and Kline’s icy stare beside him, calculating. \textit{Wait. The pastor grilled me, but Kline just watched. What if Ruiz and Kline designed it together?}

Mia tilted her head, piecing it together. \textit{Possible. The startup built the trial. Kline’s presence, Ruiz’s tech, Ethan could’ve been their experiment.} I nodded, the golden sun pendant spinning as I twisted my bracelet. \textit{Then we go. To Mexico. To Ruiz.}

We packed fast, breaking down the tent, loading Ethan’s car with our bags. The engine purred to life, the dashboard glowing with those coordinates, a digital lifeline into the unknown. As we drove down the mountain, pines thinning into scrubland, I gripped Mia’s hand, her strength steadying me. The mafia, the trial, Ethan’s wires, or blood, loomed behind us, but ahead was Dr. Ruiz, a key to cracking this nightmare. My charm bracelet jingled, a faint shimmer in the dust, and I muttered, \textit{We’re coming for you, doc, ready or not.}

The engine's hum was the only sound as we plunged into the neon-drenched darkness, leaving the mountains to recede into the endless expanse of circuitry and corruption that lay ahead.

\section{To be continued...}

\end{document}